% latex table generated in R 4.1.0 by xtable 1.8-4 package
% Tue Sep 28 13:39:52 2021
\begin{longtable}{p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{8cm}}
\caption{Data in 2021 and 2020having problems causing the data in the specific year to be excluded from the analysis. Codes for stages are G = glass eel, GY = glass eel + yellow eel, Y = yellow eel, Division = FAO marine division. Kept: 0 = missing, 1 = good quality,
		2 = wgeel has modified the data, 3 = not used due to poor quality, 4 =	data is used, but there are warnings on its quality} \\ 
  \hline
\scshape{Name} & \scshape{Stage} & \scshape{Country} & \scshape{Division} & \scshape{Year} & \scshape{Kept} & \scshape{Comment} \\ 
  \hline
BeeG & G & GB & . & 2020 &   4 & Provisional data as of June 2020 - comment updated 2021 and confirmed as a final count for 2020. Das\_value updated from 7446 to 8303. Monitoring impacted by COVID19. \\ 
  BroG & G & GB & . & 2020 &   4 & Comment updated from "Provisional data as of June 2020" to "Final count for 2020". Monitoring impacted by COVID19. \\ 
  FlaG & G & GB & . & 2020 &   4 & Value updated 2021 from 93 to 1136. Underestimate due to impact of Covid restrictions.  \\ 
  NaloG & G & ES & 27.8.c & 2020 &   4 & In March (allowed from 20 to 27) only a few fishermen were active because of the reduced price of glass eel due to the COVID-19. \\ 
  SeEAG & G & GB & . & 2020 &   4 & Previous comment and value updated 2021: Value not available last year due to Covid - now available but reduced as not all returns received <U+2013> postal service impacted by covid.  \\ 
  SeHMG & G & GB & . & 2020 &   4 & Note that UK trade of glass eel has been impacted by COVID19- elver station closure within season will have impacted upon effort \\ 
  ShiFG & G & GB & 27.6.a & 2020 &   0 & Covid-19 prevented collection \\ 
  VacG & G & FR & . & 2020 &   4 & due to COVID19, the glass eel monitoring was stop since mid-march then one month of monitoring was not made at the end of the migration period \\ 
  VeAmG & G & BE & 27.4.c & 2020 &   3 & Monitoring started on 3 March and stopped on 19 March. Since 19 March monitoring was not allowed any more due to Covid 19. \\ 
  YserG & G & BE & 27.4.c & 2020 &   3 & Monitoring started on 3 February and stopped on 5 March. On 6 March there was a malfunction at the sluice, after that water level was too high to perform the monitoring and on 19 March monitoring was not allowed any more due to Covid 19. \\ 
  BroG & G & GB & . & 2021 &   4 & Provisional data up to July 2021. Trap flooded out May and June.  \\ 
  GiScG & G & FR & . & 2021 &   4 & Provisional data \\ 
  SeEAG & G & GB & . & 2021 &   4 & This is a provisional figure, with approx. 60\% of returns processed to date \\ 
  SeHMG & G & GB & . & 2021 &   4 & 0.52 was restocked to the ÅghomeÅh rivers; remaining 0.06t exported to Northern Ireland within UK also for restocking \\ 
  VacG & G & FR & . & 2021 &   4 & Provisional data \\ 
  BeeGY & GY & GB & . & 2020 &   4 & Comment and value updated in 2021. Das\_value from 758 to 3479 and comment from "Provisional data as of June 2020. Two weeks at the start of the run- end of March/early April monitoring impacted by COVID19- trap not monitored within this period" to "Two weeks at the start of the run- end of March/early April monitoring impacted by COVID19- trap not monitored within this period". \\ 
  BroGY & GY & GB & . & 2020 &   4 & Value and comment updated 2021. "Two weeks at the start of the run- end of March/early April monitoring impacted by COVID19- trap not monitored within this period." Das\_value changed from 3795 to 3794. \\ 
  GreyGY & GY & GB & . & 2020 &   4 & das\_value updated from to 2367 to 15098. Monitoring impacted by COVID19- monitoring did not start until 19th May 2020 so is a significant underestimate missing the early part of the migration period. \\ 
  HHKGY & GY & DE & 27.4.b & 2020 &   0 & no monitoring. Series ended in 2013 \\ 
  NmiGY & GY & GB & . & 2020 &   4 & das\_value updated 2021 from 3464 to 4459 (0 G, 4280 GY and 179 Y). No monitoring April May due to Covid-19 restrictions \\ 
  OatGY & GY & GB & . & 2020 &   4 & Partial count for 2020 (until end of June 2020). \\ 
  SousGY & GY & FR & . & 2020 &   4 & Provisional data \\ 
  BannGY & GY & GB & 27.6.a & 2021 &   4 & as of 10th July Derek Evans; provisional; not affected by Covid-19. \\ 
  BresGY & GY & FR & . & 2021 &   4 & Provisional data \\ 
  BroGY & GY & GB & . & 2021 &   4 & Provisional data up to July 2021. Trap flooded out May and June \\ 
  HHKGY & GY & DE & 27.4.b & 2021 &   0 & no monitoring. Series ended in 2013 \\ 
  NmiGY & GY & GB & . & 2021 &   4 & Provisional data up to end of July 2021. Combined glass eel, elvers and yellow eel count. (if separated 280 G, 5495 GY and 2019 Y). \\ 
  OatGY & GY & GB & . & 2021 &   4 & Provisional data up to end of June \\ 
  SousGY & GY & FR & . & 2021 &   4 & Provisional data \\ 
  StraGY & GY & GB & 27.7.a & 2021 &   4 & Provisional data; Individual glass eel counted; not affected by Covid-19. \\ 
  BeeY & Y & GB & . & 2020 &   4 & Comment and value updated in 2021. Das value from 7 to 297 and comment from 'Provisional data as of June 2020. Two weeks at the start of the run- end of March/early April monitoring impacted by COVID19- trap not monitored within this period' to 'Two weeks at the start of the run- end of March/early April monitoring impacted by COVID19- trap not monitored within this period' \\ 
  BroY & Y & GB & . & 2020 &   4 & Comment updated in 2021 from "Provisional data as of June 2020" to "Final count for 2020. Monitoring impacted by COVID19." \\ 
  FlaY & Y & GB & . & 2020 &   4 & New series added. Underestimate due to impact of Covid restrictions.  \\ 
  GotaY & Y & SE & 27.3.a & 2020 &   0 & This eel pass is not running \\ 
  MertY & Y & GB & . & 2020 &   4 & Provisional count as of July 2020 \\ 
  MeusY & Y & BE & 27.4.c & 2020 &   3 & In 2020 up to 17 August, 84 eels were caught (biomass 2352.2 g). Sizes of eels caught ranged from 12.4 cm to 67.3 cm (median 22.8 cm). Maximum CPUE was 40 individuals per day. This observed number of eels caught has been impacted by the covid-19 pandemic and includes both wild and restocked eels.
 Updated 2021: effort (nr days) added. \\ 
  MillY & Y & GB & . & 2020 &   0 & NC; No sampling due to Covid restrictions \\ 
  MiSpY & Y & ES & 27.9.a & 2020 &   4 & Provisional data \\ 
  RodY & Y & GB & . & 2020 &   0 & NC; Not monitored due to Covid \\ 
  VeAmY & Y & BE & 27.4.c & 2020 &   3 & Monitoring started on 3 March and stopped on 19 March. Since 19 March monitoring was not allowed any more due to Covid 19. \\ 
  BroY & Y & GB & . & 2021 &   4 & Provisional data up to July 2021. Trap flooded out May and June \\ 
  MertY & Y & GB & . & 2021 &   4 & Provisional data up to mid July \\ 
  MillY & Y & GB & . & 2021 &   4 & Provisional data up to mid July \\ 
  MolY & Y & GB & . & 2021 &   4 & Provisional data up to mid July \\ 
   \hline
\hline
\label{table_series_prob}
\end{longtable}
