---
title: "Untitled"
author: "Hilaire Drouineau"
date: "23 janvier 2020"
output: 
  rmarkdown::md_document:
     toc: yes
  rmarkdown::html_document:
     keep_md: yes
     toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
wdsource <-"~/Documents/Bordeaux/migrateurs/WGEEL/wkeelmigration/source/"
load("res_landings.Rdata")
source("function_for_model.R")
library(dplyr)
library(tidyverse)
library(tidyr)
library(runjags)
library(coda)
library(ggplot2)

```

# Introduction
We start by loading the rdata provided by Cédric who has imported and edited all the xlsx files. He also provides a very good overview of the content [here](landings_seasonality.md). Based on this job, we will try to carry out a similar analysis as for [seasonality](jags_modelling.md). More specifically, we can use the same Bayesian model to make a clustering of time series. For each stage, we will build a data set that gives for each season, and each EMU (and perhaps habitat), the proportion of catches per month.

For convenience, we rename the data.frame with names consistent with the seasonality data.set

```{r}
res <- res %>%
  rename(das_month=month, das_value=value, das_year=year)
```

# Glass Eel
First, let's select data corresponding to glass eel stage.

```{r}
glass_eel <- subset(res, res$lfs_code=="G")

# we start by removing rows with only zero
all_zero <- glass_eel %>%	group_by(emu_nameshort,lfs_code,hty_code,das_year) %>%
		summarize(S=sum(das_value)) %>% 
    filter(S==0)

glass_eel <- glass_eel %>% 
	  anti_join(all_zero)



#For glass eel, we aggregate data per habitat
glass_eel <- glass_eel %>%
  select(das_year, das_month, das_value, emu_nameshort, cou_code) %>%
  group_by(das_year, das_month, emu_nameshort, cou_code) %>%
  summarise(das_value=sum(das_value))
```

Similarly to seasonality, we will build season. For glass eels, seasons are rather consistent in whole Europe, so we use the same definition as in seasonality: Here, we split in october (starts of catches in Spain) and a season y will correspond to ostober - december y-1 and january to september y.

```{r}
glass_eel$season <- ifelse(glass_eel$das_month>9,
                             glass_eel$das_year+1,
                             glass_eel$das_year)
glass_eel$month_in_season <- as.factor(ifelse(glass_eel$das_month>9,
                                      glass_eel$das_month-9,
                                      glass_eel$das_month+3)) #1 stands for nov,

#we remove data from season 2020
glass_eel <- glass_eel %>%
  filter(season < 2020)

```

## Data selection
Now we should carry out data selection, more specifically, we want to eliminate rows with two many missing data, too much zero and to check whether there are no duplicates (though Cedric already did it)

```{r, warning=FALSE}
kept_seasons <- lapply(unique(glass_eel$emu_nameshort), function(s){
  sub_glass <- subset(glass_eel, glass_eel$emu_nameshort==s)
  good_coverage_wave(sub_glass, "G")
})
```
Finally, here are the series kept given previous criterion.

```{r}
names(kept_seasons) <- unique(glass_eel$emu_nameshort)
kept_seasons[!sapply(kept_seasons,is.null)]
```

## Data preparation
We carry out the same procedure as for seasonality. 

```{r}
glasseel_subset <- subset(glass_eel, 
                           mapply(function(season, series){
                             season %in% kept_seasons[[series]]
                           }, glass_eel$season, glass_eel$emu_nameshort))


glasseel_wide <- pivot_wider(data=glasseel_subset[, c("emu_nameshort",
                                                     "cou_code",
                                                     "season",
                                                     "das_month",
                                                     "das_value")],
                                names_from="das_month",
                                values_from="das_value")
names(glasseel_wide)[-(1:3)] <- paste("m",
                                       names(glasseel_wide)[-(1:3)],
                                       sep="")

###we count the number of zeros per lines to remove lines without enough
###fishes
data_poor <- data.frame(glasseel_wide$emu_nameshort,
                        glasseel_wide$season,
                  zero=rowSums(glasseel_wide[, -(1:3)] == 0 |
                                 is.na(glasseel_wide[, -(1:3)])),
           tot=rowSums(glasseel_wide[, -(1:3)], na.rm=TRUE))
data_poor %>% filter(zero > 9) #we remove years where we have less than 2 months
glasseel_wide <- glasseel_wide[data_poor$zero < 10, ]

```

It leads to a dataset with `r nrow(glasseel_wide)` rows. 

We now replace NA value per zero since we selected our dataseries with missing months corresponding to insignificant months / closed months, and we compute proportions per month for each year.

```{r}
glasseel_wide <- glasseel_wide %>%
  replace_na(replace=list(m1=0,
                          m2=0,
                          m3=0,
                          m4=0,
                          m5=0,
                          m6=0,
                          m7=0,
                          m8=0,
                          m9=0,
                          m10=0,
                          m11=0,
                          m12=0))
glasseel_wide[, -(1:3)] <- glasseel_wide[, -(1:3)] + 1e-3
total_catch_year <- rowSums(glasseel_wide[, paste("m", 1:12, sep="")])
glasseel_wide <- glasseel_wide %>%
  mutate_at(.vars=paste("m",1:12,sep=""),function(x) x/total_catch_year)
```

The Commission asks us to compare the pattern before and after 2007, probably to see the effect of the Eel Regulation. It is therefore necessary to build a period index. However, since most countries implemented their EMPs only in 2009/2010, we split in 2010.

```{r}
glasseel_wide$period <- ifelse(glasseel_wide$season>2009,
                                  2,
                                  1)

table(glasseel_wide$period,
       glasseel_wide$emu_nameshort)
```
The situation is well balanced between the two periods.


## Running the model
```{r}
group <- as.integer(interaction(glasseel_wide$emu_nameshort,
                                            glasseel_wide$period,
                                            drop=TRUE))
nb_occ_group <- table(group)
y <-as.matrix(glasseel_wide[, paste("m", 1:12, sep="")])
```

Now, we make a loop to select the number of clusters based on a DIC criterion

```{r, eval=FALSE}
comparison <- lapply(2:7,
       function(nbclus){
         mydata <- build_data(nbclus)
         res <- run.jags("jags_model.txt", monitor= "deviance",
                      summarise=FALSE, adapt=20000, method="parallel",
                      sample=2000,burnin=100000,n.chains=1,
                      inits=generate_init(nbclus, mydata),
                      data=mydata)
         res_mat <- as.matrix(as.mcmc.list(res))
         mean(res_mat[,1])+0.5*var(res_mat[,1])
       })
best_glasseel_landings <- data.frame(nbclus=2:7,dic=unlist(comparison))
save(best_glasseel_landings, file="glasseel_landings_jags.rdata")
```

```{R}
load("best_glasseel_landings")
best_glasseel_landings
```

While 7 gives the best overall DIC, the gain flattens after 5 clusters. Moreover, we only have `r length(unique(group))` groups of period x emu, therefore we won't go beyond 7 clusters (8 would correspond to 4 groups at each period).


```{r, eval=FALSE}
nbclus <- 7
mydata <-build_data(7)
myfit_glasseel_landings <- run.jags("jags_model.txt", monitor= c("cluster", "esp", "alpha_group",
                                            "cluster", "centroid",
                                            "centroid_group",
                                            "distToClust", "duration_clus",
                                            "duration_group",
                                            "lambda","id_cluster",
                                            "centroid"),
                      summarise=FALSE, adapt=20000, method="parallel",
                      sample=10000,burnin=200000,n.chains=3, thin=5,
                      inits=generate_init(nbclus, mydata), data=mydata)

#analysis of traceplots and message confirm that adaptation phase of chains 2 
#and 3 were not successful, therefore, we keep only chain 1.
myfit_glasseel_landings <- divide.jags(myfit_glasseel_landings, 1)

save(myfit_glasseel_landings, best_glasseel_landings,
     file="glasseel_landings_jags.rdata")
```

## Results
Once fitted, we can plot monthly pattern per cluster
```{r}
load("glasseel_landings_jags.rdata")
nbclus <- 7
mydata <-build_data(7)
get_pattern_month <- function(res,type="cluster"){
  res_mat <- as.matrix(as.mcmc.list(res, add.mutate=FALSE))
  if (type=="cluster"){
    sub_mat <- as.data.frame(res_mat[,grep("esp",colnames(res_mat))])
  }
  sub_mat <- sub_mat %>% 
    pivot_longer(cols=1:ncol(sub_mat),
                 names_to="param",
                 values_to="proportion")
  tmp <- lapply(as.character(sub_mat$param),function(p) strsplit(p,"[[:punct:]]"))
  sub_mat$cluster<-as.factor(
    as.integer(lapply(tmp, function(tt) tt[[1]][2])))
  sub_mat$month <- as.character(lapply(tmp,
                                       function(tt) paste("m",
                                                          tt[[1]][3],
                                                          sep="")))
  sub_mat$month <- factor(sub_mat$month, levels=paste("m", 1:12, sep=""))
  sub_mat
}

#since clusters 5 and 6 are not used, we removed them from the plot
pat <-get_pattern_month(myfit_glasseel_landings)
pat <- pat[pat$cluster!=5 & pat$cluster!=6,]
ggplot(pat,aes(x=month,y=proportion))+
  geom_boxplot(aes(fill=cluster),outlier.shape=NA) +
  theme_bw()
```

We compute some statistics to characterize the clusters.
```{r}
t(as.data.frame(characteristics(myfit_glasseel_landings, 7)))[-(5:6),]
```
Duration indicates the minimum number of months that covers 80% of the wave (1st column is the median, and the 2 next one quantiles 2.5% and 97.5% of credibility intervals). Centroid is the centroid of the migration wave (e.g. 11.5 would indicate a migration centred around mid november). The first column is the median and the two next one the quantiles 2.5 and 97.5%.

Clusters 1 and 4 starts in autum and last still january (1) or march (cluster 4). Cluster 3 is similar to cluster 4 but shited one month later. Cluster 2 and 7 correspond to fishing in spring with a shift of one month.

We can also look at the belonging of the different groups.
```{r}
get_pattern_month <- function(res,mydata){
  
  groups <- interaction(glasseel_wide$emu_nameshort,
                                            glasseel_wide$period,
                                            drop=TRUE)
  group_name <- levels(groups)
  tmp <- strsplit(as.character(group_name),
                  "\\.")
  ser <- as.character(lapply(tmp,function(tt){
    tt[1]
  }))
  period <- as.character(lapply(tmp,function(tt){
    tt[2]
  }))
  res_mat <- as.matrix(as.mcmc.list(res,add.mutate=FALSE))
  
  clus <- t(sapply(seq_len(length(unique(groups))), function(id){
    name_col <- paste("cluster[",id,"]",sep="")
    freq <- table(res_mat[,name_col])
    max_class <- names(freq)[order(freq,decreasing=TRUE)[1]]
    c(max_class,freq[as.character(1:nbclus)])
  }))
  storage.mode(clus) <- "numeric"
  classes <- as.data.frame(clus)
  names(classes) <- c("cluster", paste("clus",seq_len(nbclus),sep=""))
  cbind.data.frame(data.frame(ser=ser, period=period),
                   classes)
}

myclassif <- get_pattern_month(myfit_glasseel_landings)
myclassif <- myclassif[, -(8:9)]
print(myclassif[order(myclassif$cluster),])
```
The spatial pattern is obvious in the results. Interestingly, we saw that some EMUs are affected to different patterns before and after 2010. This seem to correspond to management measures that have effectively shorten the fishing season.

```{r}
library(sf)
library(RPostgreSQL)
cols <- c("1" = "red", "2" = "blue", "3" = "darkgreen", "4" = "orange", "7"="yellow")
con<-dbConnect(PostgreSQL(),host="localhost",dbname="wgeel_old",user="hilaire")
emu <- st_read(con,query="select * from carto.emu")
myclassif_p1 <- subset(myclassif, myclassif$period == 1)
myclassif_p2 <- subset(myclassif, myclassif$period == 2)
emu$cluster1 <- factor(myclassif_p1$cluster[match(emu$name_short,myclassif_p1$ser)],levels=1:7)
emu$cluster2 <- factor(myclassif_p2$cluster[match(emu$name_short,myclassif_p2$ser)],levels=1:7)
cou <- st_read("/mnt/SIG/01-REFERENTIELS/LIMITES_ADMINISTRATIVES_monde/european_countries_WGS84.shp")
cou <- st_transform(cou, crs=4326)
ggplot(data = cou) +  geom_sf(fill= "antiquewhite") +
		geom_sf(data=emu,aes(fill=cluster1)) + scale_fill_manual(values=cols)+
  theme_bw() +xlim(-20,30) + ylim(35,65) 
ggplot(data = cou) +  geom_sf(fill= "antiquewhite") +
		geom_sf(data=emu,aes(fill=cluster2)) + scale_fill_manual(values=cols)+
  theme_bw() +xlim(-20,30) + ylim(35,65)  

```

# Yellow
First, let's select data corresponding to yellow stage.

```{r}
yellow_eel <- subset(res, res$lfs_code=="Y")

# we start by removing rows with only zero
all_zero <- yellow_eel %>%	group_by(emu_nameshort,lfs_code,hty_code,das_year) %>%
		summarize(S=sum(das_value)) %>% 
    filter(S==0)

yellow_eel <- yellow_eel %>% 
	  anti_join(all_zero)

table(yellow_eel$hty_code)

#We have many data, so we remove "FC" and "FTC" which are weirds mixes
yellow_eel <- yellow_eel %>%
  filter(!hty_code %in% c("FTC", "FC"))

#in this analysis, the unit will correspond to EMU / habitat so we create 
#corresponding column
yellow_eel$emu <- yellow_eel$emu_nameshort
yellow_eel$emu_nameshort <- paste(yellow_eel$emu_nameshort,
                                  yellow_eel$hty_code, sep="_")

#There are some duplicates for IE_West_F that should be summed up according to
#Russel
summed_up_IE <-yellow_eel %>%
  filter(yellow_eel$emu_nameshort=="IE_West_F") %>%
  group_by(das_year,das_month) %>%
  summarize(das_value=sum(das_value))

yellow_eel <- yellow_eel %>% 
  distinct(das_year,das_month,emu_nameshort, .keep_all = TRUE)

yellow_eel[yellow_eel$emu_nameshort=="IE_West_F",
          c("das_year","das_month","das_value") ] <- summed_up_IE
  
```

Similarly to seasonality, we will build season. We reuse the procedure made for silver eel and yellow eel seasonality, i.e. defining seasons per emu, with the season starting at the month with minimum landings. The month with lowest catch fmin define the beggining of the season (month_in_season=1) and season y stands for the 12 months from fmin y (e.g., if lowest migration is in december, season ranges from december to november, and season y denotes season from december y to november y+1).

```{r}
#creating season
yelloweel <- do.call("rbind.data.frame",
                     lapply(unique(yellow_eel$emu_nameshort),
                            function(s)
                              season_creation(yellow_eel[yellow_eel$emu_nameshort==s,])))
months_peak_per_series<- unique(yelloweel[,c("emu_nameshort","peak_month")])

#large variety in the month with peak of catches among EMU / habitat
table(months_peak_per_series$peak_month)

#we remove data from season 2020
yelloweel <- yelloweel %>%
  filter(season < 2020)

```

## Data selection
Now we should carry out data selection, more specifically, we want to eliminate rows with two many missing data, too much zero and to check whether there are no duplicates (though Cedric already did it)

```{r, warning=FALSE}
kept_seasons <- lapply(unique(yelloweel$emu_nameshort), function(s){
  sub_yellow <- subset(yelloweel, yelloweel$emu_nameshort==s)
  kept <- good_coverage_wave(sub_yellow)
  #we remove season in which we have less than 50 kg of landings
  if(!is.null(kept))
    kept <- kept[sapply(kept,function(k)
      sum(sub_yellow$das_value[sub_yellow$season==k],na.rm=TRUE)>50)]
  if (length(kept) == 0) kept <- NULL
  kept
})
```
Finally, here are the series kept given previous criterion.

```{r}
names(kept_seasons) <- unique(yelloweel$emu_nameshort)
kept_seasons[!sapply(kept_seasons,is.null)]
```

## Data preparation
We carry out the same procedure as for seasonality. 

```{r}
yelloweel_subset <- subset(yelloweel, 
                           mapply(function(season, series){
                             season %in% kept_seasons[[series]]
                           }, yelloweel$season, yelloweel$emu_nameshort))


yelloweel_wide <- pivot_wider(data=yelloweel_subset[, c("emu_nameshort",
                                                     "cou_code",
                                                     "season",
                                                     "das_month",
                                                     "das_value")],
                                names_from="das_month",
                                values_from="das_value")
names(yelloweel_wide)[-(1:3)] <- paste("m",
                                       names(yelloweel_wide)[-(1:3)],
                                       sep="")

###we count the number of zeros per lines to remove lines without enough
###fishes
data_poor <- data.frame(yelloweel_wide$emu_nameshort,
                        yelloweel_wide$season,
                  zero=rowSums(yelloweel_wide[, -(1:3)] == 0 |
                                 is.na(yelloweel_wide[, -(1:3)])),
           tot=rowSums(yelloweel_wide[, -(1:3)], na.rm=TRUE))
data_poor %>% filter(zero > 9) #we remove years where we have less than 2 months
yelloweel_wide <- yelloweel_wide[data_poor$zero < 10, ]

```

It leads to a dataset with `r nrow(yelloweel_wide)` rows. 

We now replace NA value per zero since we selected our dataseries with missing months corresponding to insignificant months / closed months, and we compute proportions per month for each year.

```{r}
yelloweel_wide <- yelloweel_wide %>%
  replace_na(replace=list(m1=0,
                          m2=0,
                          m3=0,
                          m4=0,
                          m5=0,
                          m6=0,
                          m7=0,
                          m8=0,
                          m9=0,
                          m10=0,
                          m11=0,
                          m12=0))
yelloweel_wide[, -(1:3)] <- yelloweel_wide[, -(1:3)] + 1e-3
total_catch_year <- rowSums(yelloweel_wide[, paste("m", 1:12, sep="")])
yelloweel_wide <- yelloweel_wide %>%
  mutate_at(.vars=paste("m",1:12,sep=""),function(x) x/total_catch_year)
```

The Commission asks us to compare the pattern before and after 2007, probably to see the effect of the Eel Regulation. It is therefore necessary to build a period index. However, since most countries implemented their EMPs only in 2009/2010, we split in 2010.

```{r}
yelloweel_wide$period <- ifelse(yelloweel_wide$season>2009,
                                  2,
                                  1)

table(yelloweel_wide$period,
       yelloweel_wide$emu_nameshort)
```
The situation is not well balanced. Most EMU which have data in periods 1 don't have data in period 2 and conversely.


## Running the model
```{r}
group <- as.integer(interaction(yelloweel_wide$emu_nameshort,
                                            yelloweel_wide$period,
                                            drop=TRUE))
nb_occ_group <- table(group)
y <-as.matrix(yelloweel_wide[, paste("m", 1:12, sep="")])
```

Now, we make a loop to select the number of clusters based on a DIC criterion

```{r, eval=FALSE}
comparison <- lapply(2:7,
       function(nbclus){
         mydata <- build_data(nbclus)
         res <- run.jags("jags_model.txt", monitor= "deviance",
                      summarise=FALSE, adapt=40000, method="parallel",
                      sample=2000,burnin=100000,n.chains=1,
                      inits=generate_init(nbclus, mydata),
                      data=mydata)
         res_mat <- as.matrix(as.mcmc.list(res))
         mean(res_mat[,1])+0.5*var(res_mat[,1])
       })
best_yelloweel_landings <- data.frame(nbclus=2:7,dic=unlist(comparison))
save(best_yelloweel_landings, file="yelloweel_landings_jags.rdata")
```

```{R}
load("best_glasseel_landings")
best_glasseel_landings
```

While 7 gives the best overall DIC, the gain flattens after 5 clusters. Moreover, we only have `r length(unique(group))` groups of period x emu, therefore we won't go beyond 7 clusters (8 would correspond to 4 groups at each period).


```{r, eval=FALSE}
nbclus <- 7
mydata <-build_data(7)
myfit_glasseel_landings <- run.jags("jags_model.txt", monitor= c("cluster", "esp", "alpha_group",
                                            "cluster", "centroid",
                                            "centroid_group",
                                            "distToClust", "duration_clus",
                                            "duration_group",
                                            "lambda","id_cluster",
                                            "centroid"),
                      summarise=FALSE, adapt=20000, method="parallel",
                      sample=10000,burnin=200000,n.chains=3, thin=5,
                      inits=generate_init(nbclus, mydata), data=mydata)

#analysis of traceplots and message confirm that adaptation phase of chains 2 
#and 3 were not successful, therefore, we keep only chain 1.
myfit_glasseel_landings <- divide.jags(myfit_glasseel_landings, 1)

save(myfit_glasseel_landings, best_glasseel_landings,
     file="glasseel_landings_jags.rdata")
```

## Results
Once fitted, we can plot monthly pattern per cluster
```{r}
load("glasseel_landings_jags.rdata")
nbclus <- 7
mydata <-build_data(7)
get_pattern_month <- function(res,type="cluster"){
  res_mat <- as.matrix(as.mcmc.list(res, add.mutate=FALSE))
  if (type=="cluster"){
    sub_mat <- as.data.frame(res_mat[,grep("esp",colnames(res_mat))])
  }
  sub_mat <- sub_mat %>% 
    pivot_longer(cols=1:ncol(sub_mat),
                 names_to="param",
                 values_to="proportion")
  tmp <- lapply(as.character(sub_mat$param),function(p) strsplit(p,"[[:punct:]]"))
  sub_mat$cluster<-as.factor(
    as.integer(lapply(tmp, function(tt) tt[[1]][2])))
  sub_mat$month <- as.character(lapply(tmp,
                                       function(tt) paste("m",
                                                          tt[[1]][3],
                                                          sep="")))
  sub_mat$month <- factor(sub_mat$month, levels=paste("m", 1:12, sep=""))
  sub_mat
}

#since clusters 5 and 6 are not used, we removed them from the plot
pat <-get_pattern_month(myfit_glasseel_landings)
pat <- pat[pat$cluster!=5 & pat$cluster!=6,]
ggplot(pat,aes(x=month,y=proportion))+
  geom_boxplot(aes(fill=cluster),outlier.shape=NA) +
  theme_bw()
```

We compute some statistics to characterize the clusters.
```{r}
t(as.data.frame(characteristics(myfit_glasseel_landings, 7)))[-(5:6),]
```
Duration indicates the minimum number of months that covers 80% of the wave (1st column is the median, and the 2 next one quantiles 2.5% and 97.5% of credibility intervals). Centroid is the centroid of the migration wave (e.g. 11.5 would indicate a migration centred around mid november). The first column is the median and the two next one the quantiles 2.5 and 97.5%.

Clusters 1 and 4 starts in autum and last still january (1) or march (cluster 4). Cluster 3 is similar to cluster 4 but shited one month later. Cluster 2 and 7 correspond to fishing in spring with a shift of one month.

We can also look at the belonging of the different groups.
```{r}
get_pattern_month <- function(res,mydata){
  
  groups <- interaction(glasseel_wide$emu_nameshort,
                                            glasseel_wide$period,
                                            drop=TRUE)
  group_name <- levels(groups)
  tmp <- strsplit(as.character(group_name),
                  "\\.")
  ser <- as.character(lapply(tmp,function(tt){
    tt[1]
  }))
  period <- as.character(lapply(tmp,function(tt){
    tt[2]
  }))
  res_mat <- as.matrix(as.mcmc.list(res,add.mutate=FALSE))
  
  clus <- t(sapply(seq_len(length(unique(groups))), function(id){
    name_col <- paste("cluster[",id,"]",sep="")
    freq <- table(res_mat[,name_col])
    max_class <- names(freq)[order(freq,decreasing=TRUE)[1]]
    c(max_class,freq[as.character(1:nbclus)])
  }))
  storage.mode(clus) <- "numeric"
  classes <- as.data.frame(clus)
  names(classes) <- c("cluster", paste("clus",seq_len(nbclus),sep=""))
  cbind.data.frame(data.frame(ser=ser, period=period),
                   classes)
}

myclassif <- get_pattern_month(myfit_glasseel_landings)
myclassif <- myclassif[, -(8:9)]
print(myclassif[order(myclassif$cluster),])
```
The spatial pattern is obvious in the results. Interestingly, we saw that some EMUs are affected to different patterns before and after 2010. This seem to correspond to management measures that have effectively shorten the fishing season.

```{r}
library(sf)
library(RPostgreSQL)
cols <- c("1" = "red", "2" = "blue", "3" = "darkgreen", "4" = "orange", "7"="yellow")
con<-dbConnect(PostgreSQL(),host="localhost",dbname="wgeel_old",user="hilaire")
emu <- st_read(con,query="select * from carto.emu")
myclassif_p1 <- subset(myclassif, myclassif$period == 1)
myclassif_p2 <- subset(myclassif, myclassif$period == 2)
emu$cluster1 <- factor(myclassif_p1$cluster[match(emu$name_short,myclassif_p1$ser)],levels=1:7)
emu$cluster2 <- factor(myclassif_p2$cluster[match(emu$name_short,myclassif_p2$ser)],levels=1:7)
cou <- st_read("/mnt/SIG/01-REFERENTIELS/LIMITES_ADMINISTRATIVES_monde/european_countries_WGS84.shp")
cou <- st_transform(cou, crs=4326)
ggplot(data = cou) +  geom_sf(fill= "antiquewhite") +
		geom_sf(data=emu,aes(fill=cluster1)) + scale_fill_manual(values=cols)+
  theme_bw() +xlim(-20,30) + ylim(35,65) 
ggplot(data = cou) +  geom_sf(fill= "antiquewhite") +
		geom_sf(data=emu,aes(fill=cluster2)) + scale_fill_manual(values=cols)+
  theme_bw() +xlim(-20,30) + ylim(35,65)  

```
