---
title: "Data ailability"
author: "none"
date: "02/12/2021"
output: 
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    reference_docx: "../../R/Rmarkdown/ICES_template.docx" 
---






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE,message=FALSE)
library(RPostgres)
library(sf)
library(getPass)
library(ggforce)
library(ggplot2)
library(readxl)
library(flextable)
library(tidyverse)
library(yaml)
cred=read_yaml("../../credentials.yml")
con = dbConnect(Postgres(), dbname=cred$dbname,host=cred$host,port=cred$port,user=cred$user, password=getPass())
load("../../R/shiny_data_visualisation/shiny_dv/data/maps_for_shiny.Rdata")
load("../..//R/shiny_data_visualisation/shiny_dv/data/ref_and_eel_data.Rdata")
eu_cou_codes=c("AT",	"BE",	"BG",	"HR",	"CY",	"CZ",	"DK",	"EE",	"FI",	"FR",	"DE",	"GR",	"HU",	"IE",	"IT",	"LV",	"LT",	"LU",	"MT",	"NL",	"PL",	"PT",	"RO",	"SK",	"SI",	"ES",	"SE",	"GB")
country_p <- country_p %>%
  filter(cou_code %in% eu_cou_codes)
```

# Annexes 9

```{r download}
mortality <- dbGetQuery(con,"select e.* from datawg.t_eelstock_eel e where eel_qal_id in (0,1,2,3,4) and eel_typ_id in (17,18,19)")
```

# Data availability
## General overview
Tables showing the numbers of the range and numbers of years provided for each indicator by each country

```{r mortadata}
flextable(mortality %>% 
            mutate(eel_value=ifelse(is.na(eel_value & eel_missvaluequal == "NP"), 0,eel_value)) %>% 
            select(eel_typ_id,
                   eel_year,
                   eel_emu_nameshort,
                   eel_value) %>%
            mutate(eel_typ_id=case_when(eel_typ_id==17~"sumA",eel_typ_id==18~"sumF",eel_typ_id==19~"sumH")) %>%
            na.omit() %>%
            group_by(eel_typ_id,
                     eel_emu_nameshort) %>%
            summarize(minyear=min(eel_year), maxyear=max(eel_year), nb_value=n()) %>%
            mutate(range=paste(minyear, maxyear, sep = "-")) %>%
            select(eel_typ_id, eel_emu_nameshort, nb_value, range) %>%
            arrange(eel_emu_nameshort) %>%
            merge(emu_c %>% select(emu_nameshort) %>%
                    st_drop_geometry(), data_avail, by.y="emu_nameshort",by.x="eel_emu_nameshort",all.y=TRUE) %>%
            pivot_wider(names_from=eel_typ_id, values_from=c(range, nb_value),
                        names_glue="{eel_typ_id}_{.value}",
                        names_sort=TRUE)%>%
            select(-NA_range))
  
```

# EU: not reported country
```{r notans}
not_reported=country_p$cou_code[! country_p$cou_code %in% c(mortality$eel_cou_code)]
sort(country_p$cou_country[! country_p$cou_code %in% c(mortality$eel_cou_code)]) 
```

# Annexes 10

```{r downloadbiom}
biomass <- dbGetQuery(con,"select e.* from datawg.t_eelstock_eel e  where eel_qal_id in (0,1,2,3,4) and eel_typ_id in (13,14,15)")

```

# Data availability
## General overview
Tables showing the numbers of the range and numbers of years provided for each indicator by each country
```{r data2020biom}
flextable(biomass %>%
            mutate(eel_value=ifelse(is.na(eel_value & eel_missvaluequal == "NP"), 0,eel_value)) %>% 
            select(eel_typ_id,
                   eel_year,
                   eel_emu_nameshort,
                   eel_value) %>%
            mutate(eel_typ_id=case_when(eel_typ_id==13~"B0",eel_typ_id==14~"Bbest",eel_typ_id==15~"Bcurrent")) %>%
            na.omit() %>%
            group_by(eel_typ_id,
                     eel_emu_nameshort) %>%
            summarize(minyear=min(eel_year), maxyear=max(eel_year), nb_value=n()) %>%
            mutate(range=paste(minyear, maxyear, sep = "-")) %>%
            select(eel_typ_id, eel_emu_nameshort, nb_value, range) %>%
            arrange(eel_emu_nameshort) %>%
            merge(emu_c %>% select(emu_nameshort) %>%
                    st_drop_geometry(), by.y="emu_nameshort",by.x="eel_emu_nameshort",all.y=TRUE) %>%
            pivot_wider(names_from=eel_typ_id, values_from=c(range, nb_value),
                        names_glue="{eel_typ_id}_{.value}",
                        names_sort=TRUE) %>%
            select(-NA_range))
```


# not reported country
```{r notansbiom}
not_reported=country_p$cou_code[! country_p$cou_code %in% c(biomass$eel_cou_code )]
sort(country_p$cou_country[! country_p$cou_code %in% c(biomass$eel_cou_code)]) 
```



# Annex 11

```{r downloadrec}
folder="/home/hilaire.drouineau/Bureau/data_call/Annex11/"
list_files=list.files(path=folder,pattern="xls")
rec = do.call(rbind.data.frame, lapply(list_files,function(f) read_xlsx(paste0(folder,f),sheet="fisher_data")))
```

# Data availability
## General overview
Tables showing the numbers of the range and numbers of years provided for each indicator by each country

```{r recdata}
  

flextable(rec %>% 
            mutate(eel_value=ifelse(is.na(eel_value & eel_missvaluequal == "NP"), 0,eel_value)) %>% 
            select(eel_typ_name,
                   eel_year,
                   eel_emu_nameshort,
                   eel_value) %>%
            na.omit() %>%
            group_by(eel_typ_name,
                     eel_emu_nameshort) %>%
            summarize(minyear=min(eel_year), maxyear=max(eel_year), nb_value=n()) %>%
            mutate(range=paste(minyear, maxyear, sep = "-")) %>%
            select(eel_typ_name, eel_emu_nameshort, nb_value, range) %>%
            arrange(eel_emu_nameshort) %>%
            pivot_wider(names_from=eel_typ_name, values_from=c(range, nb_value),
                        names_glue="{eel_typ_name}_{.value}",
                        names_sort=TRUE))
  
```

# EU: not reported country
```{r notansrec}
not_reported=country_p$cou_code[! country_p$cou_code %in% c(rec$eel_cou_code)]
sort(country_p$cou_country[! country_p$cou_code %in% c(rec$eel_cou_code)]) 
```


# Annex 12

```{r downloadeffort}
folder="/home/hilaire.drouineau/Bureau/data_call/Annex12/"
list_files=list.files(path=folder,pattern="xls")
effort = do.call(rbind.data.frame, lapply(list_files,function(f) read_xlsx(paste0(folder,f),sheet="Effort")))
```

# Data availability
## General overview
Tables showing the numbers of the range and numbers of years provided for each indicator by each country

```{r effdata}
  

flextable(effort %>% 
            mutate(eel_value=ifelse(is.na(effort_value_number & eel_missvaluequal == "NP"), 0,effort_value_number)) %>% 
            select(eel_gear,
                   eel_year,
                   eel_emu_nameshort,
                   eel_value) %>%
            na.omit() %>%
            group_by(eel_emu_nameshort) %>%
            summarize(minyear=min(eel_year), maxyear=max(eel_year), nb_years=n_distinct(eel_year),nb_gears=n_distinct(eel_gear)) %>%
            mutate(range=paste(minyear, maxyear, sep = "-")) %>%
            select(eel_emu_nameshort, range,nb_years,nb_gears) %>%
            arrange(eel_emu_nameshort))
  
```

# EU: not reported country
```{r notanseff}
not_reported=country_p$cou_code[! country_p$cou_code %in% c(effort$eel_cou_code)]
sort(country_p$cou_country[! country_p$cou_code %in% c(effort$eel_cou_code)]) 
```



# Annex 13

```{r downloadmeth}
folder="/home/hilaire.drouineau/Bureau/data_call/Annex13/"
list_files=list.files(path=folder,pattern="xls")
```

# EU: not reported country
```{r notansmeth}
not_reported=country_p$cou_code[sapply(country_p$cou_code,function(cou) length(grep(cou,list_files))==0)]
sort(not_reported) 
```

Here are listed countries that have not sent data. 


# Annex 14

```{r downloaduse}
folder="/home/hilaire.drouineau/Bureau/data_call/Annex14/"
list_files=list.files(path=folder,pattern="xls")
use = do.call(rbind.data.frame, lapply(list_files,function(f) {
  print(f)
  read_xlsx(paste0(folder,f),sheet="new_data") %>%
    filter(eel_comment != "EXAMPLE ROW TO BE DELETED")}))
```

# Data availability
## General overview
Tables showing the numbers of the range and numbers of years provided for each indicator by each country

```{r usedata}
flextable(use %>% 
            mutate(eel_value=ifelse(is.na(Check_allocation & eel_missvaluequal == "NP"), 0,Check_allocation)) %>% 
            select(eel_year,
                   eel_emu_nameshort,
                   eel_value) %>%
            na.omit() %>%
            group_by(eel_emu_nameshort) %>%
            summarize(minyear=min(eel_year), maxyear=max(eel_year), nb_value=n()) %>%
            mutate(range=paste(minyear, maxyear, sep = "-")) %>%
            select(eel_emu_nameshort, nb_value, range) %>%
            arrange(eel_emu_nameshort)) 
  
```

# EU: not reported country
```{r notansuse}
not_reported=country_p$cou_code[sapply(country_p$cou_code,function(cou) length(grep(cou,list_files))==0)]
sort(not_reported) 
```

Here are listed countries that have not sent data. Other countries have reported either an empty file, either only missing values






# Annex 15

```{r downloadmeas}
folder="/home/hilaire.drouineau/Bureau/data_call/Annex15/"
list_files=list.files(path=folder,pattern="xls")
meas = unique(do.call(rbind.data.frame, lapply(list_files,function(f) {
  print(f)
  cou_code=gsub(".xlsx","",strsplit(f,split="_")[[1]][8])
  sheets=excel_sheets(paste0(folder,f))
  do.call(rbind.data.frame, lapply(sheets[grep("^INPUT",sheets)],function(s){
                                   read_xlsx(paste0(folder,f),sheet=s, guess_max=5000) %>%
                                     filter(startsWith(emu_name_short,cou_code) |
                                              (s=="INPUT_measures ES_Minh" & emu_name_short=="ES_Minh"))}))
  })) %>%
  filter(emu_name_short!="emu_name_short"))

```
# Data availability
## General overview
Tables showing the numbers of the range and numbers of years provided for each indicator by each country

```{r measdata}
flextable(meas %>% 
            mutate(id_bis=seq_len(nrow(meas))) %>%
            group_by(emu_name_short) %>%
            summarize(nb_measures=n(),
                      nb_fully_implemented=sum(progress=="Fully_implemented",na.rm=TRUE),
                      na_impact=sum(is.na(impact)),
                      na_effectiveness=sum(is.na(effectiveness_monitored)),
                      na_estimated_effect_size=sum(is.na(estimated_effect_size))
            ) %>%
            arrange(emu_name_short)
) 
```

# EU: not reported country
```{r notansmeas}
not_reported=country_p$cou_code[sapply(country_p$cou_code,function(cou) length(grep(cou,list_files))==0)]
sort(not_reported) 
```

Here are listed countries that have not sent data. 


