---
title: "RDBES - SG6"
date: "2025-01-24"
documentclass: report
format:
  docx:
    fig_caption: yes
    keep_md: yes
    reference-doc: "../../R/quarto/ICES_template.docx"
bibliography: "../../R/quarto/ICES.bib"
csl: "../../R/quarto/ices-journal-of-marine-science.csl"
lang: en
crossref:
  chapters: true
  fig-prefix: ''
  tbl-prefix: ''
  eq-prefix: ''
  ref-hyperlink: true
link-citations: true
link-bibliography: true
editor: source
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flextable)
library(ggplot2)
library(dplyr)
library(gt)
library(officer)

if (!dir.exists("images"))
  dir.create("images")

library(flextable)
library(gt)
library(knitr)
knit_print.flextable <- function (x, ...) {
    is_bookdown <- flextable:::is_in_bookdown()
    is_quarto <- flextable:::is_in_quarto()
    x <- flextable:::knitr_update_properties(x, bookdown = is_bookdown, quarto = is_quarto)
    if (is.null(knitr::pandoc_to())) {
        str <- flextable:::to_html(x, type = "table")
        str <- knitr:::asis_output(str)
    }
    else if (!is.null(getOption("xaringan.page_number.offset"))) {
        str <- knit_to_html:::knit_to_html(x, bookdown = FALSE, quarto = FALSE)
        str <- knitr:::asis_output(str, meta = html_dependencies_list(x))
    }
    else if (knitr:::is_html_output(excludes = "gfm")) {
        str <- knit_to_html:::knit_to_html(x, bookdown = is_bookdown, quarto = is_quarto)
        str <- knit_to_html:::raw_html(str, meta = html_dependencies_list(x))
    }
    else if (knitr:::is_latex_output()) {
        str <- flextable:::knit_to_latex(x, bookdown = is_bookdown, quarto = is_quarto)
        str <- flextable:::raw_latex(x = str, meta = unname(list_latex_dep(float = TRUE, 
            wrapfig = TRUE)))
    }
    else if (grepl("docx", knitr::opts_knit$get("rmarkdown.pandoc.to"))) {
        if (rmarkdown::pandoc_version() < numeric_version("2")) {
            stop("pandoc version >= 2 required for printing flextable in docx")
        }
        str <- flextable:::knit_to_wml(x, bookdown = is_bookdown, quarto = is_quarto)
        str <- gsub("</w:tbl>","</w:tbl><w:p></w:p>",str, fixed =  TRUE)
        str <- gsub('<w:pPr><w:pStyle w:val="Normal"/><w:jc w:val="left"/><w:pBdr><w:bottom w:val="none" w:sz="0" w:space="0" w:color="B7D1C3"/><w:top w:val="none" w:sz="0" w:space="0" w:color="B7D1C3"/><w:left w:val="none" w:sz="0" w:space="0" w:color="B7D1C3"/><w:right w:val="none" w:sz="0" w:space="0" w:color="B7D1C3"/></w:pBdr><w:spacing w:after="40" w:before="40" w:line="240"/><w:ind w:left="40" w:right="40" w:firstLine="0" w:firstLineChars="0"/></w:pPr>',
                    '<w:pPr><w:pStyle w:val="Table-Heading"/><w:jc w:val="left"/><w:spacing w:after="40" w:before="40" w:line="240"/><w:ind w:left="40" w:right="40" w:firstLine="0" w:firstLineChars="0"/></w:pPr>', str, fixed = TRUE)
        str <- gsub('<w:pPr><w:pStyle w:val="Normal"/><w:jc w:val="left"/><w:pBdr><w:bottom w:val="none" w:sz="0" w:space="0" w:color="000000"/><w:top w:val="none" w:sz="0" w:space="0" w:color="000000"/><w:left w:val="none" w:sz="0" w:space="0" w:color="000000"/><w:right w:val="none" w:sz="0" w:space="0" w:color="000000"/></w:pBdr><w:spacing w:after="40" w:before="40" w:line="240"/><w:ind w:left="40" w:right="40" w:firstLine="0" w:firstLineChars="0"/></w:pPr>',
                    '<w:pPr><w:pStyle w:val="Table-Text"/><w:jc w:val="left"/><w:spacing w:after="40" w:before="40" w:line="240"/><w:ind w:left="40" w:right="40" w:firstLine="0" w:firstLineChars="0"/></w:pPr>', str, fixed = TRUE)
        str <- knitr:::asis_output(str)
    }
    else if (grepl("pptx", knitr::opts_knit$get("rmarkdown.pandoc.to"))) {
        if (rmarkdown::pandoc_version() < numeric_version("2.4")) {
            stop("pandoc version >= 2.4 required for printing flextable in pptx")
        }
        str <- flextable:::knit_to_pml(x)
        str <- knitr:::asis_output(str)
    }
    else {
        plot_counter <- getFromNamespace("plot_counter", "knitr")
        in_base_dir <- getFromNamespace("in_base_dir", "knitr")
        tmp <- fig_path("png", number = plot_counter())
        in_base_dir({
            dir.create(dirname(tmp), showWarnings = FALSE, recursive = TRUE)
            save_as_image(x, path = tmp, expand = 0)
        })
        str <- include_graphics(tmp)
    }
    str
}

registerS3method(
  "knit_print", 'flextable', knit_print.flextable, 
  envir = asNamespace("flextable") 
  # important to overwrite {flextable}s knit_print
)



knit_print.gt_tbl <- function (x, ..., inline = FALSE) {
    if (gt:::knitr_is_rtf_output()) {
        x <- gt:::as_rtf(x)
    }
    else if (knitr::is_latex_output()) {
        x <- gt:::as_latex(x)
    }
    else if (gt:::knitr_is_word_output()) {
       str <- gsub("</w:tbl>","</w:tbl><w:p></w:p>", as_word(x), fixed = TRUE)
        x <- knitr::asis_output(paste("\n\n``````{=openxml}", str, 
            "``````\n\n", sep = "\n"))
    }
    else {
        x <- htmltools:::as.tags(x, ...)
    }
    knitr::knit_print(x, ..., inline = FALSE)
}



registerS3method(
  "knit_print", 'gt_tbl', knit_print.gt_tbl, 
  envir = asNamespace("gt") 
  # important to overwrite {gt}s knit_print
)


flextable2ICES <- function(x){
  x |>
    font(fontname = "Calibri", part = "all") |>
    fontsize(size = 8.5, part = "all") |>
    bold(part = "header") |>
    align(align = "left", part = "all") |>
    flextable::border(part = "all", 
                      border.top = fp_border(color = "black", width = 0.5),
                      border.bottom = fp_border(color = "black", width = 0.5)) |>
    bg(bg = "#B7D1C3", part = "header") |>
    style(pr_p=fp_par(padding = 2),
          part = "all") |>
    style(pr_p=fp_par(padding = 2,
                      border = fp_border(width = 0, color = "#B7D1C3", style = "none")),
          part = "header") |>
    fit_to_width(16/2.54)
}


```


```{r load_utilities, eval=TRUE, echo=FALSE,include=FALSE}

source("../../R/utilities/load_library.R")

#-----------------
# other libraries
#-----------------
load_package("hues")
load_package("readxl")
load_package("stringr")
load_package("reshape2")
load_package("tidyr") # unite cols in maps
load_package("rlang")
load_package("flextable")
load_package("officer")

load_package("sp")
#load_package("pool")
#load_package("DBI")
load_package("RPostgreSQL")
load_package("dplyr")
load_package("RColorBrewer")
load_package("sqldf")
load_package("scales")
load_package('stringr') # text handling
#load_package("XLConnect") # for excel
load_package("ggplot2") # for excel
load_package("gridExtra")
load_package("colorspace")
load_package("ggrepel")
load_package("patchwork")

load_package("viridis")
load_package("svglite")
load_package("leaflet.minicharts")
load_package("glue")
load_package("kableExtra")
load_package("yaml")
load_package("grid")
load_package("ggmagnify")
library("ggmagnify")
#install.packages("remotes")
#remotes::install_github("hughjonesd/ggmagnify")


# load functions ------------------------------------------------------------------------------------
# retrieve reference tables needed
# the shiny is launched from shiny_data_integration/shiny thus we need the ../
if (is.null(options()$sqldf.RPostgreSQL.user)) {
  wd <- getwd()
  setwd("../shiny_data_visualisation/shiny_dv")
  source("database_connection.R")
  source("database_reference.R")
  source("database_data.R")
  source("database_precodata.R")
  source("preco_diagram.R")
  source("graphs.R")
  source("maps.R")
  source("filter_and_group_functions.R")
  source("predict_missing.R")
  setwd(wd)
}

# loading datasets 

# this file is added to the ignore list, so ask for it in your own git before launching the app
#habitat_ref <- extract_ref("Habitat type")
#lfs_code_base <- extract_ref("Life stage")
##lfs_code_base <- lfs_code_base[!lfs_code_base$lfs_code %in% c("OG","QG"),]
#country_ref <- extract_ref("Country")
#country_ref <- country_ref[order(country_ref$cou_order), ]
#country_ref$cou_code <- factor(country_ref$cou_code, levels = country_ref$cou_code[order(country_ref$cou_order)], ordered = TRUE)

##have an order for the emu
#emu_ref <- extract_ref("EMU")
#emu_cou<-merge(emu_ref,country_ref,by.x="emu_cou_code",by.y="cou_code")
#emu_cou<-emu_cou[order(emu_cou$cou_order,emu_cou$emu_nameshort),]
#emu_cou<-data.frame(emu_cou,emu_order=1:nrow(emu_cou))
## Extract data from the database -------------------------------------------------------------------
# cedric 2020 : ATTENTION LOAD shiny_di version database_interaction version uses different names
#landings = extract_data("landings",quality=c(1,2,4),quality_check=TRUE)
#aquaculture = extract_data("aquaculture",quality=c(1,2,4),quality_check=TRUE)
#release = extract_data("release",quality=c(1,2,4),quality_check=TRUE)
# this file is added to the ignore list, so ask for it in your own git before launching the app
load("../shiny_data_visualisation/shiny_dv/data/maps_for_shiny.Rdata") 
# now data are generated by the script load_data_from_the_database.R
load("../shiny_data_visualisation/shiny_dv/data/ref_and_eel_data.Rdata")
## Download the colors by country

# coeffy increases ylim by about coeffy to let more space for subgraph
subplot <- function(grob, coeffy, minyear = 2009, xmin = 2000, xmax = Inf, ymin = 5000, ymax = Inf, ymaxbox = 5000) {
  sub <- grob +
    scale_x_continuous(limits = c(minyear, CY + 1), breaks = pretty_breaks()) +
    theme(
      legend.position = "none",
      rect = element_rect(fill = "transparent"),
      plot.background = element_rect(fill = "transparent", colour = NA)
    ) # ,
  # axis.title.y=element_blank(),
  # axis.text.y=element_blank(),
  # axis.ticks.y=element_blank())
  grob2 <- grob +
    annotate("rect", xmin = minyear + .5, xmax = CY + 0.5, ymin = 0, ymax = ymaxbox, fill = "transparent", col = "black") +
    scale_y_continuous(limits = c(0, pretty(layer_scales(grob)$y$range$range[2] * coeffy))) +
    annotation_custom(ggplotGrob(sub), xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax)
  return(grob2)
}

values <- c(
  RColorBrewer::brewer.pal(12, "Set3"),
  RColorBrewer::brewer.pal(12, "Paired"),
  RColorBrewer::brewer.pal(8, "Accent"),
  RColorBrewer::brewer.pal(8, "Dark2")
)
color_countries <- setNames(values, country_ref$cou_code)
library("hues")
swatch(colours()[1:10])
iwanthue(5, 0, 240, 0, 24, 0, 100, plot = TRUE) # shades
iwanthue(5, 0, 360, 0, 54, 67, 100, plot = TRUE) # pastel
iwanthue(5, 0, 360, 54, 180, 27, 67, plot = TRUE) # pimp
iwanthue(5, 0, 360, 36, 180, 13, 73, plot = TRUE) # intense
iwanthue(3, 0, 300, 60, 180, 73, 100, plot = TRUE) # fluoro
iwanthue(3, 220, 260, 12, 150, 0, 53, plot = TRUE) # blue ocean



#' fun.agg
#' aggregation of a table
#' @param X table to aggregate
#' @param conversion (1000 to convert kg to tons, 1e6 to convert
#' nb to millions)
#'
#' @return aggregated table
#' @export
#'
fun.agg <- function(X, conversion = 1000) {
  if (length(X) > 0) {
    round(sum(X) / conversion, ifelse(sum(X) > conversion, 1, 1))
  } else {
    sum(c(X, NA))
  }
}
```


# ToR h) Review RDBES/RDBFIS

Review RDBES/RDBFIS and i) identify the protocols used to collect landings data and ii) check if parameters/series recorded are consistent between DBES/RDBFIS and Metric DB and harmonize them

In order to facilitate an efficient and complete data collection it is of fundamental importance that databases (RDBES/RDBFIS & WGEEL METRIC database) follow FAIR principles. Therefore it is required to harmonize/implement respective structures across all platforms and develop/amend protocols to collect data

# DATSU

## Preparing the future datacall : EDMO and stations.

The locations of the sampling have to be recorded in the Station vocabulary. A station is a fixed location, where a sampling or data collecting instrument is deployed. Stations may be associated with a national or international project or with a monitoring programme. Station metadata provide additional information about the location where samples or observations are collected. For WGEEL stations are most often corresponding to series code. Station can change over time if for instance another organisation takes over monitoring at that location. [Stations](https://www.ices.dk/data/tools/Pages/Station-dictionary.aspx) are maintained in ICES . As part of the stations attributes, we need to identify the organisations doing the monitoring and register them as "marine organisations".

**EDMO** **(European Directory of Marine Organisations) :**

[EDMO](http://European%20Directory%20of%20Marine%20Organisations%20(EDMO)%20-%20SeaDataNet) is a reference directory maintained within the SeaDataNet infrastructure that contains standardized information about marine-related organizations, including research institutes, data centres, monitoring agencies, governmental bodies, and private organizations involved in marine and oceanographic activities. This Marine network needs to be extended to organisations working inland to monitor Migratory Fishes.

To register EDMO once for all our stations. For this we have created an EDMO [folder](https://icesit.sharepoint.com/sites/ExpertGroup/wgeel/2026%20Meeting%20Documents/Forms/AllItems.aspx?id=%2Fsites%2FExpertGroup%2Fwgeel%2F2026%20Meeting%20Documents%2F06%2E%20Data%2FEDMO&viewid=1a38b478%2Da003%2D4070%2D8001%2De5c505734bd7%22) in the sharepoint under data with one file per country, which contains two sheets :

- **National_edmo :**

The [EDMO](http://European%20Directory%20of%20Marine%20Organisations%20(EDMO)%20-%20SeaDataNet) will be needed to submit data through DATSU. This is the first table. Check in[ICES directory of EDMO codes](https://vocab.ices.dk/?ref=1398) or in the [EDMO](http://European%20Directory%20of%20Marine%20Organisations%20(EDMO)%20-%20SeaDataNet) web site to see if the national data reporter has an EDMO. If it's OK just fill in the EDMO code. Otherwise fill in the rest of the table with the institute coordinates.

If the EDMO exists but need to be changed, for instance the address has changed, please send mail to info\@maris.nl to create a new one and link it to the old one.

- **Station_edmo :**

This corresponds to the series that are currently in our database. This code refers to the institute responsible for the governance of a station. It might be different from the national edmo. The name, native name, Longitude and Latitude are those of the institute, not the station. 

```{r}
#| label: fig-tableedmo
#| fig-cap: "Information required for EDMO data integration"
#| fig-height: 6.3
#| fig-width: 6.3
imgfile <- file.path("images", "Table_structure.png") 
knitr::include_graphics(imgfile)
```

```{r}
#| label: fig-rdbes_workflow
#| fig-cap: "RDBES infographic summarizing the data flow for ICES working groups"
#| fig-height: 6.3
#| fig-width: 6.3
imgfile <- file.path("images", "RDBES infographic.jpg") 
knitr::include_graphics(imgfile)
```

Data from RDBES were requested from ICES data center. The objective is to build the data workflow (Figure @fig-rdbes_workflow)

# Testing the access to data

[icesRDBES dev](https://ices-tools-prod.r-universe.dev/icesRDBES) [icesRDBES prod](https://github.com/ices-tools-prod/icesRDBES) [icesRDBEScore](https://github.com/ices-tools-prod/icesRDBEScore)



```{r}
#| label: test-RDBES-API
#| eval: false
#| result: "hide"


#install.packages('icesRDBES', repos = c('https://ices-tools-prod.r-universe.dev', 'https://cloud.r-project.org'))
#install.packages("RDBEScore", repos = c("https://ices-tools-prod.r-universe.dev", "https://cloud.r-project.org"))
library(icesRDBES)
# shift to sandbox mode
#use_sboxrdbes(flag = TRUE)
rdbes_api()
# back to production mode
use_sboxrdbes(FALSE)
rdbes_api() 
# The rdbes_download_data can be used to download detailed RDBES data from RDBES and CEF data from RDBES.
#&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&
#dataType: “CS”, “CL”, “CE”, “SL”, “VD”, or “CEF”
#format: “SingleCsvFile” or “CsvFilePerTable”.
#hierarchies: “HCS”, “HCL”, “HCE”, “HSL”, “HVD”, "HNI", "HEN", or "HSN".
#data type filters: The specific filter object for the data type (e.g. csFilters).
#&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&

type_filters[["CL"]]

my_filters <- list(
  dataType = "CL",
  format = "SingleCsvFile",
  hierarchies = list("HCL"),
  CLFilters = list(
    "clVesselFlagCountry" = list("FR"),
    "clYear" = as.list(c("2024", "2025")),
    "clArea" = list("27.8.a"),
    "clSpeciesCode" = list("126281")
  )
)

dest_dir = "data"


rdbes_download_data(
  payload =  my_filters,
  dest_dir = dest_dir,
  production = getOption("rdbes.production"))


zip_path <- paste0(dest_dir, "/extracts")
dir.create(zip_path, showWarnings = FALSE)
downloaded_files <- list.files("data", pattern = ".zip",include.dirs = FALSE)
downloaded_files |> purrr::map(\(x) unzip(zipfile = x, exdir = "extracts"))    



```

## Second Title

This is ICES report [@ices2007]. A reference to the graph (Figure @fig-fig1).

```{r}
#| label: fig-fig1
#| fig-cap: "mon graph"
#| fig-height: 6.3
#| fig-width: 6.3

data(iris)
g <- ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point()
plotfile <- tempfile(fileext = ".png", tmpdir = "images")
ggsave(plotfile, g, width = 16/2.54, height = 16/2.54, dpi = 300)
knitr::include_graphics(plotfile)
```

and this is my table (Table @tbl-mytab).

```{r}
#| label: tbl-mytab
#| tbl-cap: mon tableau
flextable(iris |> slice(1:5)) |>
  flextable2ICES()
```

I can include ref to equation (equation @eq-mygreateq).

$$
\begin{equation}
E=m \cdot c^2 
\end{equation}
$$ {#eq-mygreateq}

## Title2

Nothing

```{r}
#| label: tbl-mytab2
#| tbl-cap: mon tableau 2
gt(head(iris)) |>
  opt_table_font(font = "Calibri",
                 size = gt::px(8.5)) |>
  tab_style(
    style = list(cell_fill("#B7D1C3"),
                 cell_text(weight = "bolder",
                           align = "left")),
    locations = cells_column_labels()
  ) |>
  tab_style(
    style = list(cell_text(align = "left")),
    locations = cells_body()) |>
  tab_options(table.layout = "auto",
              table.border.top.width = px(0.5),
              table.border.bottom.width = px(0.5),
              table.border.top.color = "#000000",
              table.border.bottom.color = "#000000") 
```

<br>

\newpage

::: {custom-style="Annex heading"}
Annex XX Using the RDBES
:::

**RDBES (Regional Database and Estimation System)** organizes fisheries sampling data into a set of 13 standardized hierarchies representing commercial fisheries, recreational fisheries, scientific surveys, and associated biological and laboratory sampling. The hierarchical model links observations from sampling programmes and fishing activities down to individual fish measurements and analyses, ensuring traceability of data and supporting statistically robust estimation procedures used in ICES stock assessments and fisheries advice.

## RDBES data types


In the **ICES Regional Database & Estimation System (RDBES)**, the main data types are:

| DataType | Description |
|------------------------------------|------------------------------------|
| **CS** | **Commercial Sampling**: detailed biological sampling data collected from commercial catches (length, age, sex, maturity, weight, etc.). |
| **CL** | **Commercial Landings**: aggregated information on landings by fleet, métier, species, area, time period, and other fisheries variables. |
| **CE** | **Commercial Effort**: fishing effort information associated with commercial fisheries (days at sea, fishing hours, gear deployment, vessel activity, etc.). |
| **SL** | **Species List**: reference table containing the species included in a sampling or reporting activity. It is used together with biological and catch records. |
| **VD** | **Vessel Details**: information describing vessels participating in fishing activities, such as vessel identifiers and characteristics. |
| **CEF** | **Catch, Effort and Frequency**: the standard RDBES upload format that combines catch data, fishing effort information, and length/species frequency distributions for fisheries monitoring and reporting. The RDBES upload API is specifically described as handling CEF data. |

For WGEEL the main use is currently **CL**.
Commercial Effort **CE** needs to be analysed in a second time.
Other data type will not be of use in the short term.

## RDBES hierarchies for commercial sampling

The following table summarizes the most commonly used **RDBES hierarchy codes** in ICES commercial fisheries sampling. These hierarchies define the pathway from the population of fishing activities to the biological observations collected from catches and individual fish. The hierarchy names are used throughout RDBES documentation and estimation workflows.

Articles of note : [data import RDBEScore](https://ices-tools-dev.github.io/RDBEScore/articles/v01a-data-import.html)

| Hierarchy | Name | Purpose |
|------------------------|------------------------|------------------------|
| **H** | Commercial Catch Sampling | Describes sampling of commercial catches, linking fishing activity, catch categories, and sampled catches. It is the core hierarchy for raising biological samples to catches. |
| **HCL** | Commercial Length Sampling | Used for collection of length-frequency data from commercial fisheries. Individual fish lengths are measured from sampled catches. |
| **HCE** | Commercial Age/Biological Estimation | Extends length sampling with biological measurements such as age, weight, sex, and maturity, supporting age-length-key based estimation. |
| **HSL** | Survey Length Sampling | Records length-frequency measurements collected during scientific surveys rather than commercial fisheries. |
| **HVD** | Vessel Details Hierarchy | Stores vessel-level information used to characterize the sampling frame and fishing effort associated with commercial fishing operations. |
| **HNI** | Individual Biological Measurements | Contains observations on individual fish, such as length, weight, sex, maturity stage, and other biological variables. |
| **HEN** | Age and Enhanced Biological Sampling | Hierarchy for samples requiring more detailed biological analyses, including age determination and related laboratory observations. |
| **HSN** | Survey Biological Sampling | Survey-based hierarchy including individual fish biological observations collected during scientific surveys and monitoring programmes. |


::: {custom-style="Annex heading"}
References
:::
