---
title: "biometry_individual"
author: "ICES Data Group"
date: "12/09/2022"
bibliography: biometry.bib
csl: "../Rmarkdown/ices-journal-of-marine-science.csl"
output: 
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    reference_docx: "../Rmarkdown/ICES_template.docx"
params:
  load_data: FALSE
  run_rq: FALSE
---

# Individual biometrics data

** All graph and table are given to illustrate the data provided to th WGEEL through the data. They should not be taken
as a real analysis of trends, biological phenomenon ... **

```{r setup, include=FALSE}
source("../utilities/load_library.R")
source("biometry_individual_functions.R")

knitr::opts_chunk$set(echo = FALSE, warning=TRUE, message=FALSE, error=FALSE, fig.width=14.9/2.54, dpi=150)

load_library("readxl")
load_library("sf")
load_library("rnaturalearth")
load_library("getPass")
load_library("dplyr")
load_library("ggplot2")
load_library("Kendall")
load_library("RPostgres")
load_library("ggmap")
load_library("hues")
load_library("RPostgres")
load_library("flextable")
load_library("yaml")
load_library("tidyr")
load_library("lubridate")
load_library("stringr")
load_library("quantreg")
load_library("ggridges")
load_library("scales")
load_library(("ggpubr"))

if(Sys.info()["user"]=="hilaire.drouineau"){
  allometry=read_excel("~/Bureau/slopesintercepts.xlsx")
  setwd("~/Documents/Bordeaux/migrateurs/WGEEL/github/wg_WGEEL/R/biometry_analysis/")
}

colorpalette=cbf_1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73", 
           "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

if(params$load_data)
{
	# db connection
	cred=read_yaml("../../credentials.yml")
	con_wgeel = dbConnect(Postgres(), dbname=cred$dbname,host=cred$host,port=cred$port,user=cred$user, password=getPass())
	
	## download data from the database
	biometry_individual_series=dbGetQuery(con_wgeel,"with sel as(SELECT d.*, t_series.*, mty_name FROM datawg.t_metricindseries_meiser d, datawg.t_fishseries_fiser t_series, ref.tr_metrictype_mty WHERE mty_id=mei_mty_id AND mei_fi_id = fi_id) 
	select sel.*, ser_nameshort, ser_cou_code, ser_x,ser_y,ser_emu_nameshort, ser_hty_code,ser_lfs_code,gea_name_en, sam_samplingtype,t_series_ser.ser_qal_id from sel, datawg.t_series_ser, ref.tr_gear_gea, ref.tr_samplingtype_sam where ser_id=fiser_ser_id and ser_sam_gear=gea_id and ser_sam_id=sam_id")
	
	biometry_individual_series<-biometry_individual_series %>% filter(fi_id!=421454)
	
	biometry_individual_sampling=dbGetQuery(con_wgeel,"with sel as(SELECT d.*, t_samp.*, mty_name FROM datawg.t_metricindsamp_meisa d, datawg.t_fishsamp_fisa t_samp, ref.tr_metrictype_mty WHERE mty_id=mei_mty_id AND mei_fi_id = fi_id) 
	select * from sel, datawg.t_samplinginfo_sai where sai_id=fisa_sai_id")
	
	cou_ref=dbGetQuery(con_wgeel,"select cou_code, cou_order from ref.tr_country_cou")
	cou_ref= cou_ref[order(cou_ref$cou_order), ]
	
	values=c(RColorBrewer::brewer.pal(12,"Set3"),
	    RColorBrewer::brewer.pal(12, "Paired"), 
	    RColorBrewer::brewer.pal(8,"Accent"),
	    RColorBrewer::brewer.pal(8, "Dark2"))
	color_countries = setNames(values,cou_ref$cou_code)
	
	## preparing the data to be exploited
	
	  ## individual series
	
	data_ind_series = biometry_individual_series %>% 
		select(ser_id = fiser_ser_id, year = fi_year,date=fi_date,  fi_id, country=ser_cou_code, comment = fi_comment, quality = mei_qal_id, mty_name, mei_value,ser_nameshort, coord_x = ser_x, coord_y = ser_y,ser_emu_nameshort, ser_hty_code,ser_lfs_code, gea_name_en, sam_samplingtype,ser_qal_id) %>%
		pivot_wider(names_from = mty_name, values_from = mei_value)
	
	data_ind_series$ser_lfs_code=factor(as.character(data_ind_series$ser_lfs_code),levels=c("G","GY","Y","S"))
	data_ind_series$month<-format(data_ind_series$date,"%m")
	data_ind_series$country<-factor(data_ind_series$country,levels=cou_ref$cou_code,ordered=TRUE)
	
	  ## individual sampling data
	
	data_ind_samp = biometry_individual_sampling %>% 
	  mutate(year = ifelse(is.na(fi_year),year(fi_date), fi_year)) %>% 
		select(ser_id = fisa_sai_id, year, date=fi_date,  fi_id=mei_fi_id, coord_x=fisa_x_4326, coord_y=fisa_y_4326, fi_lfs_code, country=sai_cou_code, comment = fi_comment, quality = mei_qal_id, mty_name, mei_value,ser_nameshort=sai_name,ser_emu_nameshort=sai_emu_nameshort, ser_hty_code=sai_hty_code,sai_samplingstrategy) %>%
		pivot_wider(names_from = mty_name, values_from = mei_value)
	
	data_ind_samp$fi_lfs_code=factor(as.character(data_ind_samp$fi_lfs_code),levels=c("G","GY","Y","YS","S"))
	data_ind_samp$month<-format(data_ind_samp$date,"%m")
	data_ind_samp$country<-factor(data_ind_samp$country,levels=cou_ref$cou_code,ordered=TRUE)
	
	    ## total data
	
	total_individual= bind_rows(
		data_ind_series %>% as_tibble() %>%
			select(country, EMU = ser_emu_nameshort, ser_nameshort, coord_x, coord_y, year,month, lengthmm, weightg,eye_diam_meanmm, pectoral_lengthmm, ageyear,differentiated_proportion, female_proportion, habitat = ser_hty_code, life_stage = ser_lfs_code, gear = gea_name_en) %>%
			mutate(source = "series"),
	
		data_ind_samp %>% as_tibble() %>%
			mutate(commercial = str_detect(sai_samplingstrategy, "ommercial") | str_detect(sai_samplingstrategy, "CF")) %>%
			select(country, EMU = ser_emu_nameshort, ser_nameshort, coord_x, coord_y, year,month, lengthmm, weightg,eye_diam_meanmm, pectoral_lengthmm, ageyear,differentiated_proportion, female_proportion, habitat = ser_hty_code, life_stage = fi_lfs_code, commercial) %>% mutate(gear = "unkonwn", source = "sampling") 
	)	%>% 
		mutate(length_class_cm = as.integer(as.character(cut(lengthmm, breaks = seq(0, 1350, 10), labels = seq(0, 1340, 10) + 5)))/10)
	
	total_individual$country<-factor(total_individual$country,levels=cou_ref$cou_code,ordered=TRUE)
	
	#save(cou_ref, data_ind_series, data_ind_samp, color_countries, total_individual, biometry_individual_sampling, biometry_individual_series, file = "ind_biom.RData")
	dbDisconnect(con_wgeel)
} else {
	load("ind_biom.RData")
	warnings("The data was loaded with a RData file, please turn params `load_data` to TRUE if you want uptodate data")
}

```


```{r mapfunctions,echo=FALSE}

# compute the summary of data

stats_data_coord = total_individual %>% group_by(source,country,EMU, coord_x, coord_y,habitat,life_stage) %>%
	summarize(series=paste(unique(EMU),collapse=", "),
		n_lengthmm=(sum(!is.na(lengthmm))),
		n_bio_weight=(sum(!is.na(weightg))),
		n_female_proportion=(sum(!is.na(female_proportion))),
		n_pectoral_length=(sum(!is.na(pectoral_lengthmm))),
		n_eye_diam_meanmm=(sum(!is.na(eye_diam_meanmm))),
		n_ageyear=(sum(!is.na(ageyear))),
		n_differentiated_proportion=(sum(!is.na(differentiated_proportion)))) %>%
	filter((n_lengthmm + n_bio_weight + n_female_proportion + n_pectoral_length + n_eye_diam_meanmm + n_ageyear + n_differentiated_proportion)>0) %>%
	arrange(source,life_stage,country,habitat,EMU)

```

## Available data 

The table (**Annex**) describes the available individual biometric data from Appendix 1,2,3 (series) and 10 (sampling).

```{r available_data, include = TRUE }
#TODO: make the column's title more explicit (true title instead of variable names)

stats_data= total_individual %>% group_by(source, country, EMU, ser_nameshort, habitat, life_stage) %>%
  summarize(
            n_lengthmm=(sum(!is.na(lengthmm))),
            n_bio_weight=(sum(!is.na(weightg))),
            n_female_proportion=(sum(!is.na(female_proportion))),
            n_pectoral_length=(sum(!is.na(pectoral_lengthmm))),
            n_eye_diam_meanmm=(sum(!is.na(eye_diam_meanmm))),
            n_ageyear=(sum(!is.na(ageyear))),
            n_differentiated_proportion=(sum(!is.na(differentiated_proportion)))) %>%
  filter((n_lengthmm + n_bio_weight + n_female_proportion + n_pectoral_length + n_eye_diam_meanmm + n_ageyear + n_differentiated_proportion)>0) %>%
  arrange(source,life_stage,country,habitat,EMU)

ft = flextable(stats_data)
ft = set_caption(ft, "Number of avaible data for each biometry metrics")

autofit(ft)

```

## Length data

```{r lengthdecriptivegraphs, include=TRUE, fig.cap = "Length distribution par life stage and source of data"}
## length frequency

	ggplot(total_individual %>% mutate(type_sampling = ifelse(is.na(commercial), "Series", ifelse(commercial, "Fisheries sampling", "Scientific sampling")))) + aes(x = length_class_cm, color = life_stage) +
		geom_density() + facet_grid(life_stage ~type_sampling, scales = "free_y") +
		scale_color_discrete(guide = "none") +
		xlab("Length (cm)") + ylab("") + theme_classic() + theme(
			axis.text.y = element_blank(),
			axis.ticks = element_blank(),
			axis.text.x = element_text(angle = 90),
			axis.ticks.x = element_line()
		) + coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 
```

```{r lengthdecriptivegraphs-month, include=TRUE, fig.cap = "** not for the report ** Length distribution by month and by life stage. Point is the median, bar gives 5% and 95% quantile.", fig.height=20/2.54}
## length by month

total_lengthmmg<-total_individual %>% filter(!is.na(month),life_stage=="G",!is.na(lengthmm))%>%group_by(month)%>%summarise(q50=quantile(lengthmm,0.5),q5=quantile(lengthmm,0.05),q95=quantile(lengthmm,0.95))

total_lengthmmy<-total_individual %>% filter(!is.na(month),life_stage=="Y", !is.na(lengthmm))%>%group_by(month)%>%summarise(q50=quantile(lengthmm,0.5),q5=quantile(lengthmm,0.05),q95=quantile(lengthmm,0.95))

total_lengthmms<-total_individual %>% filter(!is.na(month), year>1,life_stage=="S",!is.na(lengthmm))%>%group_by(month)%>%summarise(q50=quantile(lengthmm,0.5),q5=quantile(lengthmm,0.05),q95=quantile(lengthmm,0.95))

gridExtra::grid.arrange(

ggplot(total_lengthmmg, aes(x=as.factor(month),y=q50)) + 
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ggtitle("Glass eel")+ 
  theme(axis.text.x = element_text(size = 12, angle = 90))+ 
  xlab("Month")+
  ylab("Length (mm)") + theme_classic(),

ggplot(total_lengthmmy, aes(x=as.factor(month),y=q50)) + 
  geom_pointrange(aes(ymin = q5, ymax = q95)) +ggtitle("Yellow eel")+ 
  theme(axis.text.x = element_text(size = 12, angle = 90))+ 
  xlab("Month")+
  ylab("Length (mm)") + theme_classic(),

ggplot(total_lengthmmy, aes(x=as.factor(month),y=q50)) + 
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ggtitle("Silver eel")+ 
  theme(axis.text.x = element_text(size = 12, angle = 90))+ 
  xlab("Month")+
  ylab("Length (mm)") + theme_classic(),

nrow = 3
)

```

** NO yellow eel to be checked **

```{r lengthdescriptivegraphs, include=TRUE, fig.cap = "Length distribtion by country and by life stage"}
#TODO: add the number of samples for each line

total_length<-total_individual %>% filter(!is.na(lengthmm), life_stage %in% c("Y","S")) %>%
	mutate(life_stage  = case_when(life_stage =="Y" ~"Yellow eel", life_stage =="S" ~ "Silver eel")) %>%
	mutate(country = factor(country, levels = cou_ref$cou_code, ordered=TRUE))

ggplot(total_length) + aes(x = lengthmm, y=country, fill = country, alpha=0.5)  + 
  geom_density_ridges( scale = 3, rel_min_height = 0.005, bandwidth = 5)+ 
  facet_grid(vars(life_stage)) +
  scale_fill_manual("Country",values=color_countries[names(color_countries) %in% unique(total_age$country)], drop = TRUE, guide = "none")+
  scale_alpha(guide="none") +
  xlab("Length (mm)") +
  ylab("Country") +
  scale_y_discrete(limits=rev)  + theme_classic() +
  coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 

```

### Map of available length data by stage

Only the data series with more than 5 individual size measurements have been taken into account to make these maps

```{r maplength,echo=TRUE}

gridExtra::grid.arrange(
  plot_map_bio_emu("length","G",only_legend="no"),
  plot_map_bio_emu("length","Y",only_legend="no"),
  plot_map_bio_emu("length","S",only_legend="no"),
  plot_map_bio_emu("length","S",only_legend="yes"),

  nrow=2,
  ncol=2
)




```








## Weight data

```{r weightdecriptivegraphs, include=TRUE, fig.cap = "Weight distribution by year and by life stage. Point is the median, bar gives 5% and 95% quantile.", fig.height=20/2.54}

graph_weight = function(lifeStage = "G")
{
	lfs = switch(lifeStage,
		"G" = "Glass eel" ,
		"Y" = "Yellow eel",
		"S" = "Silver eel"
		)
		
		total_weightg<-total_individual %>% 
			filter(!is.na(weightg), !is.na(year), year>1, life_stage== lifeStage) %>%
			group_by(year) %>%
			summarise(q50=quantile(weightg, 0.5), q5=quantile(weightg,0.05), q95=quantile(weightg, 0.95))
		
		myplot = ggplot(total_weightg, aes(x=as.factor(year), y=q50)) + 
			geom_pointrange(aes(ymin = q5, ymax = q95)) + ggtitle(lfs)  + theme_classic()+ 
			theme(axis.text.x = element_text(angle = 90))+ 
			xlab("Year")+ylab("Weight (g)")
		
		return(myplot)
}


gridExtra::grid.arrange(
	graph_weight("G"),
	graph_weight("Y"),
	graph_weight("S"),
	nrow = 3
)

```

### Glass eel map

```{r glassmapweight,echo=TRUE}

plot_map_bio_emu("weight","G")

```

### Yellow eel map

Similarly to length, a pattern is visible for weight of monitored standing stock yeelow eel. This is confirmed by the
Kendall correlation test (tau=

. There are not enougth time sex disaggregated data to detect sex-specific length-pattern.

```{r yellowweighthmap,echo=TRUE}

plot_map_bio_emu("weight","Y")

```

### Silver eel map

The Kendall correlation test does not detect any spatial pattern (tau= .

```{r silverweightmap,echo=TRUE}

plot_map_bio_emu("weight","S")

```

## Length-Weight relationship


```{r lengthweightlfs, include=TRUE, fig.cap = "Length-Weight relationship by life stage and source"}

ggplot(total_individual %>% mutate(source = case_when(source == "sampling" ~ "Sampling", source == "series" ~ "Series"))) +
	aes(x=lengthmm, y=weightg) + 
	geom_point() +
  	facet_grid(vars(life_stage), vars(source),scale="free")+
  	theme_classic()+xlab("Length (mm)") + ylab("Weight (g)") +
  	xlim(c(0, NA)) + ylim(c(0, NA))

```

```{r lengthweightrelationship, include=TRUE, fig.cap = "Lenght-Weight relationship by life stage (point) and 75% quantile regression (line)"}

# all data

## prepare the data
reg_series_data <- 	total_individual %>%
	filter(!is.na(weightg), !is.na(lengthmm), 
		weightg>0, lengthmm>100,
		life_stage %in% c("Y","S"), !is.na(life_stage)
		) %>%
	mutate(country = factor(country, levels=cou_ref$cou_code, ordered=TRUE))

if(params$run_rq)
{
	reg_w_series = rq(log(reg_series_data$weightg) ~ log(reg_series_data$lengthmm), tau= 0.75)
#	save(reg_w_series, file = "reg_w_series.RData")
} else {
	load("reg_w_series.RData")
}

#calcul de Ws
reg_series_data$ws = exp(predict(reg_w_series, newdata = reg_series_data))

#calcul de Wr
reg_series_data$wr = reg_series_data$weightg / reg_series_data$ws *100

reg_series_data = reg_series_data %>% mutate(life_stage = case_when(life_stage =="Y" ~"Yellow eel", life_stage =="S" ~ "Silver eel"))

## regression with all data

ggplot(reg_series_data) +
	aes(lengthmm, ws) +
	geom_point(aes(lengthmm, weightg, colour=life_stage), size = 1, alpha = 0.3) + 
	geom_line() +
	scale_color_discrete("Life stage") +
	theme_classic() + xlab("Length (mm)") + ylab("Weight (g)") +
	coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0, NA)) +
	guides(color = guide_legend(override.aes = list(size = 5) ) ) 

```

[@blackwellRelativeWeightWr2000]

```{r lengthweightrelationship2, include=TRUE, fig.cap = "Relative Weight relationship by life stage"}
## representation of the results with all data

ggplot(reg_series_data) +
	aes(lengthmm, wr, colour=life_stage) +
	geom_point(alpha = 0.3, size = 1) +
	geom_hline(yintercept = c(25,200)) + 
	scale_y_continuous(trans = "log10", labels = scales::label_number(), breaks = c(0.1, 1, 10, 25, 100, 200, 1000, 10000)) +
	scale_color_discrete("Life stage") +
	theme_classic() + xlab("Length (mm)") + ylab("Relative weight (Wr)") +
	coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0.1, NA)) +
	guides(color = guide_legend(override.aes = list(size = 5) ) ) 

```

restricted to 25 -200

```{r lengthweightrelationship3, include=TRUE, fig.cap = "Relative Weight relationship by life stage, country and source"}

#n_total<-nrow(reg_series_data)
#
#n_inconsistent<-nrow(reg_series_data[reg_series_data$wr<25 | reg_series_data$wr>200,])

## boxplot of the resultat with only consistant data

reg_data_cons<-reg_series_data %>%
	filter(wr>25 & wr<200) %>% 
	mutate(source = case_when(source == "sampling" ~ "Sampling", source == "series" ~ "Series"))

ggplot(reg_data_cons) +aes(country, wr, fill=country) +
	geom_boxplot() + 
	scale_fill_manual(name = "Country", values=color_countries[names(color_countries) %in% unique(reg_series_data$country)], drop = TRUE)+
	geom_hline(yintercept =100) + facet_grid(vars(source),vars(life_stage))+
	theme_classic() + xlab("Country") + ylab("Relative weight (Wr)") +
	coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0.1, NA)) +
	guides(color = guide_legend(override.aes = list(size = 5) ) ) 

```

```{r rawdata, include=TRUE}

## Gear effect on size-weight
graph_LW = function(lifeStage = "G")
{
	mydata = data_ind_series %>% filter(ser_lfs_code == lifeStage)
	
	lfs = switch(lifeStage,
		"G" = "Glass eel" ,
		"GY" = "Glass & Yellow eel",
		"Y" = "Yellow eel",
		"S" = "Silver eel"
	)
	
	ggplot(mydata) +
		aes(x = lengthmm, y = weightg, color = country) + 
		geom_point(alpha = 0.3) +
		facet_grid(vars(gea_name_en))+
		scale_color_manual(name = "Country", values=color_countries[names(color_countries) %in% unique(mydata$country)], drop = TRUE) +
		theme_bw()+
		ggtitle(lfs)+xlab("Length (mm)")+ylab("Weight (g)") +
		theme_classic()  +
		coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0.1, NA)) +
		guides(color = guide_legend(override.aes = list(size = 5) ) ) 
}

graph_LW("G")
graph_LW("GY")
graph_LW("Y")
graph_LW("S")

## lfs effect on size-weight

ggplot(data_ind_series, aes(x=lengthmm,y=weightg))+geom_point()+
  facet_wrap(.~ser_lfs_code,scale="free")+
  theme_bw()+ggtitle("All gears")+xlab("Length (mm)")+ylab("Weight (g)")

## length by gear and year

stat_length_g<- data_ind_series %>% filter(ser_lfs_code == "G") %>%
    group_by(year,gea_name_en,country) %>%
    dplyr::summarize(Mean = mean(weightg, na.rm=TRUE), sd=sd(weightg,na.rm=TRUE))

stat_length_y<- data_ind_series %>% filter(ser_lfs_code == "Y") %>%
    group_by(year,gea_name_en,country) %>%
    dplyr::summarize(Mean = mean(lengthmm, na.rm=TRUE), sd=sd(lengthmm,na.rm=TRUE))

ggplot(stat_length_g, aes(year, Mean))+ geom_pointrange(aes(ymin = Mean-sd, ymax = Mean+sd))+ 
  facet_grid(vars(gea_name_en),vars(country)) + theme_bw()+xlab("Year")+ylab("Mean length (mm)") +ggtitle("Glass eel")

ggplot(stat_length_y, aes(year, Mean))+ geom_pointrange(aes(ymin = Mean-sd, ymax = Mean+sd))+ 
  facet_grid(vars(country),vars(gea_name_en)) + theme_bw()+xlab("Year")+ylab("Mean length (mm)") +ggtitle("Yellow eel")

```

The point for silver eel greater than 1250 mm appear as an outlier and is excluded from the analysis. Weights should be
checked.

For the spatial analysis, we only considered ser_hty_code x EMU x lfs_code where at leat 5 data points were available
(they may come from different time series or years).


## Age

```{r agedescriptivegraphs, include=TRUE, fig.cap = "Age distribtion by country and by life stage"}
#TODO: add the number of samples for each line

total_age<-total_individual %>% filter(!is.na(ageyear), life_stage %in% c("Y","S")) %>%
	mutate(life_stage  = case_when(life_stage =="Y" ~"Yellow eel", life_stage =="S" ~ "Silver eel"))

total_age$country<-factor(total_age$country,levels=cou_ref$cou_code,ordered=TRUE)

ggplot(total_age) + aes(x = ageyear, y=country, fill = country, alpha=0.5)  + 
  geom_density_ridges( scale = 3, rel_min_height = 0.005, bandwidth = 1)+ 
  facet_grid(vars(life_stage)) +
  scale_fill_manual("Country",values=color_countries[names(color_countries) %in% unique(total_age$country)], drop = TRUE, guide = "none")+
  scale_alpha(guide="none") +
  xlab("Age (year)") +
  ylab("Country") +
  scale_y_discrete(limits=rev)  + theme_classic() +
  coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 

```

### Yellow eel map

Too few data were correlected regarding sex to draw any conclusions regarding differences in sex-ratios among locations.

```{r yellowsagemap,echo=TRUE}
plot_map_bio_emu("age","Y")
```

### Silver eel map

```{r silveragemap, echo=TRUE}

plot_map_bio_emu("age","S")

```


## Growth

```{r agelengthy, fig.height=20/2.54, include=TRUE, fig.cap = "Length distribution by age and country for yellow eels"}

age_lengthy<-total_individual %>% filter(!is.na(ageyear), !is.na(lengthmm), life_stage=="Y") %>% 
		mutate(age_class = factor(ifelse(ageyear>19, "20+", ageyear), levels=c(0:19,"20+"), ordered=TRUE))

ggplot(age_lengthy) + aes(x = lengthmm, y=age_class, fill=country, alpha=0.5)  + 
  geom_density_ridges( scale = 3, rel_min_height = 0.005, bandwidth = 4)+ 
  scale_alpha(guide="none")+
  scale_fill_manual("Country",values=color_countries[names(color_countries) %in% unique(age_lengthy$country)], drop = TRUE)+
  ylab("Age (year)") +
  xlab("Length (mm)") +
  theme_classic() +
  coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 

```

```{r agelengths, fig.height=20/2.54, include=TRUE, fig.cap = "Length distribution by age and country for silver eels"}

age_lengths<-total_individual %>% filter(!is.na(ageyear), !is.na(lengthmm), life_stage=="S") %>% 
		mutate(age_class = factor(ifelse(ageyear>19, "20+", ageyear), levels=c(0:19,"20+"), ordered=TRUE))

ggplot(age_lengths) + aes(x = lengthmm, y=age_class, fill=country, alpha=0.5)  + 
  geom_density_ridges( scale = 3, rel_min_height = 0.005, bandwidth = 4)+ 
  scale_alpha(guide="none")+
  scale_fill_manual("Country",values=color_countries[names(color_countries) %in% unique(age_lengths$country)], drop = TRUE)+
  ylab("Age (year)") +
    xlab("Length (mm)") + 
    theme_classic() +
	coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 

```

## Sex

```{r sexratio, include=TRUE, fig.cap = "Sex distribution by life stage and country"}

sexratio<-total_individual %>%
  mutate(sex=ifelse(is.na(female_proportion), "unknown", ifelse(female_proportion==1, "Female", "Male")))%>% 
  filter(life_stage %in% c("Y","YS","S"), sex != "unknown") %>%
  mutate(life_stage = case_when(life_stage =="Y" ~"Yellow eel", life_stage =="S" ~ "Silver eel", life_stage == "YS" ~ "Yellow or Silver eel"))

	ggplot(sexratio) + aes(country) +
	geom_bar(aes(fill = sex)) + 
	  facet_grid(vars(life_stage), scales = "free_y") +
	  scale_fill_discrete("Sex") +
	  theme_classic() + xlab("Country") + ylab("Count") + coord_cartesian(expand = FALSE) 

```

### Yellow eel map

Too few data were correlected regarding sex to draw any conclusions regarding differences in sex-ratios among locations.

```{r yellowsexratiomap,echo=TRUE}
plot_map_bio_emu("sexratio","Y")
```

### Silver eel map

The number of points is again very limited and no significant spatial pattern is detected (tau= .

```{r silversexratiomap,echo=TRUE}

plot_map_bio_emu("sexratio","S")

```

## To be changed in next data call

- add a life stage column in Annex 1-3 in individual biometrics (** same for group?**)

# Maps
As an exploratory analysis, we computed average biometry (length, weight, sex-ratio) per stage, habitat type and sex (when available). All years and time series are pooled together. To explore the existance of spatial pattern, we carried out Mann Kendall tests to detect correlations between the considered traits and spatial positions of the biometry measurements. Here, spatial positions are characterised by 
distances as the crow flies from Gibraltar: this distance is used as a proxy of lattitudes patterns which is known to be correlated to life history traits [@kettle2011; @vollestad1992], but allows the consideration of the Mediterranean basin.








## Silver Eel




The length of monitored silver eel appear to increase with the distance to Gibraltar. This is confirmed by the Kendall correlation test (tau=
. There are not enougth time sex disaggregated data to detect sex-specific length-pattern.







## Distribution of slopes of length-weight regression

Linear regression between logtransformed length and weights were carried out to compare allometric relationships among time series. The slope informs on the allometric growth: higher slope means that the fish becomes heavier and suggests good growth condition. The following maps display the results for all stages. No clear spatial pattern is detected. The Bann river displays very pronounced slopes: while references as a mixed of glass-eel and yellow-eel, reported length were always smaller than 70mm but heavy compared to other sites (max: 0.41g, mean: 0.34g). 


```{r lengthweightmap,echo=TRUE}
#ggmap(background_map_transparent)+
#  geom_point(data=allometry,
#             aes(shape=Stage,fill=slopes,x=Ser_x,y=Ser_y),col="black")+
#  scale_fill_viridis_c("Slope")+
#  scale_shape_manual("Stage",values=c(21,22,24))+
#  theme_bw()

```

```{r lengthweightmapperstage,echo=TRUE}
#allometry$Stage=factor(as.character(allometry$Stage),levels=c("GY","Y","S"))
#ggmap(my_map)+
#  geom_point(data=allometry,
#             aes(col=slopes,x=Ser_x,y=Ser_y))+
#  scale_color_viridis_c("Slope")+
#  facet_wrap(.~Stage,nrow=2)+
#  theme_bw()
#
#for (s in c("GY","Y","S")){
#  print(ggmap(my_map)+
#          geom_point(data=subset(allometry,Stage==s),
#             aes(col=slopes,x=Ser_x,y=Ser_y))+
#          geom_point(data=subset(allometry,Stage==s),
#             aes(x=Ser_x,y=Ser_y),pch=1)+
#  scale_color_viridis_c("Slope")+
#  theme_bw() + ggtitle(s))
#  }


```


# Temporal trends
In this section, we explore the existence of temporal trends in biometry. For that purpose, we computed average biometry per EMU, habitat and year. Then we carry out Mann Kendall trend tests to detect time series with significant monotonic trend. We only keep EMUxHTY that have data for at least 5 years.

## Yellow Eel

```{r}
#mean_biom_hty_emuyearY=mean_biom_hty_emuyear %>%
#  filter(ser_lfs_code=="Y")
```


```{r functionstemporal,echo=FALSE}
#table_temporal_trend = function(var,stage,sex=NULL){
#  data=mean_biom_hty_emuyear %>%
#    filter(ser_lfs_code==stage)
#
#  var_name=switch (var,
#    "length" = "lengthmm",
#    "weight" = "bio_weight",
#    "sexratio" = "female_proportion"
#  )
#  
#  ylab=switch (var,
#    "length" = "Length (mm)",
#    "weight" = "Weight (g)",
#    "sexratio" = "Sex ratio (% female)"
#  )
#  
#  if (!is.null(sex)){
#    var_name=paste(var_name,sex,sep="_")
#    ylab=paste(ifelse(sex=="m",
#                      "Male",
#                      "Female"),
#               ylab,
#               sep=" ")
#  }
#  data <- data %>%
#    filter(!(is.na(!!as.symbol(var_name))))
#  
#  kept = data %>%
#    group_by(ser_emu_nameshort,ser_hty_code) %>%
#    filter(!is.na(!!as.symbol(var_name))) %>%
#    summarise(count=n()) %>%
#    filter(count>=5)
#  tmp=NA
#  if(nrow(kept)>0){
#    tmp=inner_join(kept,data) %>%
#    group_by(ser_emu_nameshort,ser_hty_code) %>%
#    summarize(`first year`=min(bio_year),
#              `last year`=max(bio_year),
#              tau=round(Kendall(bio_year,lengthmm)$tau,digits=2),
#              p.value=round(Kendall(bio_year,lengthmm)$sl,digits=2)) %>%
#    mutate(signif=ifelse(p.value<=0.001,"***",
#                         ifelse(p.value<=0.01,"**",
#                                ifelse(p.value<=0.05,"*","ns"))))
#  }
#  tmp
#}
#
#plot_temporal_trend = function(var,stage,trends,sex=NULL){
#  data=mean_biom_hty_emuyear %>%
#    filter(ser_lfs_code==stage) %>%
#    inner_join(trends)
#    
#
#  var_name=switch (var,
#    "length" = "lengthmm",
#    "weight" = "bio_weight",
#    "sexratio" = "female_proportion"
#  )
#  
#  ylab=switch (var,
#    "length" = "Length (mm)",
#    "weight" = "Weight (g)",
#    "sexratio" = "Sex ratio (% female)"
#  )
#  if (!is.null(sex)){
#    var_name=paste(var_name,sex,sep="_")
#    ylab=paste(ifelse(sex=="m",
#                      "Male",
#                      "Female"),
#               ylab,
#               sep=" ")
#  }
#
#  data <- data %>%
#    filter(!is.na(!!as.symbol(var_name)))
#  col_pal=rep(colorpalette,length.out=nrow(trends))
#  ltypes=rep(c("solid","twodash","longdash","dotted","dashed"),length.out=(nrow(trends)))
#  ggplot(data,aes_string(x="bio_year",y=var_name))+
#    geom_line(aes(col=ser_emu_nameshort,lty=ser_emu_nameshort))+
#    theme_bw()+xlab("")+ylab(ylab)+
#    scale_color_manual("series",values=col_pal,guide=guide_legend(ncol=2))+
#    scale_linetype_manual("series",values=ltypes,guide=guide_legend(ncol=2))
#}
```



### Length
```{r yellowlengthtrend,echo=TRUE}
##Mixed
#trends=table_temporal_trend("length","Y",NULL)
#if (!is.na(trends)>0) autofit(flextable(trends))
#
#if (!is.na(trends)>0) plot_temporal_trend("length","Y",trends)
#
#
##female
#trends_f=table_temporal_trend("length","Y","f")
#if (!is.na(trends_f)) autofit(flextable(trends_f))
#
#if (!is.na(trends_f)) plot_temporal_trend("length","Y",trends_f,"f")
#
##male
#trends_m=table_temporal_trend("length","Y","m")
#if (!is.na(trends_f)) autofit(flextable(trends_m))
#
#if (!is.na(trends_f)) plot_temporal_trend("length","Y",trends_m,"m")

```

Significant trends are detected in several GB EMUs and in a few other locations. Tt generally
correspond to a decrease (
)
except in 2 EMUs 
).


### Weight
```{r yellowweighttrend,echo=TRUE}
##Mixed
#trends=table_temporal_trend("weight","Y",NULL)
#autofit(flextable(trends))
#
#if (!is.na(trends)>0) plot_temporal_trend("weight","Y",trends)
#
#
##female
#trends_f=table_temporal_trend("weight","Y","f")
#if (!is.na(trends_f)) autofit(flextable(trends_f))
#
#if (!is.na(trends_f)) plot_temporal_trend("weight","Y",trends_f,"f")
#
##male
#trends_m=table_temporal_trend("weight","Y","m")
#if (!is.na(trends_m)) autofit(flextable(trends_m))
#
#if (!is.na(trends_m)) plot_temporal_trend("length","Y",trends_m,"m")

```

Results are rather similar to length with several significant trends in GB and a few in other locations. Among significant trend, most of them correspond to a decrease (
) and a few to an increase (
). 

### Sex Ratio
It was not possible to carry out any sex ratio analysis for yellow eels.
```{r yellowsexratiotrend,echo=TRUE}
##Mixed
#trends=table_temporal_trend("sexratio","Y",NULL)
#if (!is.na(trends)>0) autofit(flextable(trends))
#
#if (!is.na(trends)>0) plot_temporal_trend("sexratio","Y",trends)

```



## Silver Eel
```{r}
#mean_biom_hty_emuyearS=mean_biom_hty_emuyear %>%
#  filter(ser_lfs_code=="S")
```


### Length
```{r silverlengthtrend,echo=TRUE}
##Mixed
#trends=table_temporal_trend("length","S",NULL)
#autofit(flextable(trends))
#
#if (!is.na(trends)>0) plot_temporal_trend("length","S",trends)
#### Silver eel map

#
##female
#trends_f=table_temporal_trend("length","S","f")
#if (!is.na(trends_f)) autofit(flextable(trends_f))
#
#if (!is.na(trends_f)) plot_temporal_trend("length","S",trends_f,"f")
#
##male
#trends_m=table_temporal_trend("length","S","m")
#if (!is.na(trends_m)) autofit(flextable(trends_m))
#
#if (!is.na(trends_m)) plot_temporal_trend("length","S",trends_m,"m")
```

Many significant trends were detected in length of silver eels. It appears to be related mainly to changes in female length. Both negative and positive trends were detected.

### Weight
```{r silverweightlengthtrend,echo=TRUE}
##Mixed
#trends=table_temporal_trend("weight","S",NULL)
#if (!is.na(trends)>0) autofit(flextable(trends))
#
#if (!is.na(trends)>0) plot_temporal_trend("weight","S",trends)
#
#
##female
#trends_f=table_temporal_trend("weight","S","f")
#if (!is.na(trends_f)) autofit(flextable(trends_f))
#
#if (!is.na(trends_f)) plot_temporal_trend("weight","S",trends_f,"f")
#
##male
#trends_m=table_temporal_trend("weight","S","m")
#if (!is.na(trends_m)) autofit(flextable(trends_m))
#
#if (!is.na(trends_m)) plot_temporal_trend("weight","S",trends_m,"m")
#

```
Results are very similar than for length, except than an additional increasing significant trend was detected for male weight in FR_Bret.

### Sex Ratio
```{r silversexratiotrend,echo=TRUE}
##Mixed
#trends=table_temporal_trend("sexratio","S",NULL)
#if (!is.na(trends)>0) autofit(flextable(trends))
#
#if (!is.na(trends)>0) plot_temporal_trend("sexratio","S",trends)
#
```
The sex ratio displays increasing trend in two EMUs.

## Glass Eel
For glass eel, of mixed G and GY, we remain at the time series scale (i.e. we do not average per EMU) since biometry is too sensitive to the timing of the sampling.

```{r functionglasseel,echo=FALSE}
#table_ge_trend = function(var){
#  data=data %>%
#    filter(ser_lfs_code %in% c("G","GY"))
#
#  var_name=switch (var,
#    "length" = "lengthmm",
#    "weight" = "bio_weight",
#    "sexratio" = "female_proportion"
#  )
#  
#  ylab=switch (var,
#    "length" = "Length (mm)",
#    "weight" = "Weight (g)",
#    "sexratio" = "Sex ratio (% female)"
#  )
#  
#
#  data <- data %>%
#    filter(!(is.na(!!as.symbol(var_name))))
#  
#  kept = data %>%
#    group_by(ser_nameshort,ser_hty_code,ser_lfs_code) %>%
#    filter(!is.na(lengthmm)) %>%
#    summarize(count=n()) %>%
#    filter(count>=5)
#  
#  inner_join(kept,data) %>%
#    group_by(ser_nameshort,ser_hty_code,ser_lfs_code) %>%
#      summarize(`first year`=min(bio_year),
#                `last year`=max(bio_year),
#                tau=round(Kendall(bio_year,lengthmm)$tau,digits=2),
#                p.value=round(Kendall(bio_year,lengthmm)$sl,digits=2)) %>%
#      mutate(signif=ifelse(p.value<=0.001,"***",
#                           ifelse(p.value<=0.01,"**",
#                                  ifelse(p.value<=0.05,"*","ns"))))
#}
#
#plot_ge_trend = function(var,trends){
#  data=inner_join(data,kept)
#
#  var_name=switch (var,
#    "length" = "lengthmm",
#    "weight" = "bio_weight",
#    "sexratio" = "female_proportion"
#  )
#  
#  ylab=switch (var,
#    "length" = "Length (mm)",
#    "weight" = "Weight (g)",
#  )
#  
#  ggplot(data,aes_string(x="bio_year",y=var_name))+
#    geom_line(aes(col=ser_nameshort))+
#    theme_bw()+xlab("")+ylab(ylab)+
#    scale_color_manual("series",values=colorpalette)
#}
```


### Length
Mean length of monitored eels has significantly increased over time in ImsaGY and SousGY.

```{r gelengthtrend,echo=TRUE}
#kept=table_ge_trend("length")
#  
#autofit(flextable(kept))
#
#plot_ge_trend("length",kept)
```


### Weight
Significant trends are also detected for weights.

```{r geweightlengthtrend,echo=TRUE}
#kept=table_ge_trend("weight")
#  
#autofit(flextable(kept))
#
#plot_ge_trend("weight",kept)

```

