---
title: "biometry_individual"
author: "ICES Data Group"
date: "12/09/2022"
bibliography: biometry.bib
csl: "../Rmarkdown/ices-journal-of-marine-science.csl"
output: 
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    reference_docx: "../Rmarkdown/ICES_template.docx"
params:
  load_data: FALSE
  run_rq: FALSE
---

# Individual biometrics data

** All graph and table are given to illustrate the data provided to th WGEEL through the data. They should not be taken
as a real analysis of trends, biological phenomenon ... **

```{r setup, include=FALSE}
source("../utilities/load_library.R")
source("biometry_individual_functions.R")

knitr::opts_chunk$set(echo = FALSE, warning=TRUE, message=FALSE, error=FALSE, fig.width=14.9/2.54, dpi=150)

load_library("readxl")
load_library("sf")
load_library("rnaturalearth")
load_library("getPass")
load_library("dplyr")
load_library("ggplot2")
load_library("Kendall")
load_library("RPostgres")
load_library("ggmap")
load_library("hues")
load_library("RPostgres")
load_library("flextable")
load_library("yaml")
load_library("tidyr")
load_library("lubridate")
load_library("stringr")
load_library("quantreg")
load_library("ggridges")
load_library("scales")
load_library(("ggpubr"))

if(Sys.info()["user"]=="hilaire.drouineau"){
  allometry=read_excel("~/Bureau/slopesintercepts.xlsx")
  setwd("~/Documents/Bordeaux/migrateurs/WGEEL/github/wg_WGEEL/R/biometry_analysis/")
}

colorpalette=cbf_1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73", 
           "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

if(params$load_data)
{
	# db connection
	cred=read_yaml("../../credentials.yml")
	con_wgeel = dbConnect(Postgres(), dbname=cred$dbname,host=cred$host,port=cred$port,user=cred$user, password=getPass())
	
	## download data from the database
	biometry_individual_series=dbGetQuery(con_wgeel,"with sel as(SELECT d.*, t_series.*, mty_name FROM datawg.t_metricindseries_meiser d, datawg.t_fishseries_fiser t_series, ref.tr_metrictype_mty WHERE mty_id=mei_mty_id AND mei_fi_id = fi_id) 
	select sel.*, ser_nameshort, ser_cou_code, ser_x,ser_y,ser_emu_nameshort, ser_hty_code,ser_lfs_code,gea_name_en, sam_samplingtype,t_series_ser.ser_qal_id from sel, datawg.t_series_ser, ref.tr_gear_gea, ref.tr_samplingtype_sam where ser_id=fiser_ser_id and ser_sam_gear=gea_id and ser_sam_id=sam_id")
	
	biometry_individual_series<-biometry_individual_series %>% filter(fi_id!=421454)
	
	biometry_individual_sampling=dbGetQuery(con_wgeel,"with sel as(SELECT d.*, t_samp.*, mty_name FROM datawg.t_metricindsamp_meisa d, datawg.t_fishsamp_fisa t_samp, ref.tr_metrictype_mty WHERE mty_id=mei_mty_id AND mei_fi_id = fi_id) 
	select * from sel, datawg.t_samplinginfo_sai where sai_id=fisa_sai_id")
	
	cou_ref=dbGetQuery(con_wgeel,"select cou_code, cou_order from ref.tr_country_cou")
	cou_ref= cou_ref[order(cou_ref$cou_order), ]
	
	values=c(RColorBrewer::brewer.pal(12,"Set3"),
	    RColorBrewer::brewer.pal(12, "Paired"), 
	    RColorBrewer::brewer.pal(8,"Accent"),
	    RColorBrewer::brewer.pal(8, "Dark2"))
	color_countries = setNames(values,cou_ref$cou_code)
	
	## preparing the data to be exploited
	
	  ## individual series
	
	data_ind_series = biometry_individual_series %>% 
		select(ser_id = fiser_ser_id, year = fi_year,date=fi_date,  fi_id, country=ser_cou_code, comment = fi_comment, quality = mei_qal_id, mty_name, mei_value,ser_nameshort, coord_x = ser_x, coord_y = ser_y,ser_emu_nameshort, ser_hty_code,ser_lfs_code, gea_name_en, sam_samplingtype,ser_qal_id) %>%
		pivot_wider(names_from = mty_name, values_from = mei_value)
	
	data_ind_series$ser_lfs_code=factor(as.character(data_ind_series$ser_lfs_code),levels=c("G","GY","Y","S"))
	data_ind_series$month<-format(data_ind_series$date,"%m")
	data_ind_series$country<-factor(data_ind_series$country,levels=cou_ref$cou_code,ordered=TRUE)
	
	  ## individual sampling data
	
	data_ind_samp = biometry_individual_sampling %>% 
	  mutate(year = ifelse(is.na(fi_year),year(fi_date), fi_year)) %>% 
		select(ser_id = fisa_sai_id, year, date=fi_date,  fi_id=mei_fi_id, coord_x=fisa_x_4326, coord_y=fisa_y_4326, fi_lfs_code, country=sai_cou_code, comment = fi_comment, quality = mei_qal_id, mty_name, mei_value,ser_nameshort=sai_name,ser_emu_nameshort=sai_emu_nameshort, ser_hty_code=sai_hty_code,sai_samplingstrategy) %>%
		pivot_wider(names_from = mty_name, values_from = mei_value)
	
	data_ind_samp$fi_lfs_code=factor(as.character(data_ind_samp$fi_lfs_code),levels=c("G","GY","Y","YS","S"))
	data_ind_samp$month<-format(data_ind_samp$date,"%m")
	data_ind_samp$country<-factor(data_ind_samp$country,levels=cou_ref$cou_code,ordered=TRUE)
	
	    ## total data
	
	total_individual= bind_rows(
		data_ind_series %>% as_tibble() %>%
			select(country, EMU = ser_emu_nameshort, ser_nameshort, coord_x, coord_y, year,month, lengthmm, weightg,eye_diam_meanmm, pectoral_lengthmm, ageyear,differentiated_proportion, female_proportion, habitat = ser_hty_code, life_stage = ser_lfs_code, gear = gea_name_en) %>%
			mutate(source = "series"),
	
		data_ind_samp %>% as_tibble() %>%
			mutate(commercial = str_detect(sai_samplingstrategy, "ommercial") | str_detect(sai_samplingstrategy, "CF")) %>%
			select(country, EMU = ser_emu_nameshort, ser_nameshort, coord_x, coord_y, year,month, lengthmm, weightg,eye_diam_meanmm, pectoral_lengthmm, ageyear,differentiated_proportion, female_proportion, habitat = ser_hty_code, life_stage = fi_lfs_code, commercial) %>% mutate(gear = "unkonwn", source = "sampling") 
	)	%>% 
		mutate(length_class_cm = as.integer(as.character(cut(lengthmm, breaks = seq(0, 1350, 10), labels = seq(0, 1340, 10) + 5)))/10)
	
	total_individual$country<-factor(total_individual$country,levels=cou_ref$cou_code,ordered=TRUE)
	
	#save(cou_ref, data_ind_series, data_ind_samp, color_countries, total_individual, biometry_individual_sampling, biometry_individual_series, file = "ind_biom.RData")
	dbDisconnect(con_wgeel)
} else {
	load("ind_biom.RData")
	warnings("The data was loaded with a RData file, please turn params `load_data` to TRUE if you want uptodate data")
}

```


```{r mapfunctions,echo=FALSE}

# compute the summary of data

stats_data_coord = total_individual %>% group_by(source,country,EMU, coord_x, coord_y,habitat,life_stage) %>%
	summarize(series=paste(unique(EMU),collapse=", "),
		n_lengthmm=(sum(!is.na(lengthmm))),
		n_bio_weight=(sum(!is.na(weightg))),
		n_female_proportion=(sum(!is.na(female_proportion))),
		n_pectoral_length=(sum(!is.na(pectoral_lengthmm))),
		n_eye_diam_meanmm=(sum(!is.na(eye_diam_meanmm))),
		n_ageyear=(sum(!is.na(ageyear))),
		n_differentiated_proportion=(sum(!is.na(differentiated_proportion)))) %>%
	filter((n_lengthmm + n_bio_weight + n_female_proportion + n_pectoral_length + n_eye_diam_meanmm + n_ageyear + n_differentiated_proportion)>0) %>%
	arrange(source,life_stage,country,habitat,EMU)

```

## Available data 

The table (**Annex**) describes the available individual biometric data from Appendix 1,2,3 (series) and 10 (sampling).

```{r available_data, include = TRUE }
#TODO: make the column's title more explicit (true title instead of variable names)

stats_data= total_individual %>% group_by(source, country, EMU, ser_nameshort, habitat, life_stage) %>%
  summarize(
            n_lengthmm=(sum(!is.na(lengthmm))),
            n_bio_weight=(sum(!is.na(weightg))),
            n_female_proportion=(sum(!is.na(female_proportion))),
            n_pectoral_length=(sum(!is.na(pectoral_lengthmm))),
            n_eye_diam_meanmm=(sum(!is.na(eye_diam_meanmm))),
            n_ageyear=(sum(!is.na(ageyear))),
            n_differentiated_proportion=(sum(!is.na(differentiated_proportion)))) %>%
  filter((n_lengthmm + n_bio_weight + n_female_proportion + n_pectoral_length + n_eye_diam_meanmm + n_ageyear + n_differentiated_proportion)>0) %>%
  arrange(source,life_stage,country,habitat,EMU)

ft = flextable(stats_data)
ft = set_caption(ft, "Number of avaible data for each biometry metrics")

autofit(ft)

```

## Length data

```{r lengthdecriptivegraphs, include=TRUE, fig.cap = "Length distribution par life stage and source of data"}
## length frequency

	ggplot(total_individual %>% mutate(type_sampling = ifelse(is.na(commercial), "Series", ifelse(commercial, "Fisheries sampling", "Scientific sampling")))) + aes(x = length_class_cm, color = life_stage) +
		geom_density() + facet_grid(life_stage ~type_sampling, scales = "free_y") +
		scale_color_discrete(guide = "none") +
		xlab("Length (cm)") + ylab("") + theme_classic() + theme(
			axis.text.y = element_blank(),
			axis.ticks = element_blank(),
			axis.text.x = element_text(angle = 90),
			axis.ticks.x = element_line()
		) + coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 
```

```{r lengthdecriptivegraphs-month, include=TRUE, fig.cap = "** not for the report ** Length distribution by month and by life stage. Point is the median, bar gives 5% and 95% quantile.", fig.height=20/2.54}
## length by month

total_lengthmmg<-total_individual %>% filter(!is.na(month),life_stage=="G",!is.na(lengthmm))%>%group_by(month)%>%summarise(q50=quantile(lengthmm,0.5),q5=quantile(lengthmm,0.05),q95=quantile(lengthmm,0.95))

total_lengthmmy<-total_individual %>% filter(!is.na(month),life_stage=="Y", !is.na(lengthmm))%>%group_by(month)%>%summarise(q50=quantile(lengthmm,0.5),q5=quantile(lengthmm,0.05),q95=quantile(lengthmm,0.95))

total_lengthmms<-total_individual %>% filter(!is.na(month), year>1,life_stage=="S",!is.na(lengthmm))%>%group_by(month)%>%summarise(q50=quantile(lengthmm,0.5),q5=quantile(lengthmm,0.05),q95=quantile(lengthmm,0.95))

gridExtra::grid.arrange(

ggplot(total_lengthmmg, aes(x=as.factor(month),y=q50)) + 
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ggtitle("Glass eel")+ 
  theme(axis.text.x = element_text(size = 12, angle = 90))+ 
  xlab("Month")+
  ylab("Length (mm)") + theme_classic(),

ggplot(total_lengthmmy, aes(x=as.factor(month),y=q50)) + 
  geom_pointrange(aes(ymin = q5, ymax = q95)) +ggtitle("Yellow eel")+ 
  theme(axis.text.x = element_text(size = 12, angle = 90))+ 
  xlab("Month")+
  ylab("Length (mm)") + theme_classic(),

ggplot(total_lengthmmy, aes(x=as.factor(month),y=q50)) + 
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ggtitle("Silver eel")+ 
  theme(axis.text.x = element_text(size = 12, angle = 90))+ 
  xlab("Month")+
  ylab("Length (mm)") + theme_classic(),

nrow = 3
)

```

** NO yellow eel to be checked **

```{r lengthdescriptivegraphsYS, include=TRUE, fig.cap = "Length distribtion by country and by life stage (yellow and silver)", fig.height=20/2.54}

plot_distribution(total_individual, lifeStage = c("Y", "S"), var = "length")

```

Glass eel larger than 100 mm (so excluded)  =
`r nrow(total_individual %>% filter(!is.na(lengthmm), lengthmm > 100, life_stage %in% c("G")))`.

```{r lengthdescriptivegraphsG, include=TRUE, fig.cap = "Length distribtion of glass eel by country"}

plot_distribution(total_individual %>% filter(lengthmm < 100), lifeStage = c("G"), var = "length", scale_value = 2, bandwidth_value = 2)

```


```{r lenghtgear, include=TRUE, fig.cap="Length distribution by gear and by life stage (yellow and silver eel"}

plot_distribution(total_individual%>% filter(life_stage %in% c("Y","S")), var = "length", lifeStage=c("Y","S"), scale_value = 2, group="gear", bandwidth_value = 2)


```

### Map of available length data by stage

Only the data series with more than 5 individual size measurements have been taken into account to make these maps

```{r maplength,echo=TRUE}

gridExtra::grid.arrange(
  plot_map_bio_emu("length","G",only_legend="no"),
  plot_map_bio_emu("length","Y",only_legend="no"),
  plot_map_bio_emu("length","S",only_legend="no"),
  plot_map_bio_emu("length","S",only_legend="yes"),

  nrow=2,
  ncol=2
)

#ggsave("map_length.png", map)

```








## Weight data

```{r weightdecriptivegraphs, include=TRUE, fig.cap = "** not for the report ** Weight distribution by year and by life stage. Point is the median, bar gives 5% and 95% quantile.", fig.height=20/2.54}

graph_weight = function(lifeStage = "G")
{
	lfs = switch(lifeStage,
		"G" = "Glass eel" ,
		"Y" = "Yellow eel",
		"S" = "Silver eel"
		)
		
		total_weightg<-total_individual %>% 
			filter(!is.na(weightg), !is.na(year), year>1, life_stage== lifeStage) %>%
			group_by(year) %>%
			summarise(q50=quantile(weightg, 0.5), q5=quantile(weightg,0.05), q95=quantile(weightg, 0.95))
		
		myplot = ggplot(total_weightg, aes(x=as.factor(year), y=q50)) + 
			geom_pointrange(aes(ymin = q5, ymax = q95)) + ggtitle(lfs)  + theme_classic()+ 
			theme(axis.text.x = element_text(angle = 90))+ 
			xlab("Year")+ylab("Weight (g)")
		
		return(myplot)
}


gridExtra::grid.arrange(
	graph_weight("G"),
	graph_weight("Y"),
	graph_weight("S"),
	nrow = 3
)

```


```{r weightdescriptivegraphsYS, include=TRUE, fig.cap = "Weight distribtion by country and by life stage (yellow and silver)"}

plot_distribution(total_individual, lifeStage =  c("Y","S"), var = "weight", bandwidth_value = 1)

```

Glass eel larger than 1g = `r nrow(total_individual %>% filter(weightg > 1, life_stage %in% c("G")))`.

```{r weightdescriptivegraphsG, include=TRUE, fig.cap = "Weight distribtion of glass eel by country"}

plot_distribution(total_individual  %>% filter(weightg < 1), lifeStage =  c("G"), var = "weight", scale_value = 1, bandwidth_value = 0.005)

```

### Map of available weight data by stage



```{r mapweight,echo=TRUE}

gridExtra::grid.arrange(
  plot_map_bio_emu("weight","G",only_legend="no"),
  plot_map_bio_emu("weight","Y",only_legend="no"),
  plot_map_bio_emu("weight","S",only_legend="no"),
  plot_map_bio_emu("weight","S",only_legend="yes"),

  nrow=2,
  ncol=2
)
```


## Length-Weight relationship


```{r lengthweightlfs, include=TRUE, fig.cap = "Length-Weight relationship by life stage and source"}

ggplot(total_individual %>% mutate(source = case_when(source == "sampling" ~ "Sampling", source == "series" ~ "Series"))) +
	aes(x=lengthmm, y=weightg) + 
	geom_point() +
  	facet_grid(vars(life_stage), vars(source),scale="free")+
  	theme_classic()+xlab("Length (mm)") + ylab("Weight (g)") +
  	xlim(c(0, NA)) + ylim(c(0, NA))

```

```{r lengthweightrelationship, include=TRUE, fig.cap = "Lenght-Weight relationship by life stage (point) and 75% quantile regression (line)"}

# all data

## prepare the data
reg_series_data <- 	total_individual %>%
	filter(!is.na(weightg), !is.na(lengthmm), 
		weightg>0, lengthmm>100,
		life_stage %in% c("Y","S"), !is.na(life_stage)
		) %>%
	mutate(country = factor(country, levels=cou_ref$cou_code, ordered=TRUE))

if(params$run_rq)
{
	reg_w_series = rq(log(reg_series_data$weightg) ~ log(reg_series_data$lengthmm), tau= 0.75)
#	save(reg_w_series, file = "reg_w_series.RData")
} else {
	load("reg_w_series.RData")
}

#calcul de Ws
reg_series_data$ws = exp(predict(reg_w_series, newdata = reg_series_data))

#calcul de Wr
reg_series_data$wr = reg_series_data$weightg / reg_series_data$ws *100

reg_series_data = reg_series_data %>% mutate(life_stage = case_when(life_stage =="Y" ~"Yellow eel", life_stage =="S" ~ "Silver eel"))

## regression with all data

ggplot(reg_series_data) +
	aes(lengthmm, ws) +
	geom_point(aes(lengthmm, weightg, colour=life_stage), size = 1, alpha = 0.3) + 
	geom_line() +
	scale_color_discrete("Life stage") +
	theme_classic() + xlab("Length (mm)") + ylab("Weight (g)") +
	coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0, NA)) +
	guides(color = guide_legend(override.aes = list(size = 5) ) ) 

```

[@blackwellRelativeWeightWr2000]

```{r lengthweightrelationship2, include=TRUE, fig.cap = "Relative Weight relationship by life stage"}
## representation of the results with all data

ggplot(reg_series_data) +
	aes(lengthmm, wr, colour=life_stage) +
	geom_point(alpha = 0.3, size = 1) +
	geom_hline(yintercept = c(25,200)) + 
	scale_y_continuous(trans = "log10", labels = scales::label_number(), breaks = c(0.1, 1, 10, 25, 100, 200, 1000, 10000)) +
	scale_color_discrete("Life stage") +
	theme_classic() + xlab("Length (mm)") + ylab("Relative weight (Wr)") +
	coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0.1, NA)) +
	guides(color = guide_legend(override.aes = list(size = 5) ) ) 

```

restricted to 25 -200

```{r lengthweightrelationship3, include=TRUE, fig.cap = "Relative Weight relationship by life stage, country and source"}

#n_total<-nrow(reg_series_data)
#
#n_inconsistent<-nrow(reg_series_data[reg_series_data$wr<25 | reg_series_data$wr>200,])

## boxplot of the resultat with only consistant data

reg_data_cons<-reg_series_data %>%
	filter(wr>25 & wr<200) %>% 
	mutate(source = case_when(source == "sampling" ~ "Sampling", source == "series" ~ "Series"))

ggplot(reg_data_cons) +aes(country, wr, fill=country) +
	geom_boxplot() + 
	scale_fill_manual(name = "Country", values=color_countries[names(color_countries) %in% unique(reg_series_data$country)], drop = TRUE)+
	geom_hline(yintercept =100) + facet_grid(vars(source),vars(life_stage))+
	theme_classic() + xlab("Country") + ylab("Relative weight (Wr)") +
	coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0.1, NA)) +
	guides(color = guide_legend(override.aes = list(size = 5) ) ) 

```

```{r rawdata, include=TRUE}

## Gear effect on size-weight
graph_LW = function(lifeStage = "G")
{
	mydata = data_ind_series %>% filter(ser_lfs_code == lifeStage)
	
	lfs = switch(lifeStage,
		"G" = "Glass eel" ,
		"GY" = "Glass & Yellow eel",
		"Y" = "Yellow eel",
		"S" = "Silver eel"
	)
	
	ggplot(mydata) +
		aes(x = lengthmm, y = weightg, color = country) + 
		geom_point(alpha = 0.3) +
		facet_grid(vars(gea_name_en))+
		scale_color_manual(name = "Country", values=color_countries[names(color_countries) %in% unique(mydata$country)], drop = TRUE) +
		theme_bw()+
		ggtitle(lfs)+xlab("Length (mm)")+ylab("Weight (g)") +
		theme_classic()  +
		coord_cartesian(expand = FALSE, xlim = c(0, NA), ylim = c(0.1, NA)) +
		guides(color = guide_legend(override.aes = list(size = 5) ) ) 
}

graph_LW("G")
graph_LW("GY")
graph_LW("Y")
graph_LW("S")

## lfs effect on size-weight

ggplot(data_ind_series, aes(x=lengthmm,y=weightg))+geom_point()+
  facet_wrap(.~ser_lfs_code,scale="free")+
  theme_bw()+ggtitle("All gears")+xlab("Length (mm)")+ylab("Weight (g)")

## length by gear and year

stat_length_g<- data_ind_series %>% filter(ser_lfs_code == "G") %>%
    group_by(year,gea_name_en,country) %>%
    dplyr::summarize(Mean = mean(weightg, na.rm=TRUE), sd=sd(weightg,na.rm=TRUE))

stat_length_y<- data_ind_series %>% filter(ser_lfs_code == "Y") %>%
    group_by(year,gea_name_en,country) %>%
    dplyr::summarize(Mean = mean(lengthmm, na.rm=TRUE), sd=sd(lengthmm,na.rm=TRUE))

ggplot(stat_length_g, aes(year, Mean))+ geom_pointrange(aes(ymin = Mean-sd, ymax = Mean+sd))+ 
  facet_grid(vars(gea_name_en),vars(country)) + theme_bw()+xlab("Year")+ylab("Mean length (mm)") +ggtitle("Glass eel")

ggplot(stat_length_y, aes(year, Mean))+ geom_pointrange(aes(ymin = Mean-sd, ymax = Mean+sd))+ 
  facet_grid(vars(country),vars(gea_name_en)) + theme_bw()+xlab("Year")+ylab("Mean length (mm)") +ggtitle("Yellow eel")

```

The point for silver eel greater than 1250 mm appear as an outlier and is excluded from the analysis. Weights should be
checked.

For the spatial analysis, we only considered ser_hty_code x EMU x lfs_code where at leat 5 data points were available
(they may come from different time series or years).


## Age

```{r agedescriptivegraphs, include=TRUE, fig.cap = "Age distribtion by country and by life stage"}
#TODO: add the number of samples for each line

plot_distribution(total_individual, lifeStage =  c("Y", "S"), var = "age", scale_value = 3, bandwidth_value = 0.5)

```

### Map of available age data by stage

Too few data were correlected regarding sex to draw any conclusions regarding differences in sex-ratios among locations.

```{r agemap,echo=TRUE}

gridExtra::grid.arrange(
  plot_map_bio_emu("age","Y",only_legend="no"),
  plot_map_bio_emu("age","S",only_legend="no"),
  plot_map_bio_emu("age","S",only_legend="yes"),

  nrow=2,
  ncol=2
)
```



## Growth

```{r agelengthy, fig.height=20/2.54, include=TRUE, fig.cap = "Length distribution by age and country for yellow eels"}

age_lengthy<-total_individual %>% filter(!is.na(ageyear), !is.na(lengthmm), life_stage=="Y") %>% 
		mutate(age_class = factor(ifelse(ageyear>19, "20+", ageyear), levels=c(0:19,"20+"), ordered=TRUE))

ggplot(age_lengthy) + aes(x = lengthmm, y=age_class, fill=country, alpha=0.5)  + 
  geom_density_ridges( scale = 3, rel_min_height = 0.005, bandwidth = 4)+ 
  scale_alpha(guide="none")+
  scale_fill_manual("Country",values=color_countries[names(color_countries) %in% unique(age_lengthy$country)], drop = TRUE)+
  ylab("Age (year)") +
  xlab("Length (mm)") +
  theme_classic() +
  coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 

```

```{r agelengths, fig.height=20/2.54, include=TRUE, fig.cap = "Length distribution by age and country for silver eels"}

age_lengths<-total_individual %>% filter(!is.na(ageyear), !is.na(lengthmm), life_stage=="S") %>% 
		mutate(age_class = factor(ifelse(ageyear>19, "20+", ageyear), levels=c(0:19,"20+"), ordered=TRUE))

ggplot(age_lengths) + aes(x = lengthmm, y=age_class, fill=country, alpha=0.5)  + 
  geom_density_ridges( scale = 3, rel_min_height = 0.005, bandwidth = 4)+ 
  scale_alpha(guide="none")+
  scale_fill_manual("Country",values=color_countries[names(color_countries) %in% unique(age_lengths$country)], drop = TRUE)+
  ylab("Age (year)") +
    xlab("Length (mm)") + 
    theme_classic() +
	coord_cartesian(expand = FALSE) + xlim(c(0, NA)) 

```

## Sex

```{r sexratio, include=TRUE, fig.cap = "Sex distribution by life stage and country"}

sexratio<-total_individual %>%
  mutate(sex=ifelse(is.na(female_proportion), "unknown", ifelse(female_proportion==1, "Female", "Male")))%>% 
  filter(life_stage %in% c("Y","YS","S"), sex != "unknown") %>%
  mutate(life_stage = case_when(life_stage =="Y" ~"Yellow eel", life_stage =="S" ~ "Silver eel", life_stage == "YS" ~ "Yellow or Silver eel"))

	ggplot(sexratio) + aes(country) +
	geom_bar(aes(fill = sex)) + 
	  facet_grid(vars(life_stage), scales = "free_y") +
	  scale_fill_discrete("Sex") +
	  theme_classic() + xlab("Country") + ylab("Count") + coord_cartesian(expand = FALSE) 

```

### Map of available sex data by stage

Too few data were correlected regarding sex to draw any conclusions regarding differences in sex-ratios among locations.

```{r sexratiomap,echo=TRUE}

gridExtra::grid.arrange(
  plot_map_bio_emu("sexratio","Y",only_legend="no"),
  plot_map_bio_emu("sexratio","S",only_legend="no"),
  plot_map_bio_emu("sexratio","S",only_legend="yes"),

  nrow=2,
  ncol=2
)
```


## To be changed in next data call

- add a life stage column in Annex 1-3 in individual biometrics (** same for group?**)
