---
title: "This file is to collate the revised measures version"
author: "none (contact Jani H for questions)"
date: "`r Sys.Date()`"

output:
  html_document: default
  #word_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# define libraries needed
libs <- c("readxl", "dplyr", "tidyr", "flextable", "knitr", "kableExtra", "officer", "readr", "tibble") 

#define libraries already installed
installed_libs <- libs %in% rownames(installed.packages())

# install libraries that are not installed already
if (any(installed_libs == F)) {
  install.packages(libs[!installed_libs])
}

# load libraries needed
invisible(lapply(libs, library, character.only = T))

```


```{r Import_files, include=FALSE}

### The folder where all the excel files are in. CHANGE IF NEEDED
folder_path <- "./Annex_14/revised"
#List of all emus
all_emus <- read_delim("Annex_14/Original files/all_emus.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
#Adding our standards
standards <- read_excel("./Annex_14/Other data/standards.xlsx")

# Get the list of .xls files
file_list <- list.files(path = folder_path, pattern = "\\.xlsx$", full.names = TRUE)

# Read each file into a separate data frame
data_frames <- lapply(file_list, read_excel)

# Name the data frames based on file names
names(data_frames) <- basename(file_list)
# Get all unique column names
all_columns <- unique(unlist(lapply(data_frames, colnames)))

# Ensure each data frame has all columns, filling missing columns with NA
data_frames <- lapply(data_frames, function(df) {
  missing_cols <- setdiff(all_columns, colnames(df))
  df[missing_cols] <- NA
  df <- df[all_columns]
  return(df)
})

# Check for unique "country" values across all data frames
all_countries <- unlist(lapply(data_frames, function(df) unique(df$country)))
if (length(all_countries) != length(unique(all_countries))) {
  warning("There are duplicate 'country' values across the data frames.")
}

# Combine all data frames into a single data frame
combined_df <- do.call(rbind, data_frames)


# Drop rows where fileorigin is "FileOrigin" because it was duplicated in one excel (i checked)
combined_df <- combined_df %>%
  filter(FileOrigin != "FileOrigin")


```

1.(and fill the rest with standard answers, if needed)
```{r}
library(readxl)
measures_check <- read_excel("./Annex_14/revised/allmeasures/measures_check.xlsx")

# Get the list of countries in combined_df
countries_in_combined <- combined_df$country

# Filter measures_check to keep only rows with countries not in combined_df
filtered_measures_check <- measures_check %>%
  filter(!country %in% countries_in_combined)

# Add a new column with the value TRUE for all rows
filtered_measures_check <- filtered_measures_check %>%
  mutate(JD_this_country_wasnt_checked = TRUE)


## Get the column names of both dataframes
combined_columns <- colnames(combined_df)
filtered_columns <- colnames(filtered_measures_check)

# Find columns that are in combined_df but not in filtered_measures_check
columns_in_combined_not_in_filtered <- setdiff(combined_columns, filtered_columns)

# Find columns that are in filtered_measures_check but not in combined_df
columns_in_filtered_not_in_combined <- setdiff(filtered_columns, combined_columns)

# Add missing columns to filtered_measures_check with NA values
for (col in columns_in_combined_not_in_filtered) {
  filtered_measures_check[[col]] <- NA
}

# Add missing columns to combined_df with NA values
for (col in columns_in_filtered_not_in_combined) {
  combined_df[[col]] <- NA
}

# Add the 'comment' column to combined_df with NA values
combined_df <- combined_df %>%
  mutate(comment = NA)

#dirty change to character
combined_df$FileOrigin <- as.character(combined_df$FileOrigin)
filtered_measures_check$FileOrigin <- as.character(filtered_measures_check$FileOrigin)

# Combine the two dataframes
combined_df <- bind_rows(combined_df, filtered_measures_check)




```


2. for every quantifiable measure we need to ask to fill (in "value_missing_in"; create columns if not already exist)
  2a) "effectiveness monitored" and "estimated_effect_size" "effect_size_unit"
  2b) "target_value", "target_unit", "value_achieved", and when no value ask to fill "degree_achieved" if feasible (we should prefill with fully for those where we have "yes" in "target achieved" and then delete the column "trarget_achieved", will address in guidance) 

5. For those that provided nothing (where source=2021)  I guess " value_missing_in" should spell "all" ?
Upload to SP

```{r valuemissing, include=FALSE}
#Make a new column degree achieved. It SHUOLD SAY "FULL"

combined_df <- combined_df %>%
  mutate(
    degree_achieved = ifelse(target_achieved %in% c("yes", "YES", "Yes"), "full", NA_character_)
  )

# Add the column 'value_achieved' to combined_df if it doesn't exist
if (!"value_achieved" %in% colnames(combined_df)) {
  combined_df$value_achieved <- NA
}

# Check the columns and update the Value_missing_in column
rev_measures_all <- combined_df %>%
  rowwise() %>%
  mutate(
    Value_missing_in = paste(
      na.omit(c(
        if (source == "2021") "ALL" else NA_character_,
        if (!is.na(std_quantifiable) && std_quantifiable == "TRUE" && (is.na(effectiveness_monitored) || effectiveness_monitored == "" || effectiveness_monitored == "NA")) "effectiveness_monitored" else NA_character_,
        if (!is.na(std_quantifiable) && std_quantifiable == "TRUE" && (is.na(target_value) || target_value == "" || target_value == "NA")) "target_value" else NA_character_,
        if (!is.na(std_quantifiable) && std_quantifiable == "TRUE" && (is.na(estimated_effect_size) || estimated_effect_size == "" || estimated_effect_size == "NA")) "estimated_effect_size" else NA_character_,
        if (!is.na(std_quantifiable) && std_quantifiable == "TRUE" && (is.na(target_unit) || target_unit == "" || target_unit == "NA")) "target_unit" else NA_character_,
        if (!is.na(std_quantifiable) && std_quantifiable == "TRUE" && (is.na(value_achieved) || value_achieved == "" || value_achieved == "NA")) "value_achieved" else NA_character_,
        if (!is.na(std_quantifiable) && std_quantifiable == "TRUE" && (is.na(degree_achieved) || degree_achieved == "" || degree_achieved == "NA")) "degree_achieved" else NA_character_
      )),
      collapse = "; "
    )
  ) %>%
  ungroup()

```

3. Remove all redundant columns - table should end at  "delete_reason",

4. Add columns in the end and highlight: "value_missing_in", "question_to_country" and one "country_answer". (fill the first two with what we provided)


```{r}
rev_measures_all <- rev_measures_all %>%
  mutate(
    country_answer = NA_character_
  ) %>%
  select(
    -quantifiable,
    -immediate,
    -direct,
    -std_quantifiable,
    -std_immediate,
    -std_direct,
    -check_this_column,
    -Spalte4,
    -source,
    -`Habitat type`,
    -Confirmation,
    -Comment,
    -...45,
    -...46,
    -target_achieved
  )
```

Write

```{r}
library(writexl)

# Write the dataframe to an Excel file
write_xlsx(rev_measures_all, "rev_measures_all.xlsx")
```


