---
title: 'WKLANDEEL FISHERIES DESCRIPTIONS'
author: 'Jan-Dag Pohlmann'
date: '05-16-2024'
output: 
  word_document: default
  html_document: 
    css: style.css
  pdf_document: default
---

```{r Initial preparations, include=FALSE}

#######################################################################################
### MAY NEED ADDITIONAL CHECKS, E.G. TO ENSURE THAT EMU IS CORRECT IN THE XLS FILES ###
#######################################################################################

##### 1.1 load libraries #####

### define libraries needed 
libs <- c("tidyverse", "readxl", "ggplot2", "ggforce", "stringr") #RPostgres may need to be installed manually 

### define libraries already installed
installed_libs <- libs %in% rownames(installed.packages())

### install libraries that are not installed already
if (any(installed_libs == F)) {
  install.packages(libs[!installed_libs])
}

### load libraries needed
invisible(lapply(libs, library, character.only = T))

#-------------------------#



#### 1.2 define paths ####

### path definitions
italy <- "C:/Users/pohlmann/Desktop/WKLANDEEL/data_call/fisheries description - IT_may_13.xlsx"
dc_folder <- "C:/Users/pohlmann/Desktop/WKLANDEEL/data_call"
catchdata <- "C:/Users/pohlmann/Desktop/WKLANDEEL/merged_data.RData"
wklandeelwd <- "C:/Users/pohlmann/Desktop/Home_Office/Projekte/wg_WGEEL/Misc/wklandeel/"

if (Sys.info()["user"]=="hdrouineau"){
  italy <- "~/Documents/Bordeaux/migrateurs/WGEEL/github/wg_WGEEL/Misc/wklandeel/filled_templates/fisheries_description/fisheries description - IT_may_13.xlsx"
  dc_folder <- "~/Documents/Bordeaux/migrateurs/WGEEL/github/wg_WGEEL/Misc/wklandeel/filled_templates/fisheries_description/"
  catchdata <- "~/Documents/Bordeaux/migrateurs/WGEEL/github/wg_WGEEL/Misc/wklandeel/merged_data.rdata"
  wklandeelwd <- "~/Documents/Bordeaux/migrateurs/WGEEL/github/wg_WGEEL/Misc/wklandeel"

}

```

```{r read data, include=FALSE}

#### 2.1 Create an empty global data frame to write all the input to ####

### create df with all relevant columns
fisheries_descriptions <- data.frame(country = as.character(),
                                     emu = as.character(),
                                     stage = as.character(),
                                     com_rec = as.character(),
                                     ISSCFG = as.numeric(),
                                     gear_name = as.character())

### create a dataframe with all relevant years
years <- seq(from = 1946, to = 2024)
year_columns <- as.data.frame(matrix(NA, ncol=length(years)))
year_columns <- year_columns[-c(1), ]
colnames(year_columns) <- years

### join year columns to fisheries descriptions
fisheries_descriptions <- cbind(fisheries_descriptions, year_columns)

#-------------------------#



#### 2.2 For countries that provided EMUs in differwent tabs in one file (only IT), read tabs separately and add to global df ####

### create a list of EMU tabs in italian submission
tabs <- excel_sheets(italy)
tabs <- tabs[grepl("IT", tabs)]

### read each sheet from italian call and rbind to fisheries descriptions


for (i in 1:length(tabs)){
  
temp <- read_excel(italy, sheet = tabs[i]) %>% mutate(emu = tabs[i]) %>% rename(com_rec = "com/rec", gear_name = "gear name")
fisheries_descriptions <- rbind(fisheries_descriptions, temp)  
  
print(i) 

}
 

 
#-------------------------#



#### 2.3 For countries that provided one file per EMU (containing a single tab with data), read files separately and add to global df ####

# create list of all relevant files
files <- list.files(dc_folder, pattern = "description", full.names = T)
files <- files[!grepl("IT", files)]

# read the respective sheet from each file and rbind to fisheries_descriptions
for (i in 1:length(files)){
  
  temp <- read_excel(files[i], sheet = "Fisheries description") %>% rename(com_rec = "com/rec", gear_name = "gear name") %>% select(1:85)
  fisheries_descriptions <- rbind(fisheries_descriptions, temp)  
  
  print(i) 
  
}

# replace incorrect symbols in the part of the table where data where data were entered
fisheries_descriptions[7:85] <- lapply(fisheries_descriptions[7:85], gsub,  pattern = "-", replacement = ">")
fisheries_descriptions[7:85] <- lapply(fisheries_descriptions[7:85], gsub,  pattern = ",", replacement = ".")

# save global df to RData
save(fisheries_descriptions, file = paste0(wklandeelwd,"fd_full.RData"))


```

```{r Create summary, include=FALSE}

#### 3. Create a summary file ####

# Convert data fra,me to long data
fd_long <- gather(fisheries_descriptions, year, value, 7:ncol(fisheries_descriptions)) %>% 
  filter(gear_name != "Total") %>% 
  mutate(year = as.integer(year),
         availability = ifelse(value == "NA", "no_information",
                               ifelse(value == "Y" | value == "y", "no_quantity",
                                      ifelse(value == 0, "quantified_zero", "quantified")))) 


# create summary
fd_summary <- fd_long %>% 
  filter(value != "NA") %>% 
  group_by(emu, com_rec, stage) %>% 
  summarize(min_year_total=min(year),
            max_year_total=max(year))

# create a data frame ex
fd_with_value <- fd_long %>% 
  filter(value != "NA") %>%
  filter(value != "Y"& value != "y") %>%
  group_by(emu, com_rec, stage) %>% 
  summarize(min_year_value=min(year),
            max_year_vlaue=max(year))

# add columns with max/min year where a value exists to fd_summary
fd_summary <- fd_summary %>% 
  left_join(fd_with_value, by = c("emu", "com_rec", "stage"))

# save summary to RData
save(fd_summary, file = paste0(wklandeelwd,"fd_summary.RData"))


```

## DATA AVAILABILITY
\
```{r Visualisation of availability, echo=FALSE, warning = FALSE, message = FALSE}

#### 4. visualize data availability ####

#### 4.1. by year ####

# create a summary of data availability by year (reported only)
fd_bar_year <- fd_long %>% 
  group_by(year, com_rec, stage) %>% 
  summarize(quantified = length(value[which(availability == "quantified")]),
            quantified_zero = length(value[which(availability == "quantified_zero")]),
            no_quantity = length(value[which(availability == "no_quantity")]),
            no_information = length(value[which(availability == "no_information")])) 
  
fd_bar_year <- gather(fd_bar_year, availability, value, 4:ncol(fd_bar_year))

# create graphs for commercial fisheries
com_by_year <- ggplot(data = fd_bar_year %>% filter(com_rec == "commercial"), aes(x=year, y=value, fill = availability)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_wrap(~stage) +
  theme_bw() +
  ggtitle("commercial by year")
com_by_year

# create graphs for recreational fisheries
rec_by_year <- ggplot(data = fd_bar_year %>% filter(com_rec == "recreational"), aes(x=year, y=value, fill = availability)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_wrap(~stage) +
  theme_bw() +
  ggtitle("recreational by year")
rec_by_year

#-------------------------#



#### 4.2  by EMU ####

# create a summary of data availability by emu (reported only)
fd_bar_emu <- fd_long %>% 
  group_by(emu, com_rec, stage) %>% 
  summarize(quantified = length(value[which(availability == "quantified")]),
            quantified_zero = length(value[which(availability == "quantified_zero")]),
            no_quantity = length(value[which(availability == "no_quantity")]),
            no_information = length(value[which(availability == "no_information")]))  
  
fd_bar_emu <- gather(fd_bar_emu, availability, value, 4:ncol(fd_bar_emu))

# create graphs for commercial fisheries
com_by_emu <- ggplot(data = fd_bar_emu %>% filter(com_rec == "commercial"), aes(x=emu, y=value, fill = availability)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_wrap(~stage) +
  theme_bw() +
  ggtitle("commercial_by_emu") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, size = 4))
com_by_emu

# create graphs for recreational fisheries
rec_by_emu <- ggplot(data = fd_bar_emu %>% filter(com_rec == "recreational"), aes(x=emu, y=value, fill = availability)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_wrap(~stage) +
  theme_bw() +
  ggtitle("recreational_by_emu") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, size = 4))
rec_by_emu

#-------------------------#



#### 4.3 by gear ####

# create a summary of data availability by emu (reported only)
fd_bar_gear <- fd_long %>% 
  group_by(gear_name, com_rec, stage) %>% 
  summarize(quantified = length(value[which(availability == "quantified")]),
            quantified_zero = length(value[which(availability == "quantified_zero")]),
            no_quantity = length(value[which(availability == "no_quantity")]),
            no_information = length(value[which(availability == "no_information")]))  

fd_bar_gear <- gather(fd_bar_gear, availability, value, 4:ncol(fd_bar_gear))

# create graphs for commercial fisheries
com_by_gear <- ggplot(data = fd_bar_gear %>% filter(com_rec == "commercial"), aes(x=gear_name, y=value, fill = availability)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_wrap(~stage) +
  theme_bw() +
  ggtitle("commercial_by_gear") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1.05, hjust=1.1, size = 6))
com_by_gear

# create graphs for recreational fisheries
rec_by_gear <- ggplot(data = fd_bar_gear %>% filter(com_rec == "recreational"), aes(x=gear_name, y=value, fill = availability)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_wrap(~stage) +
  theme_bw() +
  ggtitle("recreational_by_gear") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1.05, hjust=1.1, size = 6))
rec_by_gear

#-------------------------#

```
\
Fig. 1: Data availability of commercial and recreational landings expressed as percentage of rows by year, EMU and gear type. Each row represents data availability for a given life stage per EMU, gear type and year. Data was reported for all possible factor combinations of gear_type and year per EMU. Note, that EMUs are not weighted by size, i.e. countries with many small EMUs will have more rows and hence weight than countries with few large EMUs (except for the "by EMU" tables). no_information = data providers have no info at all, no_quantity = known landings but no quantification, quantified_zero = known zero landings, quantified = landings are quantified (either as a single value or upper/lower uncertainty margin) 
\
\

## REPORTED WKLANDEEL (UPPER/LOWER BOUNDARY AVAILABLE) vs LANDINGS FROM WGEEL DATABASE
\
```{r Compare uncertainty with landings, echo=FALSE, warning = FALSE, message = FALSE, results = "hide"}

#### 5. Compare landings with reported uncertainties (as of 05-14-2024)

# load catch data
load(catchdata)

# define a function to test if string contains numbers only
numbers_only <- function(x) !grepl("\\D", x)

# list emus that reported a value for commercial and recreational
fd_com_quant <- fd_long %>% filter(availability == "quantified" & com_rec == "commercial") %>% 
  mutate(min_landings_t = as.numeric(ifelse(numbers_only(value), value, sub(">.*", "", value))),
         max_landings_t = as.numeric(ifelse(numbers_only(value), value, sub(".*>", "", value))),
         min_landings = ifelse(min_landings_t > max_landings_t, max_landings_t, min_landings_t),
         max_landings = ifelse(min_landings_t > max_landings_t, min_landings_t, max_landings_t),
         min_landings_t = NULL,
         max_landings_t = NULL) %>% 
  group_by(country, emu, stage, year) %>% 
  summarize(min_landings = sum(min_landings),
            max_landings = sum(max_landings))
emus_com <- unique(fd_com_quant$emu)

fd_rec_quant <- fd_long %>% filter(availability == "quantified" & com_rec == "recreational") %>% 
  mutate(min_landings_t = as.numeric(ifelse(numbers_only(value), value, sub(">.*", "", value))),
         max_landings_t = as.numeric(ifelse(numbers_only(value), value, sub(".*>", "", value))),
         min_landings = ifelse(min_landings_t > max_landings_t, max_landings_t, min_landings_t),
         max_landings = ifelse(min_landings_t > max_landings_t, min_landings_t, max_landings_t),
         min_landings_t = NULL,
         max_landings_t = NULL) %>% 
  group_by(country, emu, stage, year) %>% 
  summarize(min_landings = sum(min_landings),
            max_landings = sum(max_landings)) 
emus_rec <- unique(fd_rec_quant$emu)

# reduce landings data from db to emus that were reported with a quantity during WKLANDEEL
com_land <- commercial %>% filter(eel_emu_nameshort %in% emus_com) %>% select(eel_lfs_code, eel_year, eel_emu_nameshort, eel_value.db)
rec_land <- recreational %>% filter(eel_emu_nameshort %in% emus_com) %>% select(eel_lfs_code, eel_year, eel_emu_nameshort, eel_value.db)

# add margins to landings data (and add an indicator combining emu&lfs for filtering later)
com_land <- com_land %>% 
  left_join(fd_com_quant %>% select(country, emu, year, stage, min_landings, max_landings), by = c("eel_lfs_code" = "stage", "eel_emu_nameshort" = "emu", "eel_year" = "year")) %>% 
  mutate(difference = abs(max_landings-min_landings),
         min_landings_min = eel_value.db-(difference/2),
         min_landings_max = eel_value.db+(difference/2),
         min_landings_cor = min_landings*(eel_value.db/((abs(max_landings+min_landings))/2)),
         max_landings_cor = max_landings*(eel_value.db/((abs(max_landings+min_landings))/2)),
         difference_cor = abs(max_landings_cor - min_landings_cor),
         emu_lfs = paste(eel_emu_nameshort, eel_lfs_code, sep = "_")) %>% 
  filter(!is.na(eel_value.db) | !is.na(min_landings) |!is.na(max_landings))

rec_land <- rec_land %>% 
  left_join(fd_rec_quant %>% select(country, emu, year, stage, min_landings, max_landings), by = c("eel_lfs_code" = "stage", "eel_emu_nameshort" = "emu", "eel_year" = "year")) %>% 
  mutate(difference = abs(max_landings-min_landings),
         min_landings_min = eel_value.db-(difference/2),
         min_landings_max = eel_value.db+(difference/2),
         min_landings_cor = min_landings*(eel_value.db/((abs(max_landings+min_landings))/2)),
         max_landings_cor = max_landings*(eel_value.db/((abs(max_landings+min_landings))/2)),
         emu_lfs = paste(eel_emu_nameshort, eel_lfs_code, sep = "_")) %>% 
  filter(!is.na(eel_value.db) | !is.na(min_landings) |!is.na(max_landings)) 


# from com_land remove all emu/stage where no uncertainty is reported (otherwise it will show the EMU all stages if for one stage uncertainty is reported)

# remove rows with NA in uncertainty, extract eel_lfs that remain and filter the original frame for those (seperated by single value and upper/lower margin)
com_emu_lfs_margins <- unique(com_land %>% filter(!is.na(difference) & difference !=0) %>% pull(emu_lfs))
com_emu_lfs_single <- unique(com_land %>% filter(!is.na(difference) & difference ==0) %>% pull(emu_lfs))

rec_emu_lfs_margins <- unique(rec_land %>% filter(!is.na(difference) & difference !=0) %>% pull(emu_lfs))
rec_emu_lfs_single <- unique(rec_land %>% filter(!is.na(difference) & difference ==0) %>% pull(emu_lfs))

# create graphs of EMUs with uncertainty margins (com & rec)
 com_land_comp <- function(x) {
  ggplot(com_land %>% filter(eel_lfs_code == x) %>% filter(emu_lfs %in% com_emu_lfs_margins), aes(x=eel_year, y=eel_value.db)) +
  geom_ribbon(aes(ymin=min_landings_cor, ymax=max_landings_cor, fill = "band"), alpha = 0.5) +
  geom_line(alpha = 0.5) +
  geom_line(aes(x=eel_year, y=min_landings), color = "blue", linetype = "dashed") +
  geom_line(aes(x=eel_year, y=max_landings), color = "blue", linetype = "dashed") +
  geom_line() +
  theme_bw() +
  guides(fill="none") +
  facet_wrap(~eel_emu_nameshort, scales="free") +
  ggtitle(paste(x, "commercial", sep = "_")) +
     theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
}
temp_lfs <- com_land %>% filter(emu_lfs %in% com_emu_lfs_margins)
lapply(unique(temp_lfs$eel_lfs_code), com_land_comp)

 rec_land_comp <- function(x) {
  ggplot(rec_land %>% filter(eel_lfs_code == x) %>% filter(emu_lfs %in% rec_emu_lfs_margins), aes(x=eel_year, y=eel_value.db)) +
  geom_ribbon(aes(ymin=min_landings_cor, ymax=max_landings_cor, fill = "band"), alpha = 0.5) +
  geom_line(alpha = 0.5) +
  geom_line(aes(x=eel_year, y=min_landings), color = "blue", linetype = "dashed") +
  geom_line(aes(x=eel_year, y=max_landings), color = "blue", linetype = "dashed") +
  geom_line() +
  guides(fill="none") +
  theme_bw() +
  facet_wrap(~eel_emu_nameshort, scales="free") +
  ggtitle(paste(x, "recreational", sep = "_")) +
     theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
}
temp_lfs <- rec_land %>% filter(emu_lfs %in% rec_emu_lfs_margins)
lapply(unique(temp_lfs$eel_lfs_code), rec_land_comp)

```
\
Fig. 2: Comparison of landings values from the WGEEL db with values where an upper and lower boundary (i.e. uncertainty) was reported to WKLANDEEL for at least one gear type. Comparisons are made by EMU and life stages and seperated by commercial and recreational fisheries. Black line = landings from WGEEL db, dashed blue line = reported raw upper/lower boundary (sum of all gears for the respective life stage and year), red ribbon = upper/lower boundary was scaled up/down to the dimension of the reported value in WGEEL db (e.g. uncertainty was reported for a specific gear type while an unquantified fishery was reported as well; hence, the implicit assumption is that uncertainty is similar between different gears).
Note, that the sum of all reported gear types is possibly lower than the total (as reported to WGEEL) if landings are not quantified for every gear type used.
\
\
\
## REPORTED WKLANDEEL (SINGLE VALUE) VS REPORTED WGEEL DATABASE
\
```{r Compare reported single values with landings, echo=FALSE, warning = FALSE, message = FALSE, results = "hide"}

#### 6. Compare landings with reported single values (as of 05-14-2024)

# create graphs of EMUs with single landings value provided (com & rec)
 com_land_comp <- function(x) {
  ggplot(com_land %>% filter(eel_lfs_code == x) %>% filter(emu_lfs %in% com_emu_lfs_single), aes(x=eel_year, y=eel_value.db)) +
  geom_ribbon(aes(ymin=min_landings_cor, ymax=max_landings_cor, fill = "band"), alpha = 0.5) +
  geom_line(alpha = 0.5) +
  geom_line(aes(x=eel_year, y=min_landings), color = "blue", linetype = "dashed") +
  geom_line(aes(x=eel_year, y=max_landings), color = "blue", linetype = "dashed") +
  geom_line() +
  guides(fill="none") +
  theme_bw() +
  facet_wrap(~eel_emu_nameshort, scales="free") +
  ggtitle(paste(x, "commercial", sep = "_")) +
     theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
}
temp_lfs <- com_land %>% filter(emu_lfs %in% com_emu_lfs_single)
lapply(unique(temp_lfs$eel_lfs_code), com_land_comp)

 rec_land_comp <- function(x) {
  ggplot(rec_land %>% filter(eel_lfs_code == x) %>% filter(emu_lfs %in% rec_emu_lfs_single), aes(x=eel_year, y=eel_value.db)) +
  geom_ribbon(aes(ymin=min_landings_cor, ymax=max_landings_cor, fill = "band"), alpha = 0.5) +
  geom_line(alpha = 0.5) +
  geom_line(aes(x=eel_year, y=min_landings), color = "blue", linetype = "dashed") +
  geom_line(aes(x=eel_year, y=max_landings), color = "blue", linetype = "dashed") +
  geom_line() +
  theme_bw() +
  guides(fill="none") +
  facet_wrap(~eel_emu_nameshort, scales="free") +
  ggtitle(paste(x, "recreational", sep = "_")) +
     theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
}
temp_lfs <- rec_land %>% filter(emu_lfs %in% rec_emu_lfs_single)
lapply(unique(temp_lfs$eel_lfs_code), rec_land_comp)


```
\
Fig. 3: Comparison of landings values from the WGEEL db with values a single value (i.e. no uncertaint) was reported to WKLANDEEL for at least one gear type. Comparisons are made by EMU and life stages and seperated by commercial and recreational fisheries. Black line = landings from WGEEL db, dashed blue line = sum of all landings for a given year and life stage as reported to WKLANDEEL. 
Note, that the sum of all reported gear types is possibly lower than the total (as reported to WGEEL) if landings are not quantified for every gear type used.
\
\
\

## CUMULATIVE UNCERTAINTIES
\
```{r cumulative uncertainty reported, echo=FALSE, warning = FALSE, message = FALSE}

# create a summarized uncertainty over all reported EMUs per year
com_unc <- com_land %>% 
  group_by(eel_year, eel_lfs_code) %>% 
  summarize(uncertainty = sum(difference, na.rm=TRUE))
  
rec_unc <- rec_land %>% 
  group_by(eel_year, eel_lfs_code) %>% 
  summarize(uncertainty = sum(difference, na.rm=TRUE))

# create graph of uncertainty margins over time
unc_plot_com <- ggplot(com_unc %>% filter(uncertainty != 0), aes(x = eel_year, y = uncertainty)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~eel_lfs_code, scales="free_y") +
  ggtitle("Known minimum uncertainty commercial")
unc_plot_com

unc_plot_rec <- ggplot(rec_unc %>% filter(uncertainty != 0), aes(x = eel_year, y = uncertainty)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~eel_lfs_code, scales="free_y") +
  ggtitle("Known minimum uncertainty recreational")
unc_plot_rec

```

\
Fig 4: Known minimum uncertinty by lifestage; represented as the sum of differences between upper and lower boundary from all gear types and EMUs where respective data was re

```{r checkerrorsindb}
library(yaml)
cred=read_yaml("../../credentials.yml")
library(RPostgres)
con=dbConnect(Postgres(), dbname=cred$dbname, user=cred$user,port=cred$port,
              host=cred$host,password=cred$password)
library(glue)

landings_data <- dbGetQuery(con, "select eel_missvaluequal,eel_value,eel_year,eel_lfs_code,eel_emu_nameshort,eel_typ_id from datawg.t_eelstock_eel where eel_typ_id in (4,6) and eel_qal_id<5")


find_match <- function(year, lfs, emu,type=4){
  list_emu <- c(emu,paste0(substr(emu,1,3),"total"))
  list_lfs <- c(lfs,"AL")
  if (lfs %in% c("Y","S")) list_lfs <- c(list_lfs,"YS")
  if (lfs %in% c("YS")) list_lfs <- c(list_lfs,"Y","S")
  res <- landings_data %>%
         filter(eel_typ_id==type & eel_year==year & eel_lfs_code %in% list_lfs & eel_emu_nameshort %in% list_emu)
  if (nrow(res)==0) return(3)
  if (nrow(res %>% filter(!is.na(eel_value)))>0) return(1)
  as.integer(nrow(res %>% filter(is.na(eel_value)) %>% filter(eel_missvaluequal!="NP")) > 0)
}

potential_fishery <- fd_long %>%
  filter(availability %in% c("no_quantity","quantified")) %>%
  mutate(typ=ifelse(com_rec=="commercial",4,6)) %>%
  mutate(data_found = unlist(purrr::pmap(list(year,stage,emu,typ),find_match)))
potential_fishery %>%
  filter(data_found==3 & com_rec=="commercial") %>%
  arrange(year)
potential_fishery %>%
  filter(data_found==0 & com_rec=="commercial")



```
