---
title: "landing_comparison"
format: html
editor: visual
params:
  countryweel : !expr c("Finland","Netherlands", "France", "Sweden","Tunisia","Denmark", "Great Britain","Czech republic", "Albania","Belgium", "Italy", "Algeria", "Croatia", "Cyprus", "Greece", "Morocco","Latvia", "Egypt","Estonia", "Finland", "Germany", "Hungary", "Lithuania", "Montenegro", "Morocco","Norway", "Poland", "Portugal","Ireland","Spain","Turkey", "Slovenia")
  countryfao : !expr c("Finland","Netherlands (Kingdom of the)", "France", "Sweden","Tunisia","Denmark","United Kingdom","Czechia", "Albania", "Belgium", "Italy","Algeria","Croatia", "Cyprus",  "Greece", "Morocco", "Latvia", "Egypt", "Estonia", "Finland", "Germany", "Hungary", "Lithuania", "Montenegro", "Morocco","Norway", "Poland","Portugal", "Ireland","Spain","Türkiye","Slovenia")
  countryfdi : !expr c("Finland","Netherlands", "France", "Sweden","Tunisia","Denmark", "United Kingdom","Czechia", "Albania", "Belgium", "Italy","Algeria", "Croatia","Cyprus",  "Greece", "Morocco","Latvia", "Egypt",  "Estonia", "Finland", "Germany", "Hungary", "Lithuania", "Montenegro", "Morocco","Norway", "Poland", "Portugal","Ireland","Spain","Türkiye", "Slovenia")
---

## Objective

The objective of this document is to compile and compare different source of data.
Most will be collected from excel tables, some from the wgeel database

## wgeel database




```{r init}
library(yaml)
library(tidyverse)
library(RPostgres)
library(openxlsx)
library(janitor) #clean names
library(magrittr) # pipes and special pipes
library(wesanderson) #palette
setwd("C:/workspace/wg_WGEEL/Misc/wklandeel")
datawdpath <- "data"
# if you want to test the params within the notebook use instructions as follows :
# params <- list() ;  params$countryfao =  c("Netherlands (Kingdom of the)", "France", "Sweden","Tunisia","Denmark","United Kingdom"); 
# params$countryfdi = c("Netherlands", "France", "Sweden","Tunisia","Denmark", "United Kingdom")
knitr::opts_chunk$set(echo=TRUE, warning=FALSE)
theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = NA, color = NA))
}

```

# wgeel

loading the data from the database. They are saved in the data folder on the git.

```{r loaddb, eval=FALSE}
#| echo: true
# credentials are at the root of the git wg_WGEEL
cred=read_yaml("../../credentials.yml")
con=dbConnect(Postgres(), dbname=cred$dbname, user=cred$user,port=cred$port,
              host=cred$host,password=cred$password)

# to get access to the sea, we use the tr_emusplit_ems table
# this is OK as we have not duplicated sea - emu in France or the Netherlands
# but beware this would not work for Spain
# firt tables with only NL, and FR built for tests
# wgeel_landings <- dbGetQuery(con,"select t.*, emu_sea, emu_wholecountry from datawg.t_eelstock_eel t 
#                              JOIN ref.tr_emu_emu emu ON  eel_emu_nameshort=emu.emu_nameshort
#                              left join ref.tr_emusplit_ems ems on ems.emu_nameshort = emu.emu_nameshort
#                              where eel_qal_id in (0,1,2,4) and 
#                              eel_typ_id in (4) 
#                              and eel_cou_code in ('FR', 'NL')
#                              --and eel_lfs_code != 'G'
#                              --and NOT emu_wholecountry 
#                              ")
save(wgeel_landings, file = file.path(getwd(), datawdpath,"wgeel_landings.Rdata"))
wgeel_landings_all <- dbGetQuery(con,"select t.*, emu_sea, emu_wholecountry, cou_country from datawg.t_eelstock_eel t 
                             JOIN ref.tr_emu_emu emu ON  eel_emu_nameshort=emu.emu_nameshort
                             JOIN ref.tr_country_cou ON eel_cou_code = cou_code
                             left join ref.tr_emusplit_ems ems on ems.emu_nameshort = emu.emu_nameshort
                             where eel_qal_id in (0,1,2,4) and 
                             eel_typ_id in (4) 
                             --and eel_cou_code in ('FR', 'NL')
                             --and eel_lfs_code != 'G'
                             --and NOT emu_wholecountry 
                             ")
save(wgeel_landings_all, file = file.path(getwd(), datawdpath,"wgeel_landings_all.Rdata"))
```

```{r wgeel_treatment }
#| echo: false

load(file.path(getwd(),datawdpath, "wgeel_landings_all.Rdata"))
#str(wgeel_landings_all)
# group by country and sea to get separated landings from Atlantic and Mediterranean
wgeel_landings_1 <- wgeel_landings_all |> 
  rename(year= eel_year, country = cou_country,sea =emu_sea) |>
  filter(country %in% params$countryweel)  |>
  #filter(!(country=="FR" & emu_wholecountry)) |>
  mutate(sea=case_when(grepl("A",sea) ~ "Atlantic",
                       grepl("M",sea) ~ "Mediterranean",
                       TRUE ~"No distinction"),
         country = case_when(grepl("Great Britain",country) ~ "United Kingdom",
                             country=="Turkey" ~ "Türkiye",
                             TRUE ~ country))  |>
  
  mutate(habitat=ifelse(eel_hty_code %in% c("F","T"), "inland", "marine")) |>
  group_by(country, sea, year, habitat) |>
  summarize(landings_t = sum(eel_value, na.rm =TRUE)/1000, .groups="drop") |>
  mutate(source = "WGEEL")

wgeel_landings_1|>
  ggplot(aes(x=year, y=landings_t, color = country, shape = habitat)) +
  geom_point() + 
  geom_line() +
  facet_wrap(~ sea, scale = "free")

#wgeel_landings_1 |> filter(year==1986, country=='France')

```


# FDI

Data have been put in a data subfolder in misc/

```{r fdi }
file <- "FDI-catches_ELE-20240304.xlsx"
path <- file.path(getwd(), datawdpath,file)
file.exists(path)
fdi_catch <- read.xlsx(path, sheet = 1)


fdi_catch <- clean_names(fdi_catch)
fdi_catch1 <- fdi_catch |> filter(country%in%params$countryfdi) |> 
  select(year, total_live_weight_landed_tonnes, country, supra_region) |>
  rename(sea = supra_region ) |>
  mutate(landings_t = as.numeric(total_live_weight_landed_tonnes)) |>
  mutate(sea=ifelse(grepl("NAO",sea), "Atlantic", "Mediterranean"),
         habitat = "marine") |>
  group_by(year, sea, country,habitat) |>
  summarize(landings_t = sum(landings_t, na.rm=T)) |>
  mutate(source = "FDI")



print({ggplot(fdi_catch1,aes(x=year, y=landings_t, color = country, shape = habitat)) +
    geom_point() + 
    geom_line() +
    facet_wrap(~ sea, scale = "free_y")})

```

# FAO


```{r fao, message=FALSE, warning=FALSE}
# paste the file capture_quantity from the FAO subfolder
file <- "capture_quantity.csv"
path <- file.path(getwd(), datawdpath,file)
fao0 <- read.csv(path)
fao0 <- fao0 %>% select(!(ends_with("Flag")))
colnames(fao0)  <- gsub(("FAO.major.fishing.area"),"area", colnames(fao0)) 
colnames(fao0)  <- gsub((".Name.En"),"", colnames(fao0)) 
colnames(fao0)  <- gsub(("Inland.Marine.areas"),"Inland_Marine", colnames(fao0)) 
fao0 <- fao0 |> pivot_longer(cols=num_range("X",1950:2021),values_to="landings_t", names_to = "year",names_prefix="X")
fao0 <- janitor::clean_names(fao0)
fao0 <- fao0[!fao0$country=="Indonesia",]
 
fao_all <- fao0 |>
  mutate(sea=case_when(grepl("Atlantic",area) ~ "Atlantic",
                       grepl("Mediterranean",area) ~ "Mediterranean",
                       grepl("Inland",area) ~ "No distinction"),
         habitat = case_when(grepl("Marine",inland_marine) ~ "marine",
                             grepl("Inland",inland_marine) ~ "inland"),
         year=as.numeric(year))


fao <- fao_all |> 
  filter(country%in%params$countryfao) |>
  group_by(year, sea, country, habitat) |>
  summarize(landings_t = sum(landings_t, na.rm=T), .groups="drop")|>
  mutate(source = "FAO") 

fao <- fao %>% mutate(country = case_when(grepl("Netherland",country) ~ "Netherlands",
                                            TRUE ~ country))
### make graph of all data previous to selection
p <- ggplot(aes(x=year, y=landings_t, color = sea, shape = habitat), data=fao_all) +
  geom_point() + 
  geom_line() +
  facet_wrap(~ country, scale = "free_y") +
  scale_color_brewer(palette ="Set2") +
  theme_clean() 
png(file=file.path(getwd(), "image","fao_all.png"),width=12,height=8, res= 300, units="in")
print(p)
dev.off()
print(p)

#fao |> filter(year==1986, country=='France') %>% group_by(country) %>%
#  summarize(landings_t=sum(landings_t))
```


# OECD

```{r oecd}
file1 <- "OECD-inland_fisheries-European_eel-20240306.csv"
file2 <- "OECD-marine_landings-total_landings-European_eel-20240306.csv"
path1 <- file.path(getwd(), datawdpath,file1)
path2<- file.path(getwd(), datawdpath,file2)

oecd_inl <- read.csv(path1)
oecd_mar <- read.csv(path2)
oecd_inl$habitat <- 'inland'
oecd_mar$habitat <- 'marine'
oecd_mar$X2021 <- NA
oecd <- rbind(oecd_inl, oecd_mar)

oecd <- oecd |> pivot_longer(cols=num_range("X",2010:2021),values_to="landings_t", names_to = "year",names_prefix="X")

oecd <- oecd |> 
  janitor::clean_names() |>
  filter(country %in% params$countryfdi) |>
  mutate(
    year = as.numeric(year),
    source = "OECD",
    sea = "No distinction")

ggplot(aes(x=year, y=landings_t, color = habitat), data=oecd) +
  geom_point() + 
  geom_line() +
  facet_wrap(~ country, scale = "free_y")


```

# EUROSTAT

```{r eurostat}
file <- "eurostat data_inland marine catch all.csv"
path <- file.path(getwd(), datawdpath,file)
eurostat <- read.csv(path)


eurostat <- eurostat |> pivot_longer(cols=num_range("X",1950:2022),values_to="landings_t", names_to = "year",names_prefix="X")

eurostat <- eurostat |> 
  filter(country %in% params$countryfdi) |>
  rename(habitat =area) |>
  mutate( sea= "No distinction",
          year=as.numeric(year),
          source = "EUROSTAT")



ggplot(aes(x=as.numeric(year), y=landings_t, color = habitat), data=eurostat) +
  geom_point() + 
  geom_line() +
  facet_wrap(~ country, scale = "free")
unique(eurostat$country)

```

# Grouping together


```{r all together, warning=FALSE, results='hide'}

res <- bind_rows(fdi_catch1, wgeel_landings_1,fao,oecd, eurostat)


print(ggplot(res,aes(x=year, y=landings_t, color = country, shape = sea)) +
        geom_point() + 
        geom_line() +
        facet_wrap(~ habitat+source))



res %>% 
  split(.$country) %>%
  imap(~{
    p <- ggplot(.x,aes(x=year, y=landings_t, color = source, shape= sea)) +
      geom_point() + 
      geom_line() +
      facet_wrap(~ habitat, scale = "free") +
      ggtitle(.y) +
      scale_color_brewer(palette ="Set2") +
      theme_clean()
    print(p)
    png(file=file.path(getwd(), "image",paste0(.y,".png")),width=10,height=8, res= 300, units="in")
    print(p)
    dev.off()
  })



```

# Compare global landings country level


```{r check total, warning=FALSE, results='hide',fig.cap="Total landings"}

res1 <- res |> group_by(country, year,source) |>
  summarize(landings_t =sum(landings_t))
p <- ggplot(res1,aes(x=year, y=landings_t, color = source, shape= source)) +
  geom_point() + geom_line() +  facet_wrap(~country, scale="free_y") +
  ggtitle("Total landings") +
  scale_color_brewer(palette ="Set2") +
  theme_clean() 

print(p)
png(file=file.path(getwd(), "image","comparison_wgeel_fao_total.png"),width=12,height=8, res= 300, units="in")
print(p)
dev.off()

```


