---
title: "WKLANDEEL reported status of landings"
author: "Philip Jacobson, philip.jacobson@slu.se"
date: today  
format: html
embed-resources: true
editor: visual
code-fold: true
execute:
  warning: false
  message: false
---

## Introduction

This code is used to produce figure 4.3, 4.4, 4.5 & 4.6 and table 4.6 and 4.7 in the WKLANDEEL workshop report.

## R-packages

```{r}
library(tidyverse)
library(flextable)
library(RColorBrewer)
```

#### Load data which contain one dataset for commercial landings and one for recreational landings

```{r}
#.rdata file provided by Hilaire
load("merged_data.rdata") 
```

### Commercial landings

Create a table that displays the combination of values in the columns all_fishers_are_included, no_significant_underreporting and status and how many rows that contained each combination.

```{r}
#Display the combination of values in the columns all_fishers_are_included, no_significant_underreporting and status

summary_table<-commercial %>% 
 group_by(all_fishers_are_included, no_significant_underreporting, status) %>% 
   summarise(n_rows_commercial=n())

flextable(summary_table)
```

#### Create a new category for each combination in the table above:

```{r}
commercial<-commercial %>% 
  mutate(Missing_data_cat=case_when(
              all_fishers_are_included=="TRUE" & 
              no_significant_underreporting=="TRUE" & 
              status=="complete (all fishers, no underreporting)" 
              ~"complete (all fishers, no underreporting)",
              all_fishers_are_included=="TRUE" & 
              no_significant_underreporting=="TRUE" &
              status=="data aggregated/disaggregated elsewhere (stage, country)" 
              ~"data aggregated/disaggregated elsewhere (stage, country)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="missing and data does not exist" 
              ~"complete (data missing and data does not exist)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="missing but data might exist" 
              ~"complete (data missing but data might exist)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="partial but minor part missing" 
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              is.na(status)
              ~"No status reported",
              is.na(all_fishers_are_included) &
              is.na(no_significant_underreporting) & 
              is.na(status)
              ~"No status reported",
              is.na(all_fishers_are_included) &
              is.na(no_significant_underreporting) & 
              status=="data aggregated/disaggregated elsewhere (stage, country)"
              ~"data aggregated/disaggregated elsewhere (stage, country)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              is.na(status)
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial but minor part missing" 
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial and significant part missing" 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              status=="missing but data might exist" 
              ~"data missing but data might exist",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="TRUE" & 
              is.na(status) 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="TRUE" & 
              status=="partial and significant part missing" 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              is.na(status)
              ~"No status reported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial but minor part missing"
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial and significant part missing"
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="missing but data might exist"
              ~"data missing but data might exist",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="missing and data does not exist"
              ~"data missing and data does not exist",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="complete (all fishers, no underreporting)"
              ~"combination error",
              TRUE ~"Other"))

Missing_data_categories_table<-commercial %>% 
  group_by(all_fishers_are_included, no_significant_underreporting, 
           status, Missing_data_cat) %>% 
   summarise(n_rows_commercial=n())

flextable(Missing_data_categories_table)
```

#### Figure 4.3 - Proportion reported status of commercial landings

Plot the proportion of the reported status for each and life-stage:

```{r}
 Commercial_land_status<-commercial %>% 
  mutate(eel_lfs_code=fct_relevel(eel_lfs_code, 
                         c("G",
                           "Y", 
                           "S", 
                           "YS"))) %>%
  mutate(Missing_data_cat=fct_relevel(Missing_data_cat, 
                          c("complete (all fishers, no underreporting)",
                            "complete (data missing but data might exist)",
                            "complete (data missing and data does not exist)",
                            "partial but minor part missing/underreported",
                            "partial but major part missing/underreported", 
                            "data missing but data might exist",
                            "data missing and data does not exist"))) %>% 
   filter(Missing_data_cat!=
      "data aggregated/disaggregated elsewhere (stage, country)") %>% 
   filter(Missing_data_cat!="combination error") %>%
   filter(eel_lfs_code!="AL") %>%
   filter(Missing_data_cat!="No status reported") %>%
   filter(eel_year>=1980) %>% 
   group_by(eel_year, eel_lfs_code, Missing_data_cat) %>% 
      summarise(n_rows=n()) %>% 
          ggplot(., aes(x=eel_year, y=n_rows, fill=Missing_data_cat))+
          geom_bar(stat="identity", position="fill")+
          facet_wrap(~eel_lfs_code, scales="free_y")+
          theme_classic()+
          ylab("Proportion of reported status")+
          xlab("Year")+
          ggtitle("Commercial landings")+
          theme(legend.position="bottom")+
           scale_fill_manual(name=NULL, values=c("#1A9850", "#66BD63", 
                                       "#A6D96A", "#F46D43", 
                                       "#D73027", "#FFFFBF", 
                                       "#FDAE61", "grey65"))
    
 Commercial_land_status
  
ggsave("Fig4_3.jpg", Commercial_land_status, dpi=300, width=12, height=8)
```

#### Figure 4.4 - reported status of commercial landings per country and life stage

```{r}

# Plot the reported status for commercial landings per country and life stage:

Commercial_land_country<-commercial %>% 
separate(eel_emu_nameshort, into=c('Country', 'EMU'), sep='_', remove=FALSE) %>% 
  mutate(eel_lfs_code=fct_relevel(eel_lfs_code, c("G","Y", "S", "YS"))) %>%
  filter(eel_year>=1980,
      Missing_data_cat!="data aggregated/disaggregated elsewhere (stage, country)",
      Missing_data_cat!="combination error",
      Missing_data_cat!="No status reported",
      eel_lfs_code!="AL") %>%
  mutate(Missing_data_cat=fct_relevel(Missing_data_cat, 
                          c("complete (all fishers, no underreporting)",
                            "complete (data missing but data might exist)",
                            "complete (data missing and data does not exist)",
                            "partial but minor part missing/underreported",
                            "partial but major part missing/underreported", 
                            "data missing but data might exist",
                            "data missing and data does not exist"))) %>% 
   group_by(Country, eel_lfs_code, Missing_data_cat) %>% 
            summarise(n=n()) %>% 
     ggplot(., aes(x=eel_lfs_code, y=n, fill=Missing_data_cat))+
          geom_bar(stat="identity",position="fill", colour="black")+
          facet_wrap(~Country)+
          theme_classic()+
          ggtitle("Commercial landings")+
          xlab("Eel life stage")+
          ylab("Proportion of reported status")+
          theme(legend.position="bottom")+
          scale_fill_manual(name=NULL, values=c("#1A9850", "#66BD63", 
                                                   "#A6D96A", "#F46D43", 
                                                   "#D73027", "#FFFFBF", 
                                                   "#FDAE61", "grey65"))
Commercial_land_country

ggsave("Fig4_4.jpg", Commercial_land_country, dpi=300, width=12, height=8)

```

#### Table 4.6. Provided comments for status *complete (all fishers, no underreporting)* for commercial landings

Some modifications of the comments has been done in the report to reduce the amount of rows.

```{r}

complete_commercial<-commercial %>% 
  mutate(eel_lfs_code=fct_relevel(eel_lfs_code, c("G","Y", "S", "YS"))) %>%
  separate(eel_emu_nameshort, into=c('Country', 'EMU'), sep='_', remove=FALSE) %>%
    filter(Missing_data_cat == "complete (all fishers, no underreporting)",
           eel_lfs_code!="AL") %>% 
     group_by(Country, EMU,Missing_data_cat) %>% 
  distinct(`description of missing data`)

flextable(complete_commercial)
```

## Recreational catches

Make a table showing the combination of values in the three columns

```{r}
summary_table_rec<-recreational %>% 
 group_by(all_fishers_are_included, no_significant_underreporting, status) %>% 
   summarise(n_rows_commercial=n())

flextable(summary_table_rec)
```

Create categories dependning on value combinations

```{r}
recreational<-recreational %>% 
  mutate(Missing_data_cat=case_when(
              all_fishers_are_included=="TRUE" & 
              no_significant_underreporting=="TRUE" & 
              status=="complete (all fishers, no underreporting)" 
              ~"complete (all fishers, no underreporting)",
              all_fishers_are_included=="TRUE" & 
              no_significant_underreporting=="TRUE" &
              status=="data aggregated/disaggregated elsewhere (stage, country)" 
              ~"data aggregated/disaggregated elsewhere (stage, country)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="missing and data does not exist" 
              ~"complete (data missing and data does not exist)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="missing but data might exist" 
              ~"complete (data missing but data might exist)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="partial but minor part missing" 
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              status=="partial and significant part missing" 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="TRUE" & 
              is.na(status)
              ~"No status reported",
              is.na(all_fishers_are_included) &
              is.na(no_significant_underreporting) & 
              is.na(status)
              ~"No status reported",
              is.na(all_fishers_are_included) &
              is.na(no_significant_underreporting) & 
              status=="data aggregated/disaggregated elsewhere (stage, country)"
              ~"data aggregated/disaggregated elsewhere (stage, country)",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              is.na(status)
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial but minor part missing" 
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial and significant part missing" 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="TRUE" &
              no_significant_underreporting=="FALSE" & 
              status=="missing but data might exist" 
              ~"data missing but data might exist",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="TRUE" & 
              is.na(status) 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="TRUE" & 
              status=="partial and significant part missing" 
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="TRUE" & 
              status=="partial but minor part missing" 
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              is.na(status)
              ~"No status reported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial but minor part missing"
              ~"partial but minor part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="partial and significant part missing"
              ~"partial but major part missing/underreported",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="missing but data might exist"
              ~"data missing but data might exist",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="missing and data does not exist"
              ~"data missing and data does not exist",
              all_fishers_are_included=="FALSE" &
              no_significant_underreporting=="FALSE" & 
              status=="complete (all fishers, no underreporting)"
              ~"combination error",
              TRUE ~"Other"))

REC_Missing_data_categories_table<-recreational %>% 
  group_by(all_fishers_are_included, no_significant_underreporting, status, Missing_data_cat) %>% 
   summarise(n_rows_recreational=n())

flextable(REC_Missing_data_categories_table)
```

#### Figure 4.5. Proportion of reported status of recreational landings

```{r}
  Recreational_land_status<-recreational %>% 
  mutate(eel_lfs_code=fct_relevel(eel_lfs_code, c("G","Y", "S", "YS"))) %>%
  mutate(Missing_data_cat=fct_relevel(Missing_data_cat, 
                c("complete (all fishers, no underreporting)",
                  "complete (data missing but data might exist)",
                  "complete (data missing and data does not exist)",
                  "partial but minor part missing/underreported",
                  "partial but major part missing/underreported", 
                  "data missing but data might exist",
                  "data missing and data does not exist"))) %>% 
   filter(Missing_data_cat!=
          "data aggregated/disaggregated elsewhere (stage, country)") %>% 
   filter(Missing_data_cat!="combination error") %>%
   filter(Missing_data_cat!="No status reported") %>%
   filter(eel_lfs_code!="AL") %>%
   filter(eel_year>=1980) %>% 
      group_by(eel_year, eel_lfs_code, Missing_data_cat) %>% 
        summarise(n_rows=n()) %>% 
  ggplot(., aes(x=eel_year, y=n_rows, fill=Missing_data_cat))+
      geom_bar(stat="identity", position="fill")+
      facet_wrap(~eel_lfs_code, scales="free_y")+
      theme_classic()+
      ylab("Proportion reported status")+
      xlab("Year")+
      ggtitle("Recreational landings")+
      theme(legend.position="bottom")+
      scale_fill_manual(name=NULL, values=c("#1A9850", "#66BD63", 
                                               "#A6D96A", "#F46D43", 
                                               "#D73027", "#FFFFBF", 
                                               "#FDAE61", "grey65"))
    
 Recreational_land_status
  
ggsave("Fig4_5_rec.jpg", Recreational_land_status, dpi=300, width=12, height=8)
```

#### Figure 4.6 - reported status of recreational landings per country and life stage

```{r}
Fig_4_6_rec<-recreational %>% 
 separate(eel_emu_nameshort, into=c('Country', 'EMU'), sep='_', remove=FALSE) %>% 
 mutate(eel_lfs_code=fct_relevel(eel_lfs_code, c("G","Y", "S", "YS"))) %>%
 mutate(Missing_data_cat=fct_relevel(Missing_data_cat, 
                         c("complete (all fishers, no underreporting)",
                           "complete (data missing but data might exist)",
                           "complete (data missing and data does not exist)",
                           "partial but minor part missing/underreported",
                           "partial but major part missing/underreported", 
                           "data missing but data might exist",
                           "data missing and data does not exist"))) %>% 
   filter(Missing_data_cat!=
          "data aggregated/disaggregated elsewhere (stage, country)") %>% 
   filter(Missing_data_cat!="No status reported") %>%
   group_by(Country, eel_lfs_code, Missing_data_cat) %>% 
     summarise(n=n()) %>% 
   ggplot(., aes(x=eel_lfs_code, y=n, fill=Missing_data_cat))+
     geom_bar(stat="identity",position="fill", colour="black")+
      facet_wrap(~Country)+
       theme_classic()+
       ggtitle("Recreational landings")+
       xlab("Eel life stage")+
       ylab("Proportion of reported status")+
       scale_fill_manual(name=NULL, values=c("#1A9850", "#66BD63", 
                                                "#A6D96A", "#F46D43", 
                                                "#D73027", "#FFFFBF", 
                                                "#FDAE61", "grey65"))+
       theme(legend.position="bottom")

Fig_4_6_rec

ggsave("Fig4_6_rec.jpg", Fig_4_6_rec, dpi=300, width=12, height=8)
```

#### Table 4.7. Provided comments for status *complete (all fishers, no underreporting)* for commercial landings

```{r}
complete_recreational<-recreational %>% 
  mutate(eel_lfs_code=fct_relevel(eel_lfs_code, c("G","Y", "S", "YS"))) %>%
  separate(eel_emu_nameshort, into=c('Country', 'EMU'), sep='_', remove=FALSE) %>%
   filter(Missing_data_cat == "complete (all fishers, no underreporting)",
        eel_lfs_code!="AL") %>% 
  group_by(Country, EMU,Missing_data_cat) %>% 
  distinct(`description of missing data`)

flextable(complete_recreational)
```

# Done