### Model description

```{r setup-description}
#| echo = FALSE,
#| warning = FALSE,
#| message = FALSE
library("dplyr")
```

Through a literature review, we have identified two possible types of analyses. The common detail of these models is that both are using multivariate auto-regressive state-space (MARSS) models.
MARSS model is a family of state-space models [@hinrichsenUsingMultivariateStatespace2009]. They have been implemented through the MARSS package [@holmesAnalysisMultivariateTime2021].

MARSS models include a state process \@ref(eq:state-process) and an observation process \@ref(eq:observation-process) [adapted from  @holmesAnalysisMultivariateTime2021].

\begin{align}
X_{i,t} = B_{i} \cdot X_{i,t-1} + U_{i} +w_{i,t} \qquad \mbox{ with } \left \{w_{i,t} \right \}  \sim N(0,Q_t) (\#eq:state-process)
\end{align}

\begin{align}
Y_{j,t} = A_j + \sum_{i=1}^{n} Z_{i,j} \cdot X_{i,t} + v_{j,t} \qquad \mbox{ with } \left \{ v_{j,t} \right \}  \sim N(0,R_t)(\#eq:observation-process)
\end{align}

In these equations:

- $t$ is the year
- $X$ is the matrix of the $m$ trends
- $U$ is the linear trend
- $w_{i,t}$ is the process error
- $Y$ is the matrix of the $n$ (silver eel) time series
- $Z$ relates the $n$ time series to the $m$ trends
- $A$ is the offset of each time series
- $v_{j,t}$ is the observation error

The DFA method is a special case of MARSS models and is fully detailed in [@zuur2003]. The basic idea is to break down each time series into a weighted sum (through $Z$) of a few ($m$) common trends and a noise factor.
The method allows both to extract the common trends through the estimates of $X$, but also to see the importance of each trend in each series through $Z$. 
This method thus does not assume any *a priori* structure in the data and allows each individual time series to be related to 0, 1 or more of the $m$ common trends.

The other alternative is to define *a priori* structures (e.g. spatial structure)[@wardInferringSpatialStructure2010]. In that case each individual series belongs to one and only one trend.

The table \@ref(tab:table-models-summary) gives the details of the configuration of the MARSS model for both type of model.

```{r table-models-summary}
#| echo = FALSE,
#| results = "asis",
#| warning = FALSE,
#| message = FALSE,
#| tab.cap = "Model summary"

model_summary <- data.frame(
    row_name  = c("B", "U", "Q", "m", "A", "Z", "R"),
    DFA = c(
        "Identity",
        "0",
        "Identity",
        "1 to 5",
        "0",
        "Full n x m matrix",
        "Diagonal and equal or inequal"
    ),
    spatial = c(
        "Identity",
        "Unequal",
        "Diagonal and equal",
        "Determined by spatial structure",
        "Zero or unequal",
        "Spatial structure (0 & 1 matrix)",
        "Diagonal and unequal"
    )
)

ft <- flextable::flextable(
    model_summary
)

flextable::autofit(
    ft %>%
        flextable::set_header_labels(
            row_name = "",
            DFA = "DFA",
            spatial = "Spatial structure"
        )
)
```
