### Dynamic factor analysis (DFA)

```{r DFA-setup, echo=FALSE}
#| echo = FALSE
load_library("MARSS")
source("../DFA_functions.R")
```

```{r arrange-data-long}
#| echo = FALSE

d.cpue <- d.cpue %>%
    filter(das_year > 1979)

## Arrange the data for the dfa
silver_arr <- d.cpue %>%
    #removed the ser_id grouping
    ungroup %>%
    select(ser_nameshort, cpue, das_year) %>%
    arrange(das_year) %>%
    pivot_wider(
        names_from = ser_nameshort, values_from = cpue
    )

# Rank the ser_nameshort
data_summ <- unique(data.frame(
    ser_nameshort = d.cpue$ser_nameshort,
    ser_rank = d.cpue$ser_rank)
)

nameshort_ranked <- data_summ %>%
    arrange(ser_rank) %>%
    select(ser_nameshort) %>%
    pull()
```

```{r run-dfa-long}
#| echo=FALSE

if (params$rerunDFA_long) {
# Design of experiments
    S <- c("diagonal and equal")
    nbtrend <- 1:5
    expe <- expand.grid(S = S, nbtrend = nbtrend)
    S <- c("diagonal and unequal")
    nbtrend <- 1:5
    expe <- rbind(expe, expand.grid(S = S, nbtrend = nbtrend))

    # run DFA
    modele_S_DFA_nolog <- run_DFA(silver_arr, expe, log = FALSE)
    #save(modele_S_DFA_nolog, file = "DFA_long.RData")
} else {
    load("DFA_long.RData")
}
```

```{r table-summary-results-long}
#| echo = FALSE,
#| include = FALSE
results_dfa <- summary_models(modele_S_DFA_nolog)
# table_summary_models(results_dfa)
```

```{r graph-summary-results-long}
#| echo = FALSE,
#| include = FALSE

graph_dfa <- graph_summary_models(results_dfa)

best_fit_dfa <- best_DFA(modele_S_DFA_nolog)

#ggplot2::autoplot(best_fit_dfa, plot.type = "std.model.resids.ytT")

#ggplot2::autoplot(best_fit_dfa, plot.type = "qqplot.std.model.resids.ytt1")
```

```{r prepare-trends-long}
#| echo=FALSE
formatted_matrices_dfa <- results_DFA(best_fit_dfa)

signe_trend <- c()

for (i in seq_len(ncol(unlist(formatted_matrices_dfa$Z.conf$Z)))) {
    if (
        length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] > 0,
                i
            ]
        ) < length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] < 0,
                i
            ]
        )
    ) {
        signe_trend[i] <- -1
    } else {
        signe_trend[i] <- 1
    }
}
```

#### DFA using all the data available from the selected series

The best model selected based on Akaike information criterion for small sample size (AIC<sub>c</sub>) has two trends and an $R$ diagonal and equal, meaning that each time series have the same variability. The two trends are shown in the Figure \@ref(fig:graph-trend-long).

They both show a decline since 2000. The first trend shows a strong increase during the two first decades, while the second is rather stable during that period. The second trend shows a increase over the last decade.

The factor loadings $Z$ are displayed in the Figure \@ref(fig:graph-z-long). When the factor loading is positive (respectively negative) the given time series is positively (resp. negatively) related to the given trend. If factor loading crosses the 0, the given time series is not significantly related to the given trend.

In the following we give example on how these results should be interpreted. ‘AICS’ series is negatively correlated to trend 1 and not to trend 2. This time series indeed shows a sudden drop in the late 1980s and a slow increase afterward. `WarS` is positively correlated to trend 1 and not to trend 2. This time series do not have any data before the 2010s. Since that date the trend is inded decreasing like in trend 1. For this time series the DFA fit before that date is only due to the fact that this times series correlated well with trend 1 for the recent period. This extrapolation (period before 2010) should not be interpreted as a prediction of what `Wars`should have been in older period. `LoiS` is positively correlated to trend 2 and not to trend 1. It indeed show a decline since 2000 after two decades with a relative stability.


```{r graph-trend-long}
#| echo=FALSE,
#| fig.cap="Estimated common trends in silver eel time series using the data set since 1980."

graph_trends(
    trends = formatted_matrices_dfa$trends,
    year = sort(unique(silver_arr$das_year)),
    sign_trends = signe_trend
)
```

```{r graph-z-long}
#| echo = FALSE,
#| fig.cap = "Factor loadings (Z) for each time series for DFA using the dataset since 1980."

graph_Z(
    formatted_matrices_dfa$Z.conf,
    sign_trends = signe_trend
) + scale_y_discrete(limits = rev)
```
  
DFA fits to data are pres>ented in Figure \@ref(fig:serie-trend-long).
 

```{r serie-trend-long}
#| echo=FALSE,
#| fig.cap = "DFA fits to time series using the data set since 1980. Points = raw data, black line = DFA fit, grey zone = confidence interval.",
#| fig.width = 16 / 2.54,
#| fig.height = 16 / 2.54

series_trends_graph(best_fit_dfa, d.cpue, FALSE)
```

This DFA analysis makes it possible to describe common trends over the long term (since 1980). The analysis revealed two common trends. This general picture shows very contrasted situations(increase/decrease, more correlated to one and/or the other trends, etc.). However, the results should be taken with caution given the limited number of series that provided data for the period of 1980-1990 (8/28 series) and for the period of 1990-2000 (12/28). 
The lack of data for the earliest period may have an impact on trend analysis. To limit this impact and make it easier to interpret the results, a second DFA analysis has been carried out for the most recent years (since 2007).


#### DFA using data available from the selected series since 2007

```{r arrange-data-short}
#| echo = FALSE

d.cpue <- d.cpue %>%
    filter(das_year > 2006)

## Arrange the data for the dfa
silver_arr <- d.cpue %>%
    ungroup %>%
    select(ser_nameshort, cpue, das_year) %>%
    arrange(das_year) %>%
    pivot_wider(
        names_from = ser_nameshort,
        values_from = cpue
    )

# Rank the ser_nameshort
data_summ <- unique(data.frame(
    ser_nameshort = d.cpue$ser_nameshort,
    ser_rank = d.cpue$ser_rank)
)

nameshort_ranked <- data_summ %>%
    arrange(ser_rank) %>%
    select(ser_nameshort) %>%
    pull()
```


```{r run-dfa-short}
#| echo = FALSE

if (params$rerunDFA_short) {
    # Design of experiments
    S <- c("diagonal and equal")
    nbtrend <- 1:5
    expe <- expand.grid(S = S, nbtrend = nbtrend)
    S <- c("diagonal and unequal")
    nbtrend <- 1:5
    expe <- rbind(expe, expand.grid(S = S, nbtrend = nbtrend))

    # run DFA
    modele_S_DFA_nolog <- run_DFA(silver_arr, expe, log = FALSE)
    #save(modele_S_DFA_nolog, file = "DFA_16.RData")
} else {
    load("DFA_16.RData")
}
```

```{r table-summary-results-short}
#| echo = FALSE,
#| include = FALSE

results_dfa <- summary_models(modele_S_DFA_nolog)
#table_summary_models(results_dfa)
```
```{r graph-summary-results-short}
#| echo = FALSE,
#| include = FALSE

graph_dfa <- graph_summary_models(results_dfa)

best_fit_dfa <- best_DFA(modele_S_DFA_nolog)

#ggplot2::autoplot(best_fit_dfa, plot.type = "std.model.resids.ytT")

#ggplot2::autoplot(best_fit_dfa, plot.type = "qqplot.std.model.resids.ytt1")
```

For this analysis on the data since 2007, the best model selected based on AIC<sub>c</sub> has one trend and an $R$ diagonal and equal. This trend was represented in Figure \@ref(fig:graph-trend-short). The factor loadings (importance of each trend in each time series) are displayed in Figure \@ref(fig:graph-z-short). Nearly all factor loadings encompass the zero, meaning a weak support to the common trend. This can be due to a high variability in each individual time series compared to a low number of time series.

```{r prepare-trends-short}
#| echo=FALSE
formatted_matrices_dfa <- results_DFA(best_fit_dfa)

signe_trend <- c()

for (i in seq_len(ncol(unlist(formatted_matrices_dfa$Z.conf$Z)))) {
    if (
        length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] > 0,
                i
            ]
        ) < length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] < 0,
                i
            ]
        )
    ) {
        signe_trend[i] <- -1
    } else {
        signe_trend[i] <- 1
    }
}
```

```{r graph-trend-short}
#| echo = FALSE,
#| fig.cap = "Estimated common trend in silver eel time series using the dataset since 2007"

graph_trends(
    trends = formatted_matrices_dfa$trends,
    year = sort(unique(silver_arr$das_year)),
    sign_trends = signe_trend
)
```

```{r graph-z-short}
#| echo = FALSE,
#| fig.cap="Factor loadings (Z) for each time series for DFA using the dataset since 2007"

graph_Z(
    formatted_matrices_dfa$Z.conf,
    sign_trends = signe_trend
) + scale_y_discrete(limits = rev)
```



```{r serie-trend-short}
#| echo = FALSE,
#| fig.cap = "DFA fits to time series using the data set since 2007. Points = raw data, black line = DFA fit, grey zone = confidence interval.",
#| fig.width = 16 / 2.54,
#| fig.height = 16 / 2.54

series_trends_graph(best_fit_dfa, d.cpue, FALSE)
```


The contrasted results (positively/negatively/none correlated to the trend) are likely related to different conditions (environmental conditions, anthropogenic pressures, management practices) among river basins but this analysis does not allow us to go any further into the factors that may affect the correlation with one or more of the trends.
