### DFA

```{r DFA-setup, echo=FALSE}
#| echo = FALSE,
load_library("MARSS")
source("../DFA_functions.R")
```

#### DFA using all the data available from the selected series

```{r arrange-data-long, echo=FALSE}

#current_year=format(Sys.Date(), "%Y")
## select only data =>1980

 d.cpue <- d.cpue %>%
     filter(das_year > 1979)
# d.cpue <- d.cpue %>%
#     filter(das_year > 1979)
## Arrange the data for the dfa
silver_arr <- d.cpue %>%
    ungroup %>% #removed the ser_id grouping
    select(ser_nameshort, cpue, das_year) %>%
    arrange(das_year) %>%
    pivot_wider(names_from = ser_nameshort, values_from = cpue)

# Rank the ser_nameshort

	data_summ<-unique(data.frame(ser_nameshort=d.cpue$ser_nameshort,ser_rank=d.cpue$ser_rank))
	
	nameshort_ranked = data_summ %>% arrange(ser_rank) %>% select(ser_nameshort) %>% pull

```

```{r run-dfa-long,echo=FALSE}
#Design of experiments
S <- c("diagonal and equal")
nbtrend <- 1:5
expe <- expand.grid(S = S, nbtrend = nbtrend)
S <- c("diagonal and unequal")
nbtrend <- 1:5
expe <- rbind(expe, expand.grid(S = S, nbtrend = nbtrend))

# run DFA
#modele_S_DFA_nolog <- run_DFA(silver_arr, expe, log = FALSE)
#save(modele_S_DFA_nolog, file = "DFA_long.RData")

load("DFA_long.RData")

```

```{r table-summary-results-long, echo=FALSE,include=FALSE}
results_dfa <- summary_models(modele_S_DFA_nolog)
#table_summary_models(results_dfa)

```

```{r graph-summary-results-long, echo=FALSE, include=FALSE}

graph_dfa <- graph_summary_models(results_dfa)

best_fit_dfa <- best_DFA(modele_S_DFA_nolog)

#ggplot2::autoplot(best_fit_dfa, plot.type = "std.model.resids.ytT")

#ggplot2::autoplot(best_fit_dfa, plot.type = "qqplot.std.model.resids.ytt1")

```

```{r prepare-trends-long, echo=FALSE}
formatted_matrices_dfa <- results_DFA(best_fit_dfa)

signe_trend <- c()

for (i in seq_len(ncol(unlist(formatted_matrices_dfa$Z.conf$Z)))) {
    if (
        length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] > 0,
                i
            ]
        ) < length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] < 0,
                i
            ]
        )
    ) {
        signe_trend[i] <- -1
    } else {
        signe_trend[i] <- 1
    }
}

```

The best model selected based on AICc has two trends and an R diagonal and equal. The two trends are shown in the Figure \@ref(fig:graph-trend-long). The factor loadings $Z$ are displayed in the Figure \@ref(fig:graph-z-long). When the factor loading is positive (respectively negative) the given time series is positively (resp. negatively) related to the given trend. If factor loading crosses the 0, the given time series is not significantly related to the given trend.

```{r graph-trend-long, echo=FALSE, fig.cap="Estimated common trend in silver eel time series using the data set since 1980"}

graph_trends(
    trends = formatted_matrices_dfa$trends,
    year = sort(unique(silver_arr$das_year)),
    sign_trends = signe_trend
)

```

```{r graph-z-long, echo=FALSE,fig.cap="Factor loadings of the silver eel DFA using the data set since 1980"}

graph_Z(
    formatted_matrices_dfa$Z.conf,
    sign_trends = signe_trend
)
```
  
DFA fits to data are presented in Figure \@ref(fig:serie-trend-long).
 

```{r serie-trend-long, echo=FALSE, fig.cap="Silver DFA fits to time series using the data set since 1980", fig.width=16/2.54, fig.height=16/2.54}

series_trends_graph(best_fit_dfa, d.cpue, FALSE)

```

This DFA analysis makes it possible to describe common trends over the long term (since 1980). The analysis revealed two common trends. This general picture hinders very contrasted situations(increase/decrease, more correlated to one and/or the other trends, etc.). However, the results should be taken with caution given the limited series that provided data for the period of 1980-1990 (8/28 series) and for the period of 1990-2000 (12/28). 
The lack of data for the earliest period may have an impact on trend analysis. To limit this impact and make it easier to interpret the results, a second DFA analysis has been carried out for the most recent years (since 2007).


#### DFA using data available from the selected series since 2007

```{r arrange-data-short, echo=FALSE}

current_year=format(Sys.Date(), "%Y")
## select only data =>1980

  n_year <- 16

 d.cpue <- d.cpue %>%
     filter(das_year > as.numeric(current_year)-(n_year+1))
# d.cpue <- d.cpue %>%
#     filter(das_year > 1979)
## Arrange the data for the dfa
silver_arr <- d.cpue %>%
    ungroup %>% #removed the ser_id grouping
    select(ser_nameshort, cpue, das_year) %>%
    arrange(das_year) %>%
    pivot_wider(names_from = ser_nameshort, values_from = cpue)

# Rank the ser_nameshort

	data_summ<-unique(data.frame(ser_nameshort=d.cpue$ser_nameshort,ser_rank=d.cpue$ser_rank))
	
	nameshort_ranked = data_summ %>% arrange(ser_rank) %>% select(ser_nameshort) %>% pull

```


```{r run-dfa-short,echo=FALSE}
#Design of experiments
S <- c("diagonal and equal")
nbtrend <- 1:5
expe <- expand.grid(S = S, nbtrend = nbtrend)
S <- c("diagonal and unequal")
nbtrend <- 1:5
expe <- rbind(expe, expand.grid(S = S, nbtrend = nbtrend))


# run DFA
#modele_S_DFA_nolog <- run_DFA(silver_arr, expe, log = FALSE)
#save(modele_S_DFA_nolog, file = "DFA_16.RData")

load("DFA_16.RData")

```

```{r table-summary-results-short, echo=FALSE,include=FALSE}
results_dfa <- summary_models(modele_S_DFA_nolog)
#table_summary_models(results_dfa)

```
```{r graph-summary-results-short, echo=FALSE, include=FALSE}

graph_dfa <- graph_summary_models(results_dfa)

best_fit_dfa <- best_DFA(modele_S_DFA_nolog)

#ggplot2::autoplot(best_fit_dfa, plot.type = "std.model.resids.ytT")

#ggplot2::autoplot(best_fit_dfa, plot.type = "qqplot.std.model.resids.ytt1")



```

For this analysis on the data since 2007, the best model selected thanks to AICc has one trend and a  R diagonal and equal. This trend was represented in the Figure \@ref(fig:graph-trend-short). The factor loadings are displayed in the Figure \@ref(fig:graph-z-short)(importance of each trend in each time series). Nearly all factor loading encompass the zero, meaning a weak support to the common trend. This can be due to a high variability in each individual time series compare to a low number of time series.

```{r prepare-trends-short, echo=FALSE}
formatted_matrices_dfa <- results_DFA(best_fit_dfa)

signe_trend <- c()

for (i in seq_len(ncol(unlist(formatted_matrices_dfa$Z.conf$Z)))) {
    if (
        length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] > 0,
                i
            ]
        ) < length(
            formatted_matrices_dfa$Z.conf$Z[
                formatted_matrices_dfa$Z.conf$Z[, i] < 0,
                i
            ]
        )
    ) {
        signe_trend[i] <- -1
    } else {
        signe_trend[i] <- 1
    }
}

```

```{r graph-trend-short, echo=FALSE, fig.cap="Estimated common trend in silver eel time series using the data set with the last 16 years"}

graph_trends(
    trends = formatted_matrices_dfa$trends,
    year = sort(unique(silver_arr$das_year)),
    sign_trends = signe_trend
)

```

```{r graph-z-short, echo=FALSE,fig.cap="Factor loadings of the silver eel DFA using the data set with the last 16 years"}

graph_Z(
    formatted_matrices_dfa$Z.conf,
    sign_trends = signe_trend
)
```



```{r serie-trend-short, echo=FALSE, fig.cap="Silver DFA fits to time series using the data set with the last 16 years", fig.width=16/2.54, fig.height=16/2.54}

series_trends_graph(best_fit_dfa, d.cpue, FALSE)

```


The contrasted results (postively/negatively/none correlated to the trend) are likely related to different conditions (environmental conditions, anthropogenic pressures, management prac-tices) among river basins but this analysis does not allow us to go any further into the factors that may affect the correlation with one or more of the trends.
